### 2022-02-01 Codes/1_geo_ml_simulation.rmd
initial commit

# Set up

## Packages
```{r }

rm(list = ls())

# /*===========================================================
#' # Preparation
# /*===========================================================
#* set up python environment
library(reticulate)

#* packages
library(sp)
library(spdep)
library(spatialreg)
library(sf)
library(raster)
library(data.table)
library(tidyverse)
library(dplyr)
library(magrittr)
library(gstat)
library(GWmodel)
library(scam)
library(mgcv)
library(magic)
library(stringr)
library(ggplot2)
library(tictoc)
library(here)
```

## Other preparations 
```{r, include=FALSE}
#* set working directory
setwd(here())

#* source all the R functions in the Functions/R folder
fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
  purrr::map(~ source(.))

#* source all the python functions in the Functions/Python folder
# source_python(here("Codes", "Functions", "Python"))
# source_python(here("Codes", "Functions", "Python", "run_DML_OF.py"))
# source_python(here("Codes", "Functions", "Python", "run_DR_OF.py"))
# source_python(here("Codes", "Functions", "Python", "run_DML_OF_c.py"))
```

# Simulation Analysis

```{r}
#-----------------------------------------
# need to update the looping codes later
profit_ls <- list()
sce_i <-  3
#-----------------------------------------
```

## Prepare data
```{r}

#* Read field data
field_data <-
  readRDS(here("Data/field_data.rds")) %>% .[sce_i, ] %>% 
  pull(field_sf) %>%
  .[[1]]

#* Read field parameters
field_parameters <- readRDS(here("Data/field_parameters.rds")) %>% .[sce_i, ]

#* number of simulation cases
nsim <- field_parameters$field_pars[[1]][, max(sim)]

#* Read field data
field_with_design <- readRDS(here("Data/field_with_design.rds")) %>% .[sce_i, ]

#* Read the simulated data
sim_data <-
  field_with_design$data_file_name %>%
  readRDS()

#* Build spatial weights matrix
# Wls <- readRDS(file = here("Data", "Wls.rds"))
# 
#
#   #*****************************************************************************
# this part should be added to the data preparation codes, and saved in field_data
  dt <- sim_data$reg_data[[1]][sim == 1, ]$data[[1]]
  D <- matrix(NA, nrow(dt), nrow(dt))             # distance matrix
  for (i in 1:nrow(dt)){
      for(j in 1:nrow(dt)){
          D[i,j] <- sqrt((dt$X[i] - dt$X[j])^2+
                             (dt$Y[i] - dt$Y[j])^2 )
      }
  }
  W <- 1/D^2             # inverse distance weights matrix
  diag(W) <- 0
  W <- W/rowSums(W)			    # row-standardize
  Wls <- mat2listw(W)	            # "listw" object
  saveRDS(Wls, file=here("Data","Wls.rds"))
#   #*****************************************************************************
```

## Find true optimal N

```{r }
#* define prices
pN <- sim_data$pN
pCorn <- sim_data$pCorn

#* find true EONR
field_pars <-
  field_parameters$field_pars %>%
  rbindlist() %>%
  .[, opt_N := (pN / pCorn - b1) / (2 * b2)] %>%
  .[, opt_N := pmin(Nk, opt_N)] %>%
  .[, opt_N := pmax(0, opt_N)]
```

Quick visualiation of site-specific EONR

```{r }
# sim_i <- 1
# temp <-
#   left_join(field_data, field_pars[sim == sim_i, ], by = "cell_id")

# ggplot(data = temp) +
#   geom_sf(aes(fill = Nk), color = NA) +
#   scale_fill_viridis_c()
```

## Define simulation function

```{r }
run_analysis <- function(sim_i, x_vars, models_data, pN, pCorn, Wls, nsim) {
  print(sim_i)

  # /*+++++++++++++++++++++++++++++++++++
  #' ## Prepare data
  # /*+++++++++++++++++++++++++++++++++++
  # /*+++++++++++++++++++++++++++++++++++
  #* extract the data for the sim_i
  train_data <- sim_data$reg_data[[1]][sim == sim_i, ]
  cv_data <- sim_data$reg_data[[1]][sim == ifelse(sim_i + 1 > nsim, 1, sim_i + 1), ]

  #* define parameters
  N_levels <- train_data$N_levels[[1]]
  reg_data <-
    train_data$data[[1]] %>%
    .[, x := (X - min(X)) / (max(X) - min(X))] %>%
    .[, y := (Y - min(Y)) / (max(Y) - min(Y))] %>%
    .[, xy := x * y] %>%
    .[, N2 := N^2]

  # reg_data[, N] %>% hist(breaks = 30)
  # ggplot(reg_data) +
  #   geom_point(aes(y = yield, x = N))

  results <-
    models_data %>%
    .[on == TRUE, ] %>%
    rowwise() %>%
    mutate(results = list(
      run_indiv_analysis(model, reg_data, cv_data, x_vars, pN, pCorn, N_levels, Wls)
    )) %>%
    mutate(results = list(
      mutate(results, model = model)
    )) %>%
    pull(results) %>%
    rbindlist()

  return(results)
}
```

## Run simulation

```{r, include=FALSE}
models_data <-
  data.table(
    model = c(
      "ser", # spatial error
      "lm", # linear quadratic
      "gwr_t", # gwr-trevisan
      "gwr_semi", # gwr-semiparametric
      "gwr_zone_scam", # scam by zone,
      "ma_cf", # multiarm-CF
      "brf", # boosted RF
      "dmlof_semi", # semiparmetric DML-OF
      "dmlof_quad", # semiparmetric DML-OF
      "drof" # DR-OF
    ),
    on = c(
      TRUE, # ser
      TRUE, # lm
      FALSE, # gwr_t
      FALSE, # gwr_semi
      FALSE, # gwr_zone_scam
      FALSE, # ma_cf
      TRUE, # brf
      FALSE, # dmlof_semi
      FALSE, # dmlof_quad
      FALSE # drof
    )
  )

x_vars <-
  c(
    "b0_1", "b0_2",
    "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
    "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
    "theta_plateau_1", "theta_plateau_2",
    "theta_Nk_1", "theta_Nk_2",
    "theta_b0_1", "theta_b0_2"
  )

control_vars <- paste0(x_vars, collapse = "+")
int_vars <-
    paste0(
      paste0("I(N * ", x_vars, ")", collapse = "+"),
      "+",
      paste0("I(N2 * ", x_vars, ")", collapse = "+")
    )

feols_formula <-
    paste0(
      "yield ~ N + N2 + ",
      control_vars, "+",
      int_vars
    ) %>%
    formula()

sim_range <- c(1:10)

eonr_results <-
  lapply(
    sim_range,
    function(x) run_analysis(sim_i = x, x_vars, models_data, pN, pCorn, Wls, nsim)
  ) %>%
  rbindlist()

# eonr_results[, .N, by = .(model, sim, aunit_id)] %>%
#   .[, .N] %>%
#   hist()

profit <-
  eonr_results %>%
  nest_by(model) %>%
  mutate(
    profit =
      field_pars[sim %in% (sim_range + 1), ] %>%
        data.table(field_data)[, .(cell_id, aunit_id)][., on = "cell_id"] %>%
        data.table(data)[., , on = c("sim", "aunit_id")] %>%
        .[, yield := gen_yield_QP(b0, b1, b2, Nk, opt_N_hat)] %>%
        .[, profit := pCorn * yield - pN * opt_N_hat] %>%
        .[, mean(profit, na.rm = TRUE)]
  )

profit_ls[[sce_i]] <- profit
```

```{r}
saveRDS(profit_ls, here("Results", "profit_ls.rds"))
```

```{r }
eonr_results <-
  lapply(
    1:50,
    function(x) run_analysis(sim_i = x, pN, pCorn)
  ) %>%
  rbindlist()

eonr_results <- readRDS("Results/eonr_results_1_50.rds")

field_tau <-
  field_pars[sim %in% 1:50, ] %>%
  data.table(field_data)[, .(cell_id, aunit_id)][., on = "cell_id"] %>%
  unique(eonr_results, by = c("sim", "aunit_id"))[., on = c("sim", "aunit_id")]
```

## Profit assessment

```{r }
field_tau %>%
  .[, .(
    cell_id, b0, b1, b2, Nk, opt_N,
    opt_N_drof,
    opt_N_drof_smth,
    # opt_N_gwr,
    # opt_N_scam,
    # opt_N_gwr_semi,
    opt_N_dmlof_c,
    opt_N_brf,
    opt_N_macf
  )] %>%
  melt(id.var = c("cell_id", "b0", "b1", "b2", "Nk")) %>%
  .[!is.na(value), ] %>%
  .[, yield := gen_yield_QP(b0, b1, b2, Nk, value)] %>%
  .[, profit := pCorn * yield - pN * value] %>%
  .[, mean(profit), by = variable]
```

## Visualization of True and Estimated EONR

```{r }
dplyr::select(
  field_tau,
  opt_N,
  opt_N_drof,
  # opt_N_drof_smth,
  opt_N_gwr,
  # opt_N_scam,
  # opt_N_gwr_semi,
  opt_N_dmlof_c,
  opt_N_brf,
  opt_N_macf,
  geometry
) %>%
  melt(id.var = "geometry") %>%
  st_as_sf() %>%
  ggplot(data = .) +
  geom_sf(aes(fill = value), color = NA) +
  facet_grid(variable ~ .) +
  scale_fill_viridis_c()
```

```{r }
ggplot(field_tau) +
  geom_point(aes(y = opt_N, x = opt_N_dmlof_c)) +
  geom_abline(slope = 1, color = "red") +
  coord_equal()

```

### 2022-02-01 Codes/0_prepare_data.R

@@ -1,0 +1,175 @@
+# /*===========================================================
+#' # Preparation
+# /*===========================================================
+
+# === Packages ===#
+library(sp)
+library(spdep)
+library(spatialreg)
+library(sf)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(dplyr)
+library(magrittr)
+library(gstat)
+library(GWmodel)
+library(scam)
+library(parallel)
+library(magic)
+library(stringr)
+library(ggplot2)
+library(tictoc)
+library(here)
+options(stringsAsFactors = FALSE)
+
+# === Set working directory ===#
+setwd(here())
+
+# === load functions ===#
+#* source all the functions in the Functions folder
+fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
+  lapply(., function(x) source(x))
+
+# /*===========================================================
+#' # Create a field
+# /*===========================================================
+# ! Define field and plot characteristics here
+
+field_data <-
+  # ! This is where you set the experiment parameters
+  CJ(
+    # plot_length = 12, # the length of a plot (in number of cells)
+    plot_length = 12, # the length of a plot (in number of cells)
+    plot_width = 3, # the width of a plot (in number of cells)
+    cell_buffer = 1,
+    aunit_length = 2, # the length of an analysis unit (in number of cells)
+    aunit_width = 3, # the width of an analysis unit (in number of cells)
+    cell = 6, # the length of a cell in meter
+    #* how wide the field is
+    field_col = c(36, 72, 144), # the number of cell columns
+    #* how tall the field is
+    field_row = 72, # the number of row columns
+    sp_range = c(600),
+    # gstat_model = "Exp",
+    gstat_model = "Sph",
+    #* prices
+    pCorn = 6.25 / 25.4, # $/kg
+    pN = 1 / 0.453592 # $/kg
+  ) %>%
+  rowwise() %>%
+  mutate(field_sf = list(
+    make_field(
+      field_col = field_col,
+      field_row = field_row,
+      aunit_length = aunit_length,
+      aunit_width = aunit_width,
+      cell = cell,
+      cell_buffer = cell_buffer
+    )
+  ))
+
+#* save the fields
+saveRDS(field_data, here("Data/field_data.rds"))
+
+# /*===========================================================
+#' # Add trial design layout
+# /*===========================================================
[…]

### 2022-02-01 Codes/1_geo_ml_simulation.R

@@ -1,0 +1,300 @@
+
+## Packages
+
+rm(list = ls())
+
+# /*===========================================================
+#' # Preparation
+# /*===========================================================
+#* set up python environment
+library(reticulate)
+
+#* packages
+library(sp)
+library(spdep)
+library(spatialreg)
+library(sf)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(dplyr)
+library(magrittr)
+library(gstat)
+library(GWmodel)
+library(scam)
+library(mgcv)
+library(magic)
+library(stringr)
+library(ggplot2)
+library(tictoc)
+library(here)
+
+#* set working directory
+setwd(here())
+
+#* source all the R functions in the Functions/R folder
+fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
+    purrr::map(~ source(.))
+
+
+
+
+# /*===========================================================
+#' # Read data
+# /*===========================================================
+
+#* Read field data
+field_data <-
+    readRDS(here("Data/field_data.rds")) %>%
+    pull(field_sf) 
+
+#* Read field parameters
+field_parameters <- readRDS(here("Data/field_parameters.rds"))
+
+#* Read field data
+field_with_design <- readRDS(here("Data/field_with_design.rds"))
+
+
+
+# /*===========================================================
+#' #  preparations
+# /*===========================================================
+
+## ---------------------------------
+## Regression functional form 
+## ---------------------------------
+
+x_vars <-
+    c(
+        "b0_1", "b0_2",
+        "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
+        "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
+        "theta_plateau_1", "theta_plateau_2",
+        "theta_Nk_1", "theta_Nk_2",
+        "theta_b0_1", "theta_b0_2"
+    )
+
+control_vars <- paste0(x_vars, collapse = "+")
+int_vars <-
+    paste0(
+        paste0("I(N * ", x_vars, ")", collapse = "+"),
+        "+",
+        paste0("I(N2 * ", x_vars, ")", collapse = "+")
+    )
+
+feols_formula <-
+    paste0(
+        "yield ~ N + N2 + ",
+        control_vars, "+",
+        int_vars
+    ) %>%
+    formula()
+
+
+## -----------------------
+## Models to run 
+## -----------------------
+
[…]

### 2022-02-01 Codes/1_gwr_simulation.R

@@ -1,0 +1,54 @@
+# /*===========================================================
+#' # MC simulation
+# /*===========================================================
+mc_sim_results <-
+  lapply(
+    1:nrow(field_with_design), # indices to loop over
+    function(x) {
+
+      # ! things to do
+      #* 1. estimate GWR and optimal N
+      #* 2. estimate BRF and optimal N
+
+      w_data <- field_with_design[x, ]
+
+      # ! for debugging
+      # data <- sim_results$data[[1]]
+      # pCorn <- sim_results$pCorn[[1]]
+      # pN <- sim_results$pN[[1]]
+      # sim <- sim_results$sim[[1]]
+      # N_levels <- sim_results$N_levels[[1]]
+
+      sim_results <-
+        #* read the right regression data for this
+        #* experimental setting from the data_file_name
+        readRDS(here(w_data$data_file_name)) %>%
+        dplyr::select(reg_data, pCorn, pN) %>%
+        unnest() %>%
+        rowwise() %>%
+        # ! MC simulations
+        mutate(mc_results = list(
+          tryCatch(
+            mc_simulate(
+              data = data,
+              pCorn = pCorn,
+              pN = pN,
+              sim = sim,
+              N_levels = N_levels
+            ),
+            error = function(e) NULL
+          )
+        )) %>%
+        dplyr::select(sim, mc_results)
+
+      results_return <-
+        w_data %>%
+        mutate(sim_results = list(sim_results))
+
+      return(results_return)
+    }
+  ) %>%
+  rbindlist()
+
+#* save the field parameters
+saveRDS(mc_sim_results, here("Results/mc_sim_results.rds"))

### 2022-02-01 Codes/2_post_sim_analysis.R

@@ -1,0 +1,288 @@
+# /*===========================================================
+#' # Preparation
+# /*===========================================================
+
+# === Packages ===#
+library(sp)
+library(spdep)
+library(spatialreg)
+library(sf)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(dplyr)
+library(magrittr)
+library(gstat)
+library(GWmodel)
+library(scam)
+library(mgcv)
+library(magic)
+library(stringr)
+library(ggplot2)
+library(tictoc)
+library(here)
+
+#* Set working directory
+setwd(here())
+
+#* Load functions
+fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
+  lapply(., function(x) source(x))
+
+# /*===========================================================
+#' # Load simulated data
+# /*===========================================================
+
+#* load generated parameters
+field_data <- readRDS(here("Data/field_data.rds"))
+field_with_design <- readRDS(here("Data/field_with_design.rds"))
+field_parameters <- readRDS(here("Data/field_parameters.rds"))
+
+#* cell-level true data (sprange=600 scenario)
+cell_data <- field_parameters$field_pars[[1]]
+field_dt <- field_parameters$field_sf[[1]] %>% data.table()
+cell_data <- cell_data[field_dt[, .(cell_id, aunit_id)], on = "cell_id"]
+
+#* load simulation results data
+mc_sim_results <- readRDS(file = here("Results/mc_sim_results.rds"))
+
+#* aunit-level estimated data
+est_data <-
+  mc_sim_results$sim_results[[1]] %>%
+  unnest(mc_results) %>%
+  data.table()
+
+#* price scenarios
+pCorn <- mc_sim_results$pCorn
+pN <- mc_sim_results$pN
+
+
+
+# /*===========================================================
+#' # Profitability Calculation
+# /*===========================================================
+
+# -----------------
+# Merge data
+# -----------------
+# === merge true parameters (cell) + estimation (aunit)
+merge_data <-
+  cell_data[est_data,
[…]

### 2022-02-01 Codes/3_figures.R

@@ -1,0 +1,397 @@
+# /*===========================================================
+#' # Visualization the field and spatial units
+# /*===========================================================
+# fig.id = "field-layout", 
+# fig.cap = "Simulated field layout with spatial unit definitions", 
+# fig.dim = c(6, 6)
+
+field_with_design <- readRDS(here("Data/field_with_design.rds"))
+field_sf <- field_with_design[1, ]$field_sf[[1]]
+
+
+
+
+
+#*************************   Performance Table    ******************************
+
+# load estimation results
+est_result_ls <-
+    readRDS(here("Results/est_result_ls_100.rds")) %>% 
+    rbindlist()
+
+dt <- est_result_ls %>% 
+    filter(model %in% c("brf", "lm", "rf", "ser_500")) %>%
+    mutate(
+        model = replace(model, model=="ser_500", "ser")
+    ) %>%
+    dplyr::select(model, perform, field_col) %>% 
+    unnest(perform) %>% 
+    data.table()
+
+perf_dt <- dt %>% 
+    .[order(sim, model), ] %>% 
+    .[, y := (rmse_cv==min(rmse_cv)) %>% as.numeric(), by = .(sim, field_col)] %>% 
+    .[, p := (profit==max(profit)) %>% as.numeric(), by = .(sim, field_col)] %>% 
+    .[, yp := y * p] %>% 
+    .[, .(n_y = sum(y),
+          n_p = sum(p),
+          n_yp = sum(yp)), by = .(field_col, model)] %>% 
+    print()
+
+perf_dt <- perf_dt %>% 
+    dcast(field_col ~ model, value.var = c("n_y", "n_yp")) %>% 
+    dplyr::select(field_col, 
+                  n_y_rf, n_yp_rf,
+                  n_y_brf, n_yp_brf,
+                  n_y_lm, n_yp_lm,
+                  n_y_ser, n_yp_ser) %>% 
+    print()
+    
+write.csv(perf_dt, here("Results/perf_dt_500.csv"))
+
+
+
+
+#*******************************************************************************
+
+
+
+plot_sf <-
[…]

### 2022-02-01 Codes/Functions/R/gen_field_pars.R

@@ -1,0 +1,169 @@
+#* Generate a complete set of variable:
+#* Plateau, Nk, b0, b1, b2, yeld error, application error
+
+# sp_range <- 600
+# gstat_model <- "Sph"
+# nsim <- 10
+# field_sf <-
+#   readRDS(here("Data/field_with_design.rds")) %>%
+#   .$field_sf %>%
+#   .[[1]]
+
+gen_field_pars <- function(sp_range, gstat_model, field_sf, nsim) {
+  xy <- data.table(field_sf)[, .(X, Y, cell_id)]
+
+  # === Nk ===#
+  Nk_data <-
+    gen_pars(
+      mean = 200,
+      psill = 1000,
+      range = sp_range,
+      coef_name = "Nk",
+      gstat_model = gstat_model,
+      xy = xy,
+      nsim = nsim
+    ) %>%
+    # >>> normalize <<<
+    .[, sd_b := sd(Nk), by = sim] %>%
+    .[, mean_b := mean(Nk), by = sim] %>%
+    .[, p := pnorm(Nk, mean = mean_b, sd = sd_b)] %>%
+    .[, Nk := 100 + p * 150] %>%
+    .[, c("cell_id", "sim", "Nk")]
+
+  # Nk_data$Nk %>% hist(breaks=40)
+  # rasterFromXYZ(Nk[sim==1, c("X","Y","Nk")]) %>% plot()
+
+  # === ymax ===#
+  ymax_data <-
+    gen_pars(
+      mean = 10000,
+      psill = 3000000,
+      range = sp_range,
+      coef_name = "ymax",
+      gstat_model = gstat_model,
+      xy = xy,
+      nsim = nsim
+    ) %>%
+    # >>> normalize <<<
+    .[, sd_b := sd(ymax), by = sim] %>%
+    .[, mean_b := mean(ymax), by = sim] %>%
+    .[, p := pnorm(ymax, mean = mean_b, sd = sd_b)] %>%
+    .[, ymax := 8000 + p * 8000] %>%
+    .[, c("cell_id", "sim", "ymax")]
+
+  # ymax$ymax %>% hist(breaks=100)
+  # rasterFromXYZ(ymax[sim==1, c("X","Y","ymax")]) %>% plot()
+
+  # === b0 ===#
+  b0_data <-
+    gen_pars(
+      mean = 6000,
+      psill = 200000,
+      range = sp_range,
+      coef_name = "b0",
+      gstat_model = gstat_model,
+      xy = xy,
[…]

### 2022-02-01 Codes/Functions/R/gen_reg_data.R

@@ -1,0 +1,97 @@
+gen_reg_data <- function(i, field_with_design, field_parameters) {
+  print(i)
+
+  experiment_data <-
+    data.table(field_with_design) %>%
+    .[i, ] %>%
+    left_join(
+      .,
+      dplyr::select(field_parameters, field_col, sp_range, field_pars),
+      by = c("field_col", "sp_range")
+    )
+
+  # === load cell level data (coef, error) ===#
+  cell_data <- experiment_data$field_pars[[1]]
+  field <- experiment_data$field_sf[[1]] %>% data.table()
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' # Define the levels of experimental input rate by simulation id
+  # /*+++++++++++++++++++++++++++++++++++
+  N_levels_data <-
+    cell_data[, .(sim, Nk)] %>%
+    .[Nk > 300, Nk := 300] %>%
+    .[, .(N_levels = list(
+      seq(
+        quantile(Nk, prob = 0.05),
+        quantile(Nk, prob = 0.95),
+        length = 5
+      ) %>%
+        pmax(0, .) %>%
+        round()
+    )), by = sim]
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' # Assign input rate
+  # /*+++++++++++++++++++++++++++++++++++
+  #* the number of blocks
+  block_num <- unique(field$block_id) %>% length()
+
+  #* assign N rates
+  n_assign_data <-
+    lapply(
+      cell_data[, sim] %>% unique(),
+      function(x) {
+
+        #* find the N_levels for the sim
+        N_levels <- N_levels_data[sim == x, N_levels][[1]]
+
+        #* assign N rates
+        assign_input_rate(
+          N_levels = N_levels,
+          block_num = block_num,
+          design = experiment_data$design_name
+        ) %>%
+          .[, sim := x]
+      }
+    ) %>%
+    rbindlist()
+
+  vars_to_summarize <-
+    names(cell_data) %>%
+    .[!(. %in% c("sim", "cell_id", "m_error", "N_error"))] %>%
+    c(., c("yield", "N", "X", "Y", "N_tgt"))
+
+  reg_data <-
+    field[cell_data, on = "cell_id"] %>%
+    n_assign_data[., on = c("sim", "block_id", "plot_in_block_id")] %>%
+    #* add cell-level N application noise to target N
[…]

### 2022-02-01 Codes/Functions/R/gen_weights_matrix.R

@@ -1,0 +1,42 @@
+#* Generate spatial weights matrix for each trial field scenario:
+#*   quarter, half, full
+#*   
+#*   
+
+
+gen_weights_matrix <- function(data_file_name, cutoff){
+
+    #=== load regression data ===#
+    dt <- data_file_name %>% readRDS() %>% 
+        pull(reg_data) %>% 
+        .[[1]] %>% 
+        pull(data) %>% 
+        .[[1]]
+    
+    #=== distance matrix ===#
+    D <- matrix(NA, nrow(dt), nrow(dt))
+    for (i in 1:nrow(dt)){
+        for(j in 1:nrow(dt)){
+            D[i,j] <- sqrt((dt$X[i] - dt$X[j])^2+
+                               (dt$Y[i] - dt$Y[j])^2 )
+        }
+    }
+    
+    #=== inverse distance weights matrix ===#
+    W <- 1/D^2                      # inverse distance
+    W[D > cutoff] <- 0              # cut off distance
+    diag(W) <- 0
+    W <- W/rowSums(W)			    # row-standardize
+    Wls <- mat2listw(W)	            # "listw" object
+    
+    return(Wls)
+}
+
+
+
+
+
+
+
+
+

### 2022-02-01 Codes/Functions/R/run_DML_OF_c_analysis.R

@@ -1,0 +1,87 @@
+# /*===========================================================
+#' # Continuous tretment DML_OF analysis
+# /*===========================================================
+
+run_DML_OF_c_analysis <- function(gam_formula, x_vars, w_vars, reg_data, cv_data, pN, pCorn, N_levels) {
+  data <- copy(reg_data)
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Construct T matrix
+  # /*+++++++++++++++++++++++++++++++++++
+  #* gam set up
+  gam_setup <- gam(gam_formula, data = data)
+
+  #* construct T matrix
+  T_mat <-
+    predict(gam_setup, data = data, type = "lpmatrix") %>%
+    #* get rid of the intercept
+    .[, -1]
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Define input data
+  # /*+++++++++++++++++++++++++++++++++++
+  Y <- data[, yield] %>% as.array() #* dependent var
+  X <- data[, x_vars, with = FALSE] %>% as.matrix() #* het impact driver
+  W <- data[, w_vars, with = FALSE] %>% as.matrix() #* controls
+  X_cv <-
+    cv_data$data[[1]] %>%
+    .[, x_vars, with = FALSE] %>%
+    as.matrix()
+
+  #* Define some hyper parameters
+  subsample_ratio <- 0.7
+  # lambda_reg <- sqrt(log(ncol(W)) / (10 * subsample_ratio * nrow(Y)))
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Estimation
+  # /*+++++++++++++++++++++++++++++++++++
+  #* estimate Doubly-Robus Orthogonal Forest
+  results_se <-
+    run_DML_OF_c(
+      Y = Y,
+      T = T_mat,
+      X = X,
+      W = W,
+      X_test = X_cv,
+      subsample_ratio = subsample_ratio
+    )
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Estimate yield at various treatment levels
+  # /*+++++++++++++++++++++++++++++++++++
+  N_data <-
+    data.table(
+      N = quantile(data$N, prob = seq(0, 1, length = 200))
+    )
+
+  eval_data <-
+    N_data %>%
+    predict(gam_setup, newdata = ., type = "lpmatrix") %>%
[…]

### 2022-02-01 Codes/Functions/R/run_brf_analysis.R

@@ -1,0 +1,64 @@
+# /*===========================================================
+#' # BRF analysis
+# /*===========================================================
+# ! Run BRF and do economic analysis
+
+
+run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
+  data <- copy(reg_data)
+
+  X <-
+    data[, c("N", x_vars), with = FALSE] %>%
+    data.frame()
+
+  Y <- data[, yield]
+
+  BRF_temp <-
+    grf::boosted_regression_forest(
+      X = X,
+      Y = Y,
+      num.trees = 2000,
+      # min.node.size = 10
+      tune.parameters = "all"
+    )
+
+  #************************   RMSR   ***********************
+  e_hat_train <- copy(data) %>%
+    .[, y_hat := predict(BRF_temp,
+      newdata = .[, c("N", x_vars), with = FALSE]
+    )] %>%
+    .[, e_hat := yield - y_hat] %>%
+    .[, .(aunit_id, e_hat)] %>%
+    setnames("e_hat", "e_hat_train")
+  e_hat_cv <- copy(cv_data$data[[1]]) %>%
+    .[, y_hat := predict(BRF_temp,
+      newdata = .[, c("N", x_vars), with = FALSE]
+    )] %>%
+    .[, e_hat := yield - y_hat] %>%
+    .[, .(aunit_id, e_hat)] %>%
+    setnames("e_hat", "e_hat_cv")
+  #*********************************************************
+
+  N_seq <-
+    data.table(
+      N = seq(min(data$N), max(data$N), by = 2)
+    )
+
+  brf_results <-
+    copy(cv_data$data[[1]]) %>%
+    .[, c("aunit_id", "yield", x_vars), with = FALSE] %>%
+    expand_grid_df(., N_seq) %>%
+    .[, yield_hat := predict(BRF_temp,
+      newdata = .[, c("N", x_vars), with = FALSE]
+    )] %>%
+    .[, pi_hat := pCorn * yield_hat - pN * N] %>%
+    .[, .SD[which.max(pi_hat)], by = aunit_id] %>%
+    .[, opt_N_hat := N] %>%
+    .[, .(aunit_id, opt_N_hat)] %>%
+    #--- RMSE ---
+    .[e_hat_train, on = "aunit_id"] %>%
+    .[e_hat_cv, on = "aunit_id"] %>%
+    .[, sim := cv_data$sim]
+
+  return(brf_results)
+}

### 2022-02-01 Codes/Functions/R/run_indiv_analysis.R

@@ -1,0 +1,143 @@
+# /*===========================================================
+#' # GWR analysis
+# /*===========================================================
+# ! Run GWR and do economic analysis
+
+run_indiv_analysis <- function(model, reg_data, cv_data, x_vars, pN, pCorn, N_levels, Wls) {
+  if (model == "lm") { # linear quadratic
+    results <-
+      run_linear_analysis(
+        reg_data,
+        cv_data,
+        x_vars,
+        pN, pCorn,
+        N_levels
+      )
+  } else if (model == "ser_50") { # spatial error
+    results <-
+      run_sperror_analysis_50(
+          reg_data = reg_data,
+          cv_data = cv_data,
+          x_vars = x_vars,
+          pN = pN, 
+          pCorn = pCorn, 
+          N_levels = N_levels,
+          Wls = Wls$Wls_50
+      )
+  } else if (model == "ser_100") { # spatial error
+      results <-
+          run_sperror_analysis_100(
+              reg_data = reg_data,
+              cv_data = cv_data,
+              x_vars = x_vars,
+              pN = pN, 
+              pCorn = pCorn, 
+              N_levels = N_levels,
+              Wls = Wls$Wls_100
+          )
+  } else if (model == "ser_200") { # spatial error
+      results <-
+          run_sperror_analysis_200(
+              reg_data = reg_data,
+              cv_data = cv_data,
+              x_vars = x_vars,
+              pN = pN, 
+              pCorn = pCorn, 
+              N_levels = N_levels,
+              Wls = Wls$Wls_200
+          )
+  } else if (model == "ser_500") { # spatial error
+      results <-
+          run_sperror_analysis_500(
+              reg_data = reg_data,
+              cv_data = cv_data,
+              x_vars = x_vars,
+              pN = pN, 
+              pCorn = pCorn, 
+              N_levels = N_levels,
+              Wls = Wls$Wls_500
+          )
+  } else if (model == "gwr_t") { # gwr-trevisan
+    results <-
+      run_GWR_analysis(
+        reg_data,
+        N_levels,
+        pN, pCorn
+      )
+  } else if (model == "gwr_semi") { # gwr-semiparametric
+    results <-
+      run_GWR_semi_analysis(
+        gam_formula = formula(yield ~ s(N, k = 4), m = 2),
+        reg_data,
+        N_levels,
+        pN, pCorn
+      )
[…]

### 2022-02-01 Codes/Functions/R/run_linear_analysis.R

@@ -1,0 +1,69 @@
+# /*===========================================================
+#' # GWR analysis
+# /*===========================================================
+# ! Run GWR and do economic analysis
+
+
+run_linear_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
+  data <- copy(reg_data)
+
+  control_vars <- paste0(x_vars, collapse = "+")
+  int_vars <-
+    paste0(
+      paste0("I(N * ", x_vars, ")", collapse = "+"),
+      "+",
+      paste0("I(N2 * ", x_vars, ")", collapse = "+")
+    )
+
+  feols_formula <-
+    paste0(
+      "yield ~ N + N2 + ",
+      control_vars, "+",
+      int_vars
+    ) %>%
+    formula()
+
+  ols_res <- fixest::feols(feols_formula, data = data)
+  
+
+  #************************   RMSR   ***********************
+  e_hat_train <- copy(data) %>% 
+      .[, y_hat := predict(ols_res, newdata = .)] %>% 
+      .[, e_hat := yield - y_hat] %>% 
+      .[, .(aunit_id, e_hat)] %>%
+      setnames("e_hat", "e_hat_train") 
+  e_hat_cv <- copy(cv_data$data[[1]]) %>% 
+      .[, y_hat := predict(ols_res, newdata = .)] %>% 
+      .[, e_hat := yield - y_hat] %>% 
+      .[, .(aunit_id, e_hat)] %>%
+      setnames("e_hat", "e_hat_cv") 
+  #*********************************************************
+ 
+
+  N_data <-
+    data.table(
+      N = seq(min(N_levels), max(N_levels), length = 50)
+    ) %>%
+    .[, N2 := N^2]
+
+  ols_results <-
+    copy(cv_data$data[[1]]) %>%
+    .[, `:=`(
+      N = NULL,
+      N2 = NULL
+    )] %>%
+    #--- prediction data ---
+    expand_grid_df(., N_data) %>%
+    .[, y_hat := predict(ols_res, newdata = .)] %>%
+    .[, pi_hat := pCorn * y_hat - pN * N] %>%
+    #--- optimal N ---
+    .[, .SD[which.max(pi_hat), ], by = aunit_id] %>%
+    .[, .(aunit_id, N)] %>%
+    setnames("N", "opt_N_hat") %>%
+    #--- RMSE ---
[…]

### 2022-02-01 Codes/Functions/R/run_linear_analysis_sd.R

@@ -1,0 +1,77 @@
+# /*===========================================================
+#' # GWR analysis
+# /*===========================================================
+# ! Run GWR and do economic analysis
+
+
+run_linear_analysis_sd <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
+  
+    train_data <- copy(reg_data)
+    test_data <- copy(cv_data$data[[1]])
+    
+    control_vars <- paste0(x_vars, collapse = "+")
+    int_vars <-
+        paste0(
+            paste0("I(N * ", x_vars, ")", collapse = "+"),
+            "+",
+            paste0("I(N2 * ", x_vars, ")", collapse = "+")
+        )
+    
+    #* Scale the train data
+    scaler_data <-
+        train_data[, c("aunit_id", "yield", "N", "N2", x_vars), with = FALSE] %>%
+        melt(id.vars = "aunit_id") %>%
+        nest_by(variable) %>%
+        mutate(scaler = 1 / max(data$value)) %>%
+        data.table() %>%
+        .[, .(variable, scaler)]
+    
+    scaled_train_data <-
+        train_data[, c("aunit_id", "yield", "N", "N2", x_vars), with = FALSE] %>%
+        scale_data(., scaler_data)
+    
+    # /*+++++++++++++++++++++++++++++++++++
+    #' ## Regression
+    # /*+++++++++++++++++++++++++++++++++++
+    feols_formula <-
+        paste0(
+            "yield ~ N + N2 + ",
+            control_vars, "+",
+            int_vars
+        ) %>%
+        formula()
+    
+    # === spatial error model ===#
+    ols_res <- fixest::feols(feols_formula, data = scaled_train_data)
+    
+    
+    # /*+++++++++++++++++++++++++++++++++++
+    #' ## Find EONR
+    # /*+++++++++++++++++++++++++++++++++++
+    #* define N space
+    N_data <-
+        data.table(
+            N = seq(min(N_levels), max(N_levels), length = 50)
+        ) %>%
+        .[, N2 := N^2]
+    
+    ols_results <-
+        copy(test_data) %>%
+        .[, `:=`(
+            N = NULL,
+            N2 = NULL
+        )] %>%
+        expand_grid_df(., N_data) %>%
+        .[, c("aunit_id", "N", "N2", x_vars), with = FALSE] %>%
+        scale_data(., scaler_data) %>%
[…]

### 2022-02-01 Codes/Functions/R/run_macf_analysis.R

@@ -1,0 +1,36 @@
+# /*===========================================================
+#' # GWR analysis
+# /*===========================================================
+# ! Run GWR and do economic analysis
+
+
+run_macf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
+    data <- copy(reg_data)
+    
+    Y <- data[, yield]
+    W_f <- as.factor(data[, N_tgt])
+    X <- data[, x_vars, with = FALSE]
+    X_cv <- cv_data$data[[1]][, x_vars, with = FALSE]
+    
+    macf_tau <- grf::multi_arm_causal_forest(X, Y, W_f)
+
+    
+    macf_results <-
+        predict(macf_tau, newdata = X_cv)[[1]][, , 1] %>%
+        data.table() %>%
+        .[, aunit_id := data[, aunit_id]] %>%
+        melt(id.var = "aunit_id") %>%
+        .[, N := as.numeric(str_extract(variable, "^[^-]*"))] %>%
+        .[, profit := pCorn * value - pN * N] %>%
+        .[, .SD[which.max(profit), ], by = aunit_id] %>%
+        .[profit < 0, N := N_levels[1]] %>%
+        .[, .(aunit_id, N)] %>%
+        setnames("N", "opt_N_hat") %>%
+        #--- RMSE not exist ---
+        .[, e_hat_train := 0] %>%
+        .[, e_hat_cv := 0] %>%
+        .[, sim := cv_data$sim]
+    
+    
+    return(macf_results)
+}

### 2022-02-01 Codes/Functions/R/run_mc_sim.R

@@ -1,0 +1,37 @@
+run_mc_sim <- function(field_with_design) {
+
+  # ! things to do
+  #* 1. estimate GWR and optimal N
+  #* 2. estimate BRF and optimal N
+
+  w_data <- field_with_design
+
+  sim_results <-
+    #* read the right regression data for this
+    #* experimental setting from the data_file_name
+    readRDS(here(w_data$data_file_name)) %>%
+    dplyr::select(reg_data, pCorn, pN) %>%
+    unnest() %>%
+    rowwise() %>%
+    # ! MC simulations
+    mutate(mc_results = list(
+      tryCatch(
+        mc_simulate(
+          data = data,
+          pCorn = pCorn,
+          pN = pN,
+          sim = sim,
+          N_levels = N_levels
+        ),
+        error = function(e) NULL
+      )
+    )) %>%
+    dplyr::select(sim, mc_results)
+
+  results_return <-
+    w_data %>%
+    mutate(sim_results = list(sim_results))
+
+  return(results_return)
+}
+

### 2022-02-01 Codes/Functions/R/run_rf_analysis.R

@@ -1,0 +1,59 @@
+# /*===========================================================
+#' # GWR analysis
+# /*===========================================================
+# ! Run GWR and do economic analysis
+
+# reg_data <- scaled_reg_data
+# cv_data <- scaled_cv_data
+
+run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
+  data <- copy(reg_data)
+
+  X <-
+    data[, c("N", x_vars), with = FALSE] %>%
+    data.frame()
+
+  Y <- data[, yield]
+
+  RF_temp <-
+    grf::regression_forest(
+      X = X,
+      Y = Y,
+      num.trees = 2000,
+      # min.node.size = 10
+      tune.parameters = "all"
+    )
+
+  #************************   RMSR   ***********************
+  e_hat_train <- copy(data) %>%
+    .[, y_hat := predict(RF_temp,
+      newdata = .[, c("N", x_vars), with = FALSE]
+    )] %>%
+    .[, e_hat := yield - y_hat] %>%
+    .[, .(aunit_id, e_hat)] %>%
+    setnames("e_hat", "e_hat_train")
+  e_hat_cv <- copy(cv_data$data[[1]]) %>%
+    .[, y_hat := predict(RF_temp,
+      newdata = .[, c("N", x_vars), with = FALSE]
+    )] %>%
+    .[, e_hat := yield - y_hat] %>%
+    .[, .(aunit_id, e_hat)] %>%
+    setnames("e_hat", "e_hat_cv")
+  #*********************************************************
+
+  rf_results <-
+    copy(cv_data$data[[1]]) %>%
+    .[, yield_hat := predict(RF_temp,
+      newdata = .[, c("N", x_vars), with = FALSE]
+    )] %>%
+    .[, pi_hat := pCorn * yield_hat - pN * N] %>%
+    .[, .SD[which.max(pi_hat)], by = aunit_id] %>%
+    .[, opt_N_hat := N] %>%
+    .[, .(aunit_id, opt_N_hat)] %>%
+    #--- RMSE ---
+    .[e_hat_train, on = "aunit_id"] %>%
+    .[e_hat_cv, on = "aunit_id"] %>%
+    .[, sim := cv_data$sim]
+
+  return(rf_results)
+}

### 2022-02-01 Codes/Functions/R/run_sperror_analysis_200.R

@@ -1,0 +1,103 @@
+# /*===========================================================
+#' # GWR analysis
+# /*===========================================================
+# ! Run GWR and do economic analysis
+
+
+run_sperror_analysis_200 <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, Wls) {
+  train_data <- copy(reg_data)
+  test_data <- copy(cv_data$data[[1]])
+
+  control_vars <- paste0(x_vars, collapse = "+")
+  int_vars <-
+    paste0(
+      paste0("I(N * ", x_vars, ")", collapse = "+"),
+      "+",
+      paste0("I(N2 * ", x_vars, ")", collapse = "+")
+    )
+
+  #* Scale the train data
+  scaler_data <-
+    train_data[, c("aunit_id", "yield", "N", "N2", x_vars), with = FALSE] %>%
+    melt(id.vars = "aunit_id") %>%
+    nest_by(variable) %>%
+    mutate(scaler = 1 / max(data$value)) %>%
+    data.table() %>%
+    .[, .(variable, scaler)]
+
+  scaled_train_data <-
+    train_data[, c("aunit_id", "yield", "N", "N2", x_vars), with = FALSE] %>%
+    scale_data(., scaler_data)
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Regression
+  # /*+++++++++++++++++++++++++++++++++++
+  feols_formula <-
+    paste0(
+      "yield ~ N + N2 + ",
+      control_vars, "+",
+      int_vars
+    ) %>%
+    formula()
+
+  # === spatial error model ===#
+  ser_res <- spatialreg::errorsarlm(feols_formula, data = scaled_train_data, listw = Wls)
+
+  
+  #************************   RMSR   ***********************
+  e_hat_train <- copy(scaled_train_data) %>% 
+      .[, yield := predict(ser_res, newdata = .) %>% data.frame() %>% pull(trend)] %>%
+      scale_data(., scaler_data, back = TRUE) %>%
+      .[, .(aunit_id, yield)] %>%
+      setnames("yield", "y_hat") %>% 
+      .[train_data, on = "aunit_id"] %>% 
+      .[, e_hat := yield - y_hat] %>% 
+      .[, .(aunit_id, e_hat)] %>%
+      setnames("e_hat", "e_hat_train") 
[…]

### 2022-02-01 Codes/Functions/R/run_sperror_analysis_50.R

@@ -1,0 +1,103 @@
+# /*===========================================================
+#' # GWR analysis
+# /*===========================================================
+# ! Run GWR and do economic analysis
+
+
+run_sperror_analysis_50 <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, Wls) {
+  train_data <- copy(reg_data)
+  test_data <- copy(cv_data$data[[1]])
+
+  control_vars <- paste0(x_vars, collapse = "+")
+  int_vars <-
+    paste0(
+      paste0("I(N * ", x_vars, ")", collapse = "+"),
+      "+",
+      paste0("I(N2 * ", x_vars, ")", collapse = "+")
+    )
+
+  #* Scale the train data
+  scaler_data <-
+    train_data[, c("aunit_id", "yield", "N", "N2", x_vars), with = FALSE] %>%
+    melt(id.vars = "aunit_id") %>%
+    nest_by(variable) %>%
+    mutate(scaler = 1 / max(data$value)) %>%
+    data.table() %>%
+    .[, .(variable, scaler)]
+
+  scaled_train_data <-
+    train_data[, c("aunit_id", "yield", "N", "N2", x_vars), with = FALSE] %>%
+    scale_data(., scaler_data)
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Regression
+  # /*+++++++++++++++++++++++++++++++++++
+  feols_formula <-
+    paste0(
+      "yield ~ N + N2 + ",
+      control_vars, "+",
+      int_vars
+    ) %>%
+    formula()
+
+  # === spatial error model ===#
+  ser_res <- spatialreg::errorsarlm(feols_formula, data = scaled_train_data, listw = Wls)
+
+  
+  #************************   RMSR   ***********************
+  e_hat_train <- copy(scaled_train_data) %>% 
+      .[, yield := predict(ser_res, newdata = .) %>% data.frame() %>% pull(trend)] %>%
+      scale_data(., scaler_data, back = TRUE) %>%
+      .[, .(aunit_id, yield)] %>%
+      setnames("yield", "y_hat") %>% 
+      .[train_data, on = "aunit_id"] %>% 
+      .[, e_hat := yield - y_hat] %>% 
+      .[, .(aunit_id, e_hat)] %>%
+      setnames("e_hat", "e_hat_train") 
[…]

### 2022-02-01 Codes/Functions/R/run_sperror_analysis_500.R

@@ -1,0 +1,103 @@
+# /*===========================================================
+#' # GWR analysis
+# /*===========================================================
+# ! Run GWR and do economic analysis
+
+
+run_sperror_analysis_500 <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, Wls) {
+  train_data <- copy(reg_data)
+  test_data <- copy(cv_data$data[[1]])
+
+  control_vars <- paste0(x_vars, collapse = "+")
+  int_vars <-
+    paste0(
+      paste0("I(N * ", x_vars, ")", collapse = "+"),
+      "+",
+      paste0("I(N2 * ", x_vars, ")", collapse = "+")
+    )
+
+  #* Scale the train data
+  scaler_data <-
+    train_data[, c("aunit_id", "yield", "N", "N2", x_vars), with = FALSE] %>%
+    melt(id.vars = "aunit_id") %>%
+    nest_by(variable) %>%
+    mutate(scaler = 1 / max(data$value)) %>%
+    data.table() %>%
+    .[, .(variable, scaler)]
+
+  scaled_train_data <-
+    train_data[, c("aunit_id", "yield", "N", "N2", x_vars), with = FALSE] %>%
+    scale_data(., scaler_data)
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Regression
+  # /*+++++++++++++++++++++++++++++++++++
+  feols_formula <-
+    paste0(
+      "yield ~ N + N2 + ",
+      control_vars, "+",
+      int_vars
+    ) %>%
+    formula()
+
+  # === spatial error model ===#
+  ser_res <- spatialreg::errorsarlm(feols_formula, data = scaled_train_data, listw = Wls)
+
+  
+  #************************   RMSR   ***********************
+  e_hat_train <- copy(scaled_train_data) %>% 
+      .[, yield := predict(ser_res, newdata = .) %>% data.frame() %>% pull(trend)] %>%
+      scale_data(., scaler_data, back = TRUE) %>%
+      .[, .(aunit_id, yield)] %>%
+      setnames("yield", "y_hat") %>% 
+      .[train_data, on = "aunit_id"] %>% 
+      .[, e_hat := yield - y_hat] %>% 
+      .[, .(aunit_id, e_hat)] %>%
+      setnames("e_hat", "e_hat_train") 
[…]

### 2022-02-01 Codes/_checking_debugging.R

@@ -1,0 +1,360 @@
+
+## Packages
+
+rm(list = ls())
+
+# /*===========================================================
+#' # Preparation
+# /*===========================================================
+#* set up python environment
+library(reticulate)
+
+#* packages
+library(sp)
+library(spdep)
+library(spatialreg)
+library(sf)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(dplyr)
+library(magrittr)
+library(gstat)
+library(GWmodel)
+library(scam)
+library(mgcv)
+library(magic)
+library(stringr)
+library(ggplot2)
+library(tictoc)
+library(here)
+
+#* set working directory
+setwd(here())
+
+#* source all the R functions in the Functions/R folder
+fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
+    purrr::map(~ source(.))
+
+
+# /*===========================================================
+#' # Read data
+# /*===========================================================
+
+#* Read field data
+field_data <-
+    readRDS(here("Data/field_data.rds")) %>%
+    pull(field_sf) 
+
+#* Read field parameters
+field_parameters <- readRDS(here("Data/field_parameters.rds"))
+
+#* Read field data
+field_with_design <- readRDS(here("Data/field_with_design.rds"))
+
+
+#* missing simulations
+profit_ls <- readRDS(here("Results", "profit_ls.rds"))
+sim_id <- profit_ls[[3]]$data[[1]]$sim %>% unique()
+c(501:600)[!501:600 %in% sim_id]
+
+
+
+
+## ---------------------------------
+## Define regression functional form 
+## ---------------------------------
+
+x_vars <-
+    c(
+        "b0_1", "b0_2",
+        "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
+        "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
+        "theta_plateau_1", "theta_plateau_2",
+        "theta_Nk_1", "theta_Nk_2",
+        "theta_b0_1", "theta_b0_2"
+    )
+
+control_vars <- paste0(x_vars, collapse = "+")
+int_vars <-
+    paste0(
+        paste0("I(N * ", x_vars, ")", collapse = "+"),
+        "+",
[…]

### 2022-02-01 Writing/manuscript_gwr.rmd
writing folder created

---
title: "Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
abstract: ""
---

```{r echo = F, cache = F}
suppressMessages(library(knitr))
suppressMessages(library(here))
suppressMessages(library(officedown))
suppressMessages(library(officer))

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = F,
  echo = F,
  fig.cap = TRUE
)
```

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
```

```{r figure_setup, cache = F}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

```{r include = FALSE}
# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================
#* source all the functions in the Functions folder
fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
  lapply(., function(x) source(x))

#* read the results rds file
results <-
  here("Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff]

pi_dif_gwr <-
  results[, .(pi_dif = mean(pi_diff)), by = type] %>%
  .[, diff(pi_dif)]

#* create figures
source(here("Codes", "3_make_figures_publication.R"))
```

**Abstract**: Geographically-weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to generate site-specific input rate recommendations using data generated by on-farm precision experimentation (OFPE). The key objectives of this paper are two-fold. First, it evaluates two sets of functional-form specifications made by two recent published studies of site-specific input management that apply GWR to data from OFPE. We show that one set of functional-form specification performs significantly better than the other. Second, we investigate the possibility of bias when GWR is used to estimate the value of site-specific vs. uniform-rate input management. We show that GWR suffers significant positive bias, which can lead to great over-estimation of the value of applying GWR methods. Our study is the first to systematically examine the statistical and economic properties of the use of GWR in OPFE settings. We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.

**Keywords**: on-farm precision experimentation, site-specific input management, geographically-weighted regression, economically optimal nitrogen rate

**Acknowledgement**: This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled “Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management,” (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled “Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation” (Award Number NR213A7500013G021).

`r run_pagebreak()`

# Introduction

In recent years, On-farm Precision Experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm]. Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods including random forest [@krause2020random] and convolutional neural network [@barbosa2020modeling] approaches. Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.

On any given field, it is typical for U.S. Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths]. The data is often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., Culman, et al. 2020). But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics. For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages. GreenSeeker then basically uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) application rate maps ($R_xs$). Veris Technologies manufactures sensor equipment that can be towed through fields to gather apparent electroconductivity (EC) data, which can be used to infer properties of soil content. The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers. FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.

However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farm profitability remains in question [@gardner2021economic]. Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site specific management recommendations without such data. The study estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data]. @trevisan2021spatial reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates. @rakshit2020 also applied GWR to on-farm experiment data. However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis unlike @trevisan2021spatial. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020 also did not estimate site-specific economically optimal nitrogen rates.

This study has two key objectives. The first is to determine which of the model specifications used by @rakshit2020 and @trevisan2021spatial result in more profitable $R_xs$. While both @rakshit2020 and @trevisan2021spatial proposed using GWR to estimate site-specific yield response functions, they use different model specifications. Both assume a quadratic response of yield to nitrogen rate ($N$). However, while @trevisan2021spatial estimate the coefficient on $N^2$ as a global parameter, @rakshit2020 estimate it locally for each point. At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial. However, the flexibility can be a disadvantage rather than an advantage because the estimation of EONR is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.

Second, we will examine the degree and direction of bias in the estimation of the value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial. In general, researchers take the following steps to estimate the value of VRA based using OFPE data [e.g., @swinton1998evaluating; @bullock2002adding; @anselin2004spatial; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits. However, this approach can result in significant bias in the estimation of the value of VRA because of the assumption made on step (3), which is that the estimated yield response functions are the true yield response functions. @trevisan2021spatial provide an example. At step (3), they used their estimated GWR as the true yield response functions. This assumption is generally unavoidable for researchers since they cannot observe any real field's true yield response function of any real field. Use of these procedures assumes accurate estimation of yield response functions, which when untrue can result in significant bias in the estimation of the value of VRA. This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions. We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.

In the following, we pursue the two objectives just described above by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data. We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions. For the same reason, we cannot test whether @trevisan2021spatial over-estimates the actual value of VRA, either. But in the Monte Carlo simulations we specify yield response functions and generate stylized data from those functions, which enables us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA. Monte Carlo simulations are commonly used in this way to gain insights into the statistical properties of trial designs and estimations methods [@mckinion2001analysis; @gebbers2010application; @bullock2020value; @alesso2021design].

One of the principal findings of this article is that the model specification used by @trevisan2021spatial creates more valuable information than does the model specification used by @rakshit2020. This is primarily due to GWR's poor local estimation of the coefficients on $N^2$. Since the coefficients on $N^2$ is highly influential in determining site-specific EONR, inaccuracy in its estimation can result in significant economic loss. We also show that even under the method used by @trevisan2021spatial, the benefit of VRA over URA is rather small, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial significantly over-estimated that value. Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.

# Materials and Methods

## Experimental Field Layout

Figure \@ref(fig:field-layout) shows the field layout and defines the spatial units of the simulated on-farm precision experiments in this study. The basic spatial unit of the field is the 6m $\times$ 6m "cell", which is the resolution at which the field characteristics data (i.e., parameters of the "true" yield response function) were allowed to vary. It was assumed, however, that yields could not be monitored at such a high resolution. Rather, the mechanical harvester was assumed to be 18m wide, and, in cases in which the N rate was unchanged, in need of harvesting on a run of no less than 12m to provide accurate yield data. Therefore, the yield data's resolution was 18m $\times$ 12m (3 cells $\times$ 2 cells, called a "subplot"). The N rate unit consisted of five "subplots", that is, 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution. A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12 m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.

The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha. Data from the 6-m-wide headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed. In total there were 1440 subplots available for experimental data analysis. The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $k \in {1, \dots , 6}$ identifies the cells within a subplot. The couplet (j, k) is used to identify individual cells.

## True Cell-specific Yield Response Function

An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop]. The quadratic, linear-plateau, quadratic-plateau, and Mitscherlich‐Baule are commonly used functional forms. In this study, each cell (j, k)'s "true" yield response function is assumed to follow the quadratic-plateau functional form:

$$
\begin{equation}
y_{j,k} = f_{j, k} (N) = f(N, c_{j,k}) = 
  \begin{cases}
  \alpha_{j,k} + \beta_{j,k} N + \gamma_{j,k} N^2 + \varepsilon_{j,k} \, ,& N < \tau_{j,k} \\
  \alpha_{j,k} + \beta_{j,k} \tau_{j,k} + \gamma_{j,k} \tau_{j,k}^2 + \varepsilon_{j,k} \, ,& N \ge \tau_{j,k}
  \end{cases}
\end{equation}
$$

where $c_{j,k} = (\alpha_{j,k},\beta_{j,k},\gamma_{j,k},\tau_{j,k})$ is the vector of yield response function parameters. $\tau_{j,k}$ can be interpreted as the critical value of N rate at which cell $(j, k)$'s yield reaches the plateau level (i.e., where yield no longer increases with additional N fertilizer). $\varepsilon_{j, k}$ is a stochastic error term. The quadratic-plateau functional form implies a diminishing marginal product of N and a yield plateau, which are desirable properties for a yield response function [@frank1990comparison]. It is a widely observed corn nitrogen response pattern by existing agronomic studies. Note that the cell-specific yield response function $f_{j, k} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, k}$. In other words, all the soil or field properties that could affect yield response to N are embedded in the simulated parameters.

The spatial distributions of cell-level parameters $\alpha_{j, k}$, $\beta_{j, k}$, $\gamma_{j,k}$, $\tau_{j, k}$, and the error term $\varepsilon_{j, k}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are not spatially correlated. A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, which most real-world N rate recommendations fall into (e.g., @sawyer2018). Note that the range of the optimal N rates of individual rounds of simulations are narrower. In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the DIFM project in 2018 by the Data-Intensive Farm Management Project (DIFM), [@bullock2019data]. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the value of sill variances assigned to the simulations' error terms.

## Trial Design

Figures \@ref(fig:field-layout) and \@ref(fig:field-N-design) illustrate the Latin square trial design schema assumed in each simulation. The field was partitioned into a 4-block $\times$ 2-block grid, in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block. The design ensured that no adjacent N plots were assigned the same N rate. Furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due the technological limitations of N application equipment commonly witnessed in real-world OFPE).

Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, k)$ was calculated as

$$
N^*_{j,k} \equiv argmax_N \Big[p\cdot f_{j,k}(N)-w\cdot N\Big].
$$

In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific optimal N rates. The means of these trial N rates across simulations were approximately, {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$.

## Yield Data Generation

In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon\_{j,k}$. This procedure generated a field-level, cell-specific data set, $\{(y_{j, k},N_{j, k} ):j=1,\dots,1440;k=1,\dots, 6 \}$. To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution. Since every cell in a plot received the same N application rate, then so did every cell within a subplot, so $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$. Letting $\mu_j$ denote the mean of the yields of the cells in subplot $j$, the analysis of each round's data was based on 1440 $(\mu_j,N_j )$ observations.

## Estimation of Yield Response Function and EONR

Three approaches to estimate yield response functions and their associated EONRs were used. The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and to estimate and economically optimal uniform nitrogen application rate for the field. The other two approaches both used GWR, but assumed different specifications in modeling the impact of nitrogen on yield. The first GWR approach (GWR-R) followed the specification used by @rakshit2020, and the second GWR approach (GWR-T) followed the specification used by @trevisan2021spatial. Further details of each approach are presented below. SCAM and GWR estimations were performed using $R$'s scam [@scam-R] and GWmodel [@gwmodel-R] packages.

### Spatially Uniform Management after Non-Spatial Regression Analysis of OFPE Data

In the lower benchmark situation, a researcher was assumed to run OFPEs to gather data, then to estimate a single "full-field" yield response function using the SCAM non-parametric regression framework, which is a spline-based series estimation that can impose a shape-constraints on the estimated function [@pya2015shape]. In using SCAM, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research. When the chosen shape constraints are correct, SCAM is more statistically efficient than a fully non-parametric regression [@pya2015shape]. The estimated model is represented mathematically as follows,

$$y_j = \alpha + \sum_{l=1}^l \beta_l g_l(N_j)+ \varepsilon_j$$

where $g_l(\cdot)$ is the $l$th spline basis and $\beta_l$ is its coefficient to be estimated. The $\beta_l$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases as $N_j$ increases, but at a diminishing rate.

Let $\hat{f}_{scam}(\cdot)$ represent the estimated whole-yield yield response function ($\sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$). Given the information derived from the SCAM approach, the estimate of the economically optimal uniform N rate is,

$$\hat{N}_{scam}^* \equiv argmax_N⁡ \big[p\cdot \hat{f}_{scam} (N)-w\cdot N\big]$$

### GWR-Rakshit (GWR-R)

In the GWR-R approach, yield response was modeled as subplot-specific quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,

$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \epsilon_j$$

The GWR-R estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}_{gwr-r,j}(N)$ for $j = 1, 2, \dots, 1440$. The estimated economically optimal N application rate for subplot $j$ was calculated by solving the subplot's profit maximization problem:

$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN]$$.

### GWR-Trevisan (GWR-T)

In the GWR-T approach, unlike GWR-Rakshit, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically. For each subplot $j \in {1, 2, \dots, 1440}$, the assumed yield response was,

$$y_j= \alpha_j+ \beta N_j + \eta N_j^2+ \epsilon_j$$.

where $\eta$ was assumed invariant among subplots. Because the coefficients on some variables were estimated as global parameters, the model used can be classified as a Mixed GWR model.

Let $\hat{f}_{gwr-t,j}(N)$ for $j = 1, 2, \dots, 1440$ denote the estimated yield response function for subplot $j$. The estimated economically optimal N application rate for subplot $j$ was then,

$$\hat{N}^*_{gwr-t,j} \equiv argmax_N⁡[p\hat{f}_{gwr-t,j} (N) -wN]$$.

## The value of GWR-based VRA over scam-based URA

To estimate the bias in the estimation of the value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the "true" yield response functions. Profits from the SCAM approach were

$$\Pi_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$

where $f_{j, k}(\cdot)$ denotes the true yield response function at cell $(j, k)$.

For $m = R, T$, the true per-ha net revenues ("profits") resulting from applying the profit-maximizing cell-specific N rate plan estimated by GWR-m were,

$$\Pi_{gwr-m}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}_{gwr-m, j}^*)-w\hat{N}_{gwr-m,j}^*]$$

where $f_{j, k} (\hat{N}_{gwr-j}^*)$ denote the true yield generated at cell $(j, k)$ with subplot $l$'s N rate.

The true value of the GWR-based VRA compared to the SCAM-based URA is defined by the difference of their partial profits:

$\Delta_{gwr-m} = \Pi_{gwr-m} - \Pi_{scam}$

To find the bias in estimating the value of VRA, the "estimated" profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR. Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:

$$\hat{\Pi}_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{gwr}_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$

$$\hat{\Pi}_{gwr-m}^*=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{gwr-m}_{j, k} (\hat{N}_{gwr-m}^{j*} )-w\hat{N}_{gwr-m}^{j*}]$$

The estimated value of the GWR-based VRA compared to the SCAM-based URA is defined as

$$\hat{\Delta}_{gwr-m} = \hat{\Pi}_{gwr-m}^* - \hat{\Pi}_{scam}^*$$

Finally, the bias in the estimation of the value of GWR-based VRA was calculated as follows:

$$bias = \hat{\Delta}_{gwr-m} - \Delta_{gwr-m}$$

# Results

## Comparing the values of GWR-based VRA and SCAM-based URA

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA. The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA. This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations. Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round. Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property. The result is consistent with the bottom panel of Figure 12 in @rakshit2020. Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach. Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.

The GWR-T approach, however, performed better than SCAM-URA in majority of cases, with some cases showing values-added exceeding \$10 ha$^{-1}$. This may seem surprising as the model estimated in the GWR-T approach is more restrictive than that in the GWR-R approach because the coefficient on $N^2$ is assumed to be global. However, unlike GWR-R, this restriction helps avoid estimating positive subplot-level coefficients on $N^2$. This result implies that the value of avoiding highly unreliable estimates of coefficients on $N^2$ subplot-specifically was greater than loss of local flexibility in the coefficients on $N^2$.

## Bias in the estimation of the value of GWR-based VRA

Next we examine the bias in the "estimated" value of GWR-based VRA that researchers would encounter using real data. Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in "estimated" profit between the GWR-based VRA and SCAM-based URA. Unlike the true difference in profit, VRA based on GWR-R appears to perform overwhelmingly better, with its average profit about \$`r round(pi_dif_gwr, digits = 2)` ha$^{-1}$ greater than that of the SCAM-based URA. That is, researchers would tend to significantly over-estimate the value of VRA based on GWR-R. When the GWR estimates are considered to define true yield response, the inaccuracy of GWR-R generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWR-R itself. Under GWR-T, the bias is more than \$10 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 10)] * 100` % of the simulation cases: under GWR-R, that bias is greater than \$10 ha$^{-1}$ in `r results[type == "GWR-R", mean(abs(bias) > 10)] * 100` % of the simulated cases. However, as can be seen in the bottom panel of Figure \@ref(fig:bias-est-pi), the distribution of bias from GWR-T has a fatter tail than GWR-R with more mass on higher bias values. Bias is more than \$50 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 50)] * 100` % of the simulation cases for GWR-T as opposed to `r results[type == "GWR-R", mean(abs(bias) > 50)] * 100` % for GWR-R.

Figure \@ref(fig:why-bias-many) illustrates how over-estimations can occur. It shows yield response functions estimated by GWR-T and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation. Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform better the SCAM-based estimates in every cell. For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in a yield far lower because of the quadratic functional form assumption. Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)). The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and then yield declines afterward. In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about $0.25$ ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b). Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ more profitable than applying the SCAM-based recommendation. This profit differential comes soley from the difference in nitrogen cost since GWR and SCAM yields are equal. However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to be about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$ greater than from the SCAM-based recommendation. Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR.

# Discussions

Our results on the relative performance of GWR-T and GWR-R show clearly that GWR-T performs better than GWR-R, and GWR-T should be used when researchers employ a GWR-based approach to find site-specific input recommendations. These findings, however, have important implications beyond just GWR-R and GWR-T. An obvious extension of the parametric GWR approaches would be a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM). However, such a method is likely to encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally.

It is important to be aware that researchers need to be extremely cautious about their estimated value of VRA based on GWR whether they follow GWR-R or GWR-T. Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high at the non-negligible probability. Extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias. Indeed, the bias problem we raised here is likely to be observed for other statistical methods because the bias comes from the assumption that the _estimated_ yield response functions are true. Whatever the underlying statistical method for yield response functions may be, researchers are likely to overestimate the true value of their methods. It would be an interesting future research to investigate the bias in other major statistical methods that are commonly used in the literature.

# Conclusions

This articles examined the value of GWR-based VRA and the bias in its estimation in the context of OFPE. We showed that restricting the coefficient on $N^2$ to a global parameter as done in @trevisan2021spatial leads to site-specific nitrogen rate recommendations with higher profits compared to the specification used by @rakshit2020, which allows the coefficients on $N^2$ to vary locally. However, we also found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations. It can be concluded that researchers need to be cautious about promoting the GWR-based approach.

A fruitful extension of GWR-based approach would be to employ more flexible yield reponse model specifications. This study has shown the assumed quadratic functional form to be the main culprit of the significant over-estimation of the value of GWR-based VRA. Applying GWR with a quadratic-plateau or linear-plateau specifications might substantially alleviate the reported bias problem.

`r run_pagebreak()`

# Figures

```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.dim = c(6, 6)}
g_layout
```

```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates"}
g_exp
```

```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
g_value
```

```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients"}
g_comp_coef
```

```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of Estimated and True EONR"}
g_comp_eonr
```

```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
g_bias
```

```{r fig.id = "why-bias-many", fig.cap = "The cause of significant over-estimation of the value of GWR-based VRA"}
g_why_bias_many
```

```{r fig.id = "why-bias-single", fig.cap = "An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA",fig.dim = c(6, 7)}
g_why_bias_single
```

`r run_pagebreak()`

# References

<br />

<div id="refs"></div>

### 2022-02-01 Writing/manuscript_gwr.rmd
Update manuscript_gwr.rmd

@@
 ---
-title: "Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management"
+title: "New"
 author:

### 2022-02-01 Writing/manuscript_gwr.rmd
rmd template added

@@
 
-**Abstract**: Geographically-weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to generate site-specific input rate recommendations using data generated by on-farm precision experimentation (OFPE).
-The key objectives of this paper are two-fold.
-First, it evaluates two sets of functional-form specifications made by two recent published studies of site-specific input management that apply GWR to data from OFPE.
-We show that one set of functional-form specification performs significantly better than the other.
-Second, we investigate the possibility of bias when GWR is used to estimate the value of site-specific vs.
-uniform-rate input management.
-We show that GWR suffers significant positive bias, which can lead to great over-estimation of the value of applying GWR methods.
-Our study is the first to systematically examine the statistical and economic properties of the use of GWR in OPFE settings.
-We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
+**Abstract**:
 
-**Keywords**: on-farm precision experimentation, site-specific input management, geographically-weighted regression, economically optimal nitrogen rate
+**Keywords**:
 
@@
 
-In recent years, On-farm Precision Experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm].
-Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods including random forest [@krause2020random] and convolutional neural network [@barbosa2020modeling] approaches.
-Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.
-
-On any given field, it is typical for U.S.
-Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
-The data is often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., Culman, et al.
-2020).
-But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics.
-For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
-GreenSeeker then basically uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) application rate maps ($R_xs$).
-Veris Technologies manufactures sensor equipment that can be towed through fields to gather apparent electroconductivity (EC) data, which can be used to infer properties of soil content.
-The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers.
-FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.
-
-However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farm profitability remains in question [@gardner2021economic].
-Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site specific management recommendations without such data.
-The study estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data].
-@trevisan2021spatial reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-@rakshit2020 also applied GWR to on-farm experiment data.
-However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis unlike @trevisan2021spatial.
-@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020 also did not estimate site-specific economically optimal nitrogen rates.
-
-This study has two key objectives.
-The first is to determine which of the model specifications used by @rakshit2020 and @trevisan2021spatial result in more profitable $R_xs$.
-While both @rakshit2020 and @trevisan2021spatial proposed using GWR to estimate site-specific yield response functions, they use different model specifications.
-Both assume a quadratic response of yield to nitrogen rate ($N$).
-However, while @trevisan2021spatial estimate the coefficient on $N^2$ as a global parameter, @rakshit2020 estimate it locally for each point.
-At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial.
-However, the flexibility can be a disadvantage rather than an advantage because the estimation of EONR is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.
-
-Second, we will examine the degree and direction of bias in the estimation of the value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial.
-In general, researchers take the following steps to estimate the value of VRA based using OFPE data [e.g., @swinton1998evaluating; @bullock2002adding; @anselin2004spatial; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
-However, this approach can result in significant bias in the estimation of the value of VRA because of the assumption made on step (3), which is that the estimated yield response functions are the true yield response functions.
-@trevisan2021spatial provide an example.
-At step (3), they used their estimated GWR as the true yield response functions.
-This assumption is generally unavoidable for researchers since they cannot observe any real field's true yield response function of any real field.
-Use of these procedures assumes accurate estimation of yield response functions, which when untrue can result in significant bias in the estimation of the value of VRA.
-This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions.
-We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.
-
-In the following, we pursue the two objectives just described above by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data.
-We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions.
-For the same reason, we cannot test whether @trevisan2021spatial over-estimates the actual value of VRA, either.
-But in the Monte Carlo simulations we specify yield response functions and generate stylized data from those functions, which enables us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA.
-Monte Carlo simulations are commonly used in this way to gain insights into the statistical properties of trial designs and estimations methods [@mckinion2001analysis; @gebbers2010application; @bullock2020value; @alesso2021design].
-
-One of the principal findings of this article is that the model specification used by @trevisan2021spatial creates more valuable information than does the model specification used by @rakshit2020.
-This is primarily due to GWR's poor local estimation of the coefficients on $N^2$.
-Since the coefficients on $N^2$ is highly influential in determining site-specific EONR, inaccuracy in its estimation can result in significant economic loss.
-We also show that even under the method used by @trevisan2021spatial, the benefit of VRA over URA is rather small, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial significantly over-estimated that value.
-Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.
-
-# Materials and Methods
-
-## Experimental Field Layout
-
-Figure \@ref(fig:field-layout) shows the field layout and defines the spatial units of the simulated on-farm precision experiments in this study.
-The basic spatial unit of the field is the 6m $\times$ 6m "cell", which is the resolution at which the field characteristics data (i.e., parameters of the "true" yield response function) were allowed to vary.
-It was assumed, however, that yields could not be monitored at such a high resolution.
-Rather, the mechanical harvester was assumed to be 18m wide, and, in cases in which the N rate was unchanged, in need of harvesting on a run of no less than 12m to provide accurate yield data.
-Therefore, the yield data's resolution was 18m $\times$ 12m (3 cells $\times$ 2 cells, called a "subplot").
-The N rate unit consisted of five "subplots", that is, 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
-A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12 m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
-
-The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha.
-Data from the 6-m-wide headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed.
-In total there were 1440 subplots available for experimental data analysis.
-The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $k \in {1, \dots , 6}$ identifies the cells within a subplot.
-The couplet (j, k) is used to identify individual cells.
-
-## True Cell-specific Yield Response Function
-
-An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-The quadratic, linear-plateau, quadratic-plateau, and Mitscherlich‐Baule are commonly used functional forms.
-In this study, each cell (j, k)'s "true" yield response function is assumed to follow the quadratic-plateau functional form:
-
-$$
-\begin{equation}
-y_{j,k} = f_{j, k} (N) = f(N, c_{j,k}) = 
-  \begin{cases}
-  \alpha_{j,k} + \beta_{j,k} N + \gamma_{j,k} N^2 + \varepsilon_{j,k} \, ,& N < \tau_{j,k} \\
-  \alpha_{j,k} + \beta_{j,k} \tau_{j,k} + \gamma_{j,k} \tau_{j,k}^2 + \varepsilon_{j,k} \, ,& N \ge \tau_{j,k}
-  \end{cases}
-\end{equation}
-$$
-
-where $c_{j,k} = (\alpha_{j,k},\beta_{j,k},\gamma_{j,k},\tau_{j,k})$ is the vector of yield response function parameters.
-$\tau_{j,k}$ can be interpreted as the critical value of N rate at which cell $(j, k)$'s yield reaches the plateau level (i.e., where yield no longer increases with additional N fertilizer).
-$\varepsilon_{j, k}$ is a stochastic error term.
-The quadratic-plateau functional form implies a diminishing marginal product of N and a yield plateau, which are desirable properties for a yield response function [@frank1990comparison].
-It is a widely observed corn nitrogen response pattern by existing agronomic studies.
-Note that the cell-specific yield response function $f_{j, k} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, k}$.
-In other words, all the soil or field properties that could affect yield response to N are embedded in the simulated parameters.
-
-The spatial distributions of cell-level parameters $\alpha_{j, k}$, $\beta_{j, k}$, $\gamma_{j,k}$, $\tau_{j, k}$, and the error term $\varepsilon_{j, k}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16].
-Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters.
-The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical).
-The range of 600m means that observations separated by more than 600m are not spatially correlated.
-A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells.
-The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, which most real-world N rate recommendations fall into (e.g., @sawyer2018).
-Note that the range of the optimal N rates of individual rounds of simulations are narrower.
-In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the DIFM project in 2018 by the Data-Intensive Farm Management Project (DIFM), [@bullock2019data].
-Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated.
-The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the value of sill variances assigned to the simulations' error terms.
-
-## Trial Design
-
-Figures \@ref(fig:field-layout) and \@ref(fig:field-N-design) illustrate the Latin square trial design schema assumed in each simulation.
-The field was partitioned into a 4-block $\times$ 2-block grid, in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block.
-The design ensured that no adjacent N plots were assigned the same N rate.
-Furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due the technological limitations of N application equipment commonly witnessed in real-world OFPE).
-
-Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, k)$ was calculated as
-
-$$
-N^*_{j,k} \equiv argmax_N \Big[p\cdot f_{j,k}(N)-w\cdot N\Big].
-$$
-
-In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific optimal N rates.
-The means of these trial N rates across simulations were approximately, {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$.
-
-## Yield Data Generation
-
-In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon\_{j,k}$.
-This procedure generated a field-level, cell-specific data set, $\{(y_{j, k},N_{j, k} ):j=1,\dots,1440;k=1,\dots, 6 \}$.
-To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution.
-Since every cell in a plot received the same N application rate, then so did every cell within a subplot, so $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$.
-Letting $\mu_j$ denote the mean of the yields of the cells in subplot $j$, the analysis of each round's data was based on 1440 $(\mu_j,N_j )$ observations.
-
-## Estimation of Yield Response Function and EONR
-
-Three approaches to estimate yield response functions and their associated EONRs were used.
-The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and to estimate and economically optimal uniform nitrogen application rate for the field.
-The other two approaches both used GWR, but assumed different specifications in modeling the impact of nitrogen on yield.
-The first GWR approach (GWR-R) followed the specification used by @rakshit2020, and the second GWR approach (GWR-T) followed the specification used by @trevisan2021spatial.
-Further details of each approach are presented below.
-SCAM and GWR estimations were performed using $R$'s scam [@scam-R] and GWmodel [@gwmodel-R] packages.
-
-### Spatially Uniform Management after Non-Spatial Regression Analysis of OFPE Data
-
-In the lower benchmark situation, a researcher was assumed to run OFPEs to gather data, then to estimate a single "full-field" yield response function using the SCAM non-parametric regression framework, which is a spline-based series estimation that can impose a shape-constraints on the estimated function [@pya2015shape].
-In using SCAM, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research.
-When the chosen shape constraints are correct, SCAM is more statistically efficient than a fully non-parametric regression [@pya2015shape].
-The estimated model is represented mathematically as follows,
-
-$$y_j = \alpha + \sum_{l=1}^l \beta_l g_l(N_j)+ \varepsilon_j$$
-
-where $g_l(\cdot)$ is the $l$th spline basis and $\beta_l$ is its coefficient to be estimated.
-The $\beta_l$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases as $N_j$ increases, but at a diminishing rate.
-
-Let $\hat{f}_{scam}(\cdot)$ represent the estimated whole-yield yield response function ($\sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$).
-Given the information derived from the SCAM approach, the estimate of the economically optimal uniform N rate is,
-
-$$\hat{N}_{scam}^* \equiv argmax_N⁡ \big[p\cdot \hat{f}_{scam} (N)-w\cdot N\big]$$
-
-### GWR-Rakshit (GWR-R)
-
-In the GWR-R approach, yield response was modeled as subplot-specific quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
-
-$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \epsilon_j$$
-
-The GWR-R estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}_{gwr-r,j}(N)$ for $j = 1, 2, \dots, 1440$.
-The estimated economically optimal N application rate for subplot $j$ was calculated by solving the subplot's profit maximization problem:
-
-$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN]$$.
-
-### GWR-Trevisan (GWR-T)
-
-In the GWR-T approach, unlike GWR-Rakshit, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically.
-For each subplot $j \in {1, 2, \dots, 1440}$, the assumed yield response was,
-
-$$y_j= \alpha_j+ \beta N_j + \eta N_j^2+ \epsilon_j$$.
-
-where $\eta$ was assumed invariant among subplots. Because the coefficients on some variables were estimated as global parameters, the model used can be classified as a Mixed GWR model.
-
-Let $\hat{f}_{gwr-t,j}(N)$ for $j = 1, 2, \dots, 1440$ denote the estimated yield response function for subplot $j$. The estimated economically optimal N application rate for subplot $j$ was then,
-
-$$\hat{N}^*_{gwr-t,j} \equiv argmax_N⁡[p\hat{f}_{gwr-t,j} (N) -wN]$$.
-
-## The value of GWR-based VRA over scam-based URA
-
-To estimate the bias in the estimation of the value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the "true" yield response functions.
-Profits from the SCAM approach were
-
-$$\Pi_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$
-
-where $f_{j, k}(\cdot)$ denotes the true yield response function at cell $(j, k)$.
-
-For $m = R, T$, the true per-ha net revenues ("profits") resulting from applying the profit-maximizing cell-specific N rate plan estimated by GWR-m were,
-
-$$\Pi_{gwr-m}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}_{gwr-m, j}^*)-w\hat{N}_{gwr-m,j}^*]$$
-
-where $f_{j, k} (\hat{N}_{gwr-j}^*)$ denote the true yield generated at cell $(j, k)$ with subplot $l$'s N rate.
-
-The true value of the GWR-based VRA compared to the SCAM-based URA is defined by the difference of their partial profits:
-
-$\Delta_{gwr-m} = \Pi_{gwr-m} - \Pi_{scam}$
-
-To find the bias in estimating the value of VRA, the "estimated" profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
-Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:
-
-$$\hat{\Pi}_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{gwr}_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$
-
-$$\hat{\Pi}_{gwr-m}^*=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{gwr-m}_{j, k} (\hat{N}_{gwr-m}^{j*} )-w\hat{N}_{gwr-m}^{j*}]$$
-
-The estimated value of the GWR-based VRA compared to the SCAM-based URA is defined as
-
-$$\hat{\Delta}_{gwr-m} = \hat{\Pi}_{gwr-m}^* - \hat{\Pi}_{scam}^*$$
-
-Finally, the bias in the estimation of the value of GWR-based VRA was calculated as follows:
-
-$$bias = \hat{\Delta}_{gwr-m} - \Delta_{gwr-m}$$
+# Methods
 
@@
 
-## Comparing the values of GWR-based VRA and SCAM-based URA
-
-Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA.
-The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA.
-This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations.
-Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round.
-Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property.
-The result is consistent with the bottom panel of Figure 12 in @rakshit2020.
-Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach.
-Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.
-
-The GWR-T approach, however, performed better than SCAM-URA in majority of cases, with some cases showing values-added exceeding \$10 ha$^{-1}$.
-This may seem surprising as the model estimated in the GWR-T approach is more restrictive than that in the GWR-R approach because the coefficient on $N^2$ is assumed to be global.
-However, unlike GWR-R, this restriction helps avoid estimating positive subplot-level coefficients on $N^2$.
-This result implies that the value of avoiding highly unreliable estimates of coefficients on $N^2$ subplot-specifically was greater than loss of local flexibility in the coefficients on $N^2$.
-
-## Bias in the estimation of the value of GWR-based VRA
-
-Next we examine the bias in the "estimated" value of GWR-based VRA that researchers would encounter using real data.
-Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in "estimated" profit between the GWR-based VRA and SCAM-based URA.
-Unlike the true difference in profit, VRA based on GWR-R appears to perform overwhelmingly better, with its average profit about \$`r round(pi_dif_gwr, digits = 2)` ha$^{-1}$ greater than that of the SCAM-based URA.
-That is, researchers would tend to significantly over-estimate the value of VRA based on GWR-R.
-When the GWR estimates are considered to define true yield response, the inaccuracy of GWR-R generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWR-R itself.
-Under GWR-T, the bias is more than \$10 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 10)] * 100` % of the simulation cases: under GWR-R, that bias is greater than \$10 ha$^{-1}$ in `r results[type == "GWR-R", mean(abs(bias) > 10)] * 100` % of the simulated cases.
-However, as can be seen in the bottom panel of Figure \@ref(fig:bias-est-pi), the distribution of bias from GWR-T has a fatter tail than GWR-R with more mass on higher bias values.
-Bias is more than \$50 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 50)] * 100` % of the simulation cases for GWR-T as opposed to `r results[type == "GWR-R", mean(abs(bias) > 50)] * 100` % for GWR-R.
-
-Figure \@ref(fig:why-bias-many) illustrates how over-estimations can occur.
-It shows yield response functions estimated by GWR-T and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation.
-Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform better the SCAM-based estimates in every cell.
-For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in a yield far lower because of the quadratic functional form assumption.
-Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)).
-The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and then yield declines afterward.
-In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about $0.25$ ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b).
-Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ more profitable than applying the SCAM-based recommendation.
-This profit differential comes soley from the difference in nitrogen cost since GWR and SCAM yields are equal.
-However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to be about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$ greater than from the SCAM-based recommendation.
-Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR.
-
 # Discussions
 
-Our results on the relative performance of GWR-T and GWR-R show clearly that GWR-T performs better than GWR-R, and GWR-T should be used when researchers employ a GWR-based approach to find site-specific input recommendations.
-These findings, however, have important implications beyond just GWR-R and GWR-T.
-An obvious extension of the parametric GWR approaches would be a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
-However, such a method is likely to encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally.
+`r run_pagebreak()`
 
-It is important to be aware that researchers need to be extremely cautious about their estimated value of VRA based on GWR whether they follow GWR-R or GWR-T.
-Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high at the non-negligible probability.
-Extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias.
-Indeed, the bias problem we raised here is likely to be observed for other statistical methods because the bias comes from the assumption that the _estimated_ yield response functions are true.
-Whatever the underlying statistical method for yield response functions may be, researchers are likely to overestimate the true value of their methods.
-It would be an interesting future research to investigate the bias in other major statistical methods that are commonly used in the literature.
-
-# Conclusions
-
-This articles examined the value of GWR-based VRA and the bias in its estimation in the context of OFPE.
-We showed that restricting the coefficient on $N^2$ to a global parameter as done in @trevisan2021spatial leads to site-specific nitrogen rate recommendations with higher profits compared to the specification used by @rakshit2020, which allows the coefficients on $N^2$ to vary locally.
-However, we also found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations.
-It can be concluded that researchers need to be cautious about promoting the GWR-based approach.
-
-A fruitful extension of GWR-based approach would be to employ more flexible yield reponse model specifications.
-This study has shown the assumed quadratic functional form to be the main culprit of the significant over-estimation of the value of GWR-based VRA.
-Applying GWR with a quadratic-plateau or linear-plateau specifications might substantially alleviate the reported bias problem.
+# Tables
 
@@
 # Figures
-
-```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.dim = c(6, 6)}
-g_layout
-```
-
-```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates"}
-g_exp
-```
-
-```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
-g_value
-```
-
-```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients"}
-g_comp_coef
-```
-
-```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of Estimated and True EONR"}
-g_comp_eonr
-```
-
-```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
-g_bias
-```
-
-```{r fig.id = "why-bias-many", fig.cap = "The cause of significant over-estimation of the value of GWR-based VRA"}
-g_why_bias_many
-```
-
-```{r fig.id = "why-bias-single", fig.cap = "An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA",fig.dim = c(6, 7)}
-g_why_bias_single
-```
 

### 2022-02-01 Writing/manuscript.rmd
modify

--- 2022-02-01 Writing/manuscript_gwr.rmd
@@
 bibliography: PA.bib
-csl: field-crops-research.csl
+csl: american-journal-of-agricultural-economics.csl
 abstract: ""
@@
 #* source all the functions in the Functions folder
-fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
-  lapply(., function(x) source(x))
-
-#* read the results rds file
-results <-
-  here("Results", "pi_data.rds") %>%
-  readRDS() %>%
-  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
-  .[, bias := pi_diff_est - pi_diff]
-
-pi_dif_gwr <-
-  results[, .(pi_dif = mean(pi_diff)), by = type] %>%
-  .[, diff(pi_dif)]
-
-#* create figures
-source(here("Codes", "3_make_figures_publication.R"))
+# fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
+#   lapply(., function(x) source(x))
+# 
+# #* read the results rds file
+# results <-
+#   here("Results", "pi_data.rds") %>%
+#   readRDS() %>%
+#   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
+#   .[, bias := pi_diff_est - pi_diff]
+# 
+# pi_dif_gwr <-
+#   results[, .(pi_dif = mean(pi_diff)), by = type] %>%
+#   .[, diff(pi_dif)]
+# 
+# #* create figures
+# source(here("Codes", "3_make_figures_publication.R"))
 ```
@@
 # Methods
+
+## results 1
 
@@
 # References
-
-<br />
-
-<div id="refs"></div>

### 2022-02-01 Writing/knit.R
updated files

@@ -1,0 +1,2 @@
+library(rmarkdown)
+render(here::here("GitControlled/Writing/manuscript_gwr.rmd"))

### 2022-02-01 Writing/knit.R
minor fixes

@@ -1,2 +1,2 @@
 library(rmarkdown)
-render(here::here("GitControlled/Writing/manuscript_gwr.rmd"))
+render(here::here("GitControlled/Writing/manuscript.rmd"))

### 2022-02-01 Codes/1_geo_ml_simulation.rmd
modified BRF analysis by adding interaction terms

@@
 #* source all the R functions in the Functions/R folder
-fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
+fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
   purrr::map(~ source(.))
 
-#* source all the python functions in the Functions/Python folder
-# source_python(here("Codes", "Functions", "Python"))
-# source_python(here("Codes", "Functions", "Python", "run_DML_OF.py"))
-# source_python(here("Codes", "Functions", "Python", "run_DR_OF.py"))
-# source_python(here("Codes", "Functions", "Python", "run_DML_OF_c.py"))
 ```
@@
 field_data <-
-  readRDS(here("Data/field_data.rds")) %>% .[sce_i, ] %>% 
+  readRDS(here("Shared/Data/field_data.rds")) %>%
+  .[sce_i, ] %>%
   pull(field_sf) %>%
@@
 #* Read field parameters
-field_parameters <- readRDS(here("Data/field_parameters.rds")) %>% .[sce_i, ]
+field_parameters <- readRDS(here("Shared/Data/field_parameters.rds")) %>% .[sce_i, ]
 
@@
 #* Read field data
-field_with_design <- readRDS(here("Data/field_with_design.rds")) %>% .[sce_i, ]
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds")) %>% .[sce_i, ]
 
@@
 D <- matrix(NA, nrow(dt), nrow(dt)) # distance matrix
-  for (i in 1:nrow(dt)){
-      for(j in 1:nrow(dt)){
-          D[i,j] <- sqrt((dt$X[i] - dt$X[j])^2+
-                             (dt$Y[i] - dt$Y[j])^2 )
+for (i in 1:nrow(dt)) {
+  for (j in 1:nrow(dt)) {
+    D[i, j] <- sqrt((dt$X[i] - dt$X[j])^2 +
+      (dt$Y[i] - dt$Y[j])^2)
   }
 }
-  W <- 1/D^2             # inverse distance weights matrix
+W <- 1 / D^2 # inverse distance weights matrix
 diag(W) <- 0
-  W <- W/rowSums(W)			    # row-standardize
+W <- W / rowSums(W) # row-standardize
 Wls <- mat2listw(W) # "listw" object
-  saveRDS(Wls, file=here("Data","Wls.rds"))
+saveRDS(Wls, file = here("Data", "Wls.rds"))
 #   #*****************************************************************************

### 2022-02-01 Codes/Functions/R/run_brf_analysis.R

@@ -5,14 +5,31 @@
 
 
 run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
-  data <- copy(reg_data)
+  train_data <- copy(reg_data)
+  test_data <- copy(cv_data$data[[1]])
 
-  X <-
-    data[, c("N", x_vars), with = FALSE] %>%
-    data.frame()
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Define X
+  # /*+++++++++++++++++++++++++++++++++++
+  int_var_names <- paste0("N_", x_vars)
+  int_var_exp <- paste0("= N * ", x_vars)
+  int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")
 
-  Y <- data[, yield]
+  all_X_vars <- c("N", x_vars, int_var_names)
 
+  eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+  eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+
+  X <- train_data[, ..all_X_vars]
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Define Y
+  # /*+++++++++++++++++++++++++++++++++++
+  Y <- train_data[, yield]
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Run BRF
+  # /*+++++++++++++++++++++++++++++++++++
   BRF_temp <-
     grf::boosted_regression_forest(
       X = X,
@@ -23,20 +40,20 @@ run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
     )
 
   #************************   RMSR   ***********************
-  e_hat_train <- copy(data) %>%
-    .[, y_hat := predict(BRF_temp,
-      newdata = .[, c("N", x_vars), with = FALSE]
-    )] %>%
+  e_hat_train <-
+    train_data %>%
+    .[, y_hat := predict(BRF_temp, newdata = .[, all_X_vars, with = FALSE])] %>%
     .[, e_hat := yield - y_hat] %>%
     .[, .(aunit_id, e_hat)] %>%
     setnames("e_hat", "e_hat_train")
-  e_hat_cv <- copy(cv_data$data[[1]]) %>%
-    .[, y_hat := predict(BRF_temp,
[…]

### 2022-02-02 Codes/Functions/R/run_brf_analysis.R
update

@@ -5,6 +5,9 @@
 
 
 run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
+  
+    
+    
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
 

### 2022-02-02 Codes/Functions/R/run_brf_analysis.R
updates

@@ -5,11 +5,9 @@
 
 
 run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
-  
-    
-    
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
+
 
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define X

### 2022-02-02 Codes/Functions/R/run_brf_analysis.R
fixed error in brf analysis

@@ -59,7 +59,7 @@ run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
 
   N_seq <-
     data.table(
-      N = seq(min(data$N), max(data$N), by = 2)
+      N = seq(min(train_data$N), max(train_data$N), by = 2)
     )
 
   brf_results <-

### 2022-02-02 Codes/0_prepare_data.R
update file name path

@@ -28,7 +28,7 @@ setwd(here())
 
 # === load functions ===#
 #* source all the functions in the Functions folder
-fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
+fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
   lapply(., function(x) source(x))
 
 # /*===========================================================
@@ -70,12 +70,12 @@ field_data <-
   ))
 
 #* save the fields
-saveRDS(field_data, here("Data/field_data.rds"))
+saveRDS(field_data, here("Shared/Data/field_data.rds"))
 
 # /*===========================================================
 #' # Add trial design layout
 # /*===========================================================
-field_data <- readRDS(here("Data/field_data.rds"))
+field_data <- readRDS(here("Shared/Data/field_data.rds"))
 
 #* (use the fixed Latin Square design)
 field_with_design <-
@@ -108,17 +108,17 @@ field_with_design <-
         stringr::str_replace_all(design_name, " ", ""),
         "_", field_col, ".rds"
       ) %>%
-        paste0("Data/", .)
+        paste0("Shared/Data/", .)
   )
 
 #* save the fields with designs
-saveRDS(field_with_design, here("Data/field_with_design.rds"))
+saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))
 
 
 # /*===========================================================
 #' # Add spatial weights matrix
 # /*===========================================================
-field_with_design <- readRDS(here("Data/field_with_design.rds"))
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 
 field_with_design <-
     field_with_design %>%
@@ -135,18 +135,18 @@ field_with_design <-
     ) 
 
 #* save the fields with weights matrix
-saveRDS(field_with_design, here("Data/field_with_design.rds"))
+saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))
 
 
 # /*===========================================================
 #' # Generate true field parameters
 # /*===========================================================
-field_with_design <- readRDS(here("Data/field_with_design.rds"))
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 
 set.seed(243730)
 
 field_parameters <-
-  readRDS(here("Data/field_data.rds")) %>%
+  readRDS(here("Shared/Data/field_data.rds")) %>%
   mutate(field_pars = list(
     gen_field_pars(
[…]

### 2022-02-02 Codes/0_prepare_data.R
format

@@ -121,18 +121,18 @@ saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))
 field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 
 field_with_design <-
-    field_with_design %>%
-    rowwise() %>%
-    mutate(
-        weights_matrix = list(
-            list(
-                Wls_50 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 50),
-                Wls_100 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 100),
-                Wls_200 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 200),
-                Wls_500 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 500)
-                )
-        )
-    ) 
+  field_with_design %>%
+  rowwise() %>%
+  mutate(
+    weights_matrix = list(
+      list(
+        Wls_50 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 50),
+        Wls_100 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 100),
+        Wls_200 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 200),
+        Wls_500 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 500)
+      )
+    )
+  )
 
 #* save the fields with weights matrix
 saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))

### 2022-02-02 Codes/Functions/R/add_errors_to_par.R
modification in gen_field_pars.R

@@ -1,0 +1,33 @@
+# par_name <- "Nk"
+# 
+# 
+
+add_errors_to_par <- function(par_name, scaler, new_var_name, cell_data, nsim, xy, sp_range, gstat_model) {
+
+  vars <- c(par_name, "sim", "cell_id")
+
+  temp_data <-
+    data.table(cell_data)[, ..vars] %>%
+    setnames(par_name, "w_var")
+
+  return_data <-
+    gen_pars(
+      mean = 0,
+      psill = 1,
+      range = sp_range,
+      coef_name = "temp_var",
+      gstat_model = gstat_model,
+      xy = xy,
+      nsim = nsim
+    ) %>%
+    # >>> normalize <<<
+    .[, min_temp_var := min(temp_var), by = sim] %>%
+    .[, max_temp_var := max(temp_var), by = sim] %>%
+    .[, error := scaler * (pnorm(temp_var, min_temp_var, max_temp_var) - 0.5)] %>%
+    .[temp_data, on = c("sim", "cell_id")] %>%
+    .[, var_with_error := w_var * error] %>%
+    .[, .(sim, cell_id, var_with_error)] %>%
+    setnames("var_with_error", new_var_name)
+
+  return(return_data)
+}

### 2022-02-02 Codes/Functions/R/gen_field_pars.R

@@ -30,7 +30,7 @@ gen_field_pars <- function(sp_range, gstat_model, field_sf, nsim) {
     .[, Nk := 100 + p * 150] %>%
     .[, c("cell_id", "sim", "Nk")]
 
-  # Nk_data$Nk %>% hist(breaks=40)
+  # Nk$Nk %>% hist(breaks=100)cell
   # rasterFromXYZ(Nk[sim==1, c("X","Y","Nk")]) %>% plot()
 
   # === ymax ===#
@@ -118,6 +118,7 @@ gen_field_pars <- function(sp_range, gstat_model, field_sf, nsim) {
     .[m_error_data, on = c("sim", "cell_id")] %>%
     .[N_error_data, on = c("sim", "cell_id")]
 
+
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Splitting parameters
   # /*+++++++++++++++++++++++++++++++++++
@@ -148,22 +149,18 @@ gen_field_pars <- function(sp_range, gstat_model, field_sf, nsim) {
   # /*+++++++++++++++++++++++++++++++++++
   cell_data <-
     cell_data %>%
-    .[, .(data = list(.SD)), by = sim] %>%
-    rowwise() %>%
-    #* create irrelevant variables
-    mutate(data = list(
-      mutate(
-        data,
-        theta_plateau_1 = faux::rnorm_pre(plateau, mu = 0, r = 0.4),
-        theta_plateau_2 = faux::rnorm_pre(plateau, mu = 0, r = 0.4),
-        theta_Nk_1 = faux::rnorm_pre(Nk, mu = 0, r = 0.4),
-        theta_Nk_2 = faux::rnorm_pre(Nk, mu = 0, r = 0.4),
-        theta_b0_1 = faux::rnorm_pre(b0, mu = 0, r = 0.4),
-        theta_b0_2 = faux::rnorm_pre(b0, mu = 0, r = 0.4)
-      )
-    )) %>%
-    unnest() %>%
-    data.table()
+    #* theta_plateau_1
+    add_errors_to_par("plateau_1", scaler = 1, "theta_plateau_1", ., nsim, xy, sp_range, gstat_model)[., on = c("sim", "cell_id")] %>%
+    #* theta_plateau_2
[…]

### 2022-02-02 Codes/0_prepare_data.R
path fixed

@@ -152,7 +152,7 @@ field_parameters <-
       sp_range = sp_range,
       gstat_model = gstat_model,
       field_sf = field_sf,
-      nsim = 1000
+      nsim = 10
     )
   ))
 

### 2022-02-02 Codes/1_geo_ml_simulation.R

@@ -33,7 +33,7 @@ library(here)
 setwd(here())
 
 #* source all the R functions in the Functions/R folder
-fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
+fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
     purrr::map(~ source(.))
 
 
@@ -45,14 +45,14 @@ fs::dir_ls(here("Codes", "Functions", "R"), full.names = TRUE) %>%
 
 #* Read field data
 field_data <-
-    readRDS(here("Data/field_data.rds")) %>%
+    readRDS(here("Shared/Data/field_data.rds")) %>%
     pull(field_sf) 
 
 #* Read field parameters
-field_parameters <- readRDS(here("Data/field_parameters.rds"))
+field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
 
 #* Read field data
-field_with_design <- readRDS(here("Data/field_with_design.rds"))
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 
 
 
@@ -115,7 +115,7 @@ models_data <-
             "drof" # DR-OF
         ),
         on = c(
-            TRUE, # ser_50
+            FALSE, # ser_50
             FALSE, # ser_100
             FALSE, # ser_200
             FALSE, # ser_500
@@ -125,7 +125,7 @@ models_data <-
             FALSE, # gwr_zone_scam
             FALSE, # ma_cf
             TRUE, # brf
-            TRUE, # rf
+            FALSE, # rf
             FALSE, # dmlof_semi
             FALSE, # dmlof_quad
             FALSE # drof
@@ -238,7 +238,7 @@ for(sc_i in 1:nrow(field_with_design)){
     ## -----------------------
     
     #* how many simulations to run
-    sim_range <- c(201:300)
+    sim_range <- c(201:210)
     
     #* run pre-defined `run_analysis` function
     eonr_results <-

### 2022-02-02 Codes/0_prepare_data.R
rf analysis modified to include interaction terms

@@ -152,7 +152,7 @@ field_parameters <-
       sp_range = sp_range,
       gstat_model = gstat_model,
       field_sf = field_sf,
-      nsim = 10
+      nsim = 1000
     )
   ))
 

### 2022-02-02 Codes/1_geo_ml_simulation.R

@@ -34,9 +34,7 @@ setwd(here())
 
 #* source all the R functions in the Functions/R folder
 fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
-    purrr::map(~ source(.))
-
-
+  purrr::map(~ source(.))
 
 
 # /*===========================================================
@@ -45,8 +43,8 @@ fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) 
 
 #* Read field data
 field_data <-
-    readRDS(here("Shared/Data/field_data.rds")) %>%
-    pull(field_sf) 
+  readRDS(here("Shared/Data/field_data.rds")) %>%
+  pull(field_sf)
 
 #* Read field parameters
 field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
@@ -61,76 +59,76 @@ field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 # /*===========================================================
 
 ## ---------------------------------
-## Regression functional form 
+## Regression functional form
 ## ---------------------------------
 
 x_vars <-
-    c(
-        "b0_1", "b0_2",
-        "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
-        "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
-        "theta_plateau_1", "theta_plateau_2",
-        "theta_Nk_1", "theta_Nk_2",
-        "theta_b0_1", "theta_b0_2"
-    )
+  c(
+    "b0_1", "b0_2",
+    "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
+    "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
+    "theta_plateau_1", "theta_plateau_2",
+    "theta_Nk_1", "theta_Nk_2",
+    "theta_b0_1", "theta_b0_2"
+  )
 
 control_vars <- paste0(x_vars, collapse = "+")
 int_vars <-
-    paste0(
-        paste0("I(N * ", x_vars, ")", collapse = "+"),
-        "+",
-        paste0("I(N2 * ", x_vars, ")", collapse = "+")
-    )
+  paste0(
+    paste0("I(N * ", x_vars, ")", collapse = "+"),
+    "+",
+    paste0("I(N2 * ", x_vars, ")", collapse = "+")
+  )
 
[…]

### 2022-02-02 Codes/Functions/R/gen_weights_matrix.R

@@ -1,42 +1,34 @@
 #* Generate spatial weights matrix for each trial field scenario:
 #*   quarter, half, full
-#*   
-#*   
+#*
+#*
 
 
-gen_weights_matrix <- function(data_file_name, cutoff){
+gen_weights_matrix <- function(data_file_name, cutoff) {
 
-    #=== load regression data ===#
-    dt <- data_file_name %>% readRDS() %>% 
-        pull(reg_data) %>% 
-        .[[1]] %>% 
-        pull(data) %>% 
-        .[[1]]
-    
-    #=== distance matrix ===#
-    D <- matrix(NA, nrow(dt), nrow(dt))
-    for (i in 1:nrow(dt)){
-        for(j in 1:nrow(dt)){
-            D[i,j] <- sqrt((dt$X[i] - dt$X[j])^2+
-                               (dt$Y[i] - dt$Y[j])^2 )
-        }
+  # === load regression data ===#
+  dt <- data_file_name %>%
+    readRDS() %>%
+    pull(reg_data) %>%
+    .[[1]] %>%
+    pull(data) %>%
+    .[[1]]
+
+  # === distance matrix ===#
+  D <- matrix(NA, nrow(dt), nrow(dt))
+  for (i in 1:nrow(dt)) {
+    for (j in 1:nrow(dt)) {
+      D[i, j] <- sqrt((dt$X[i] - dt$X[j])^2 +
+        (dt$Y[i] - dt$Y[j])^2)
     }
-    
-    #=== inverse distance weights matrix ===#
-    W <- 1/D^2                      # inverse distance
-    W[D > cutoff] <- 0              # cut off distance
-    diag(W) <- 0
-    W <- W/rowSums(W)			    # row-standardize
-    Wls <- mat2listw(W)	            # "listw" object
-    
-    return(Wls)
+  }
+
+  # === inverse distance weights matrix ===#
+  W <- 1 / D^2 # inverse distance
+  W[D > cutoff] <- 0 # cut off distance
+  diag(W) <- 0
+  W <- W / rowSums(W) # row-standardize
+  Wls <- mat2listw(W) # "listw" object
+
+  return(Wls)
 }
-
-
-
-
-
-
-
-
-

### 2022-02-02 Codes/Functions/R/run_rf_analysis.R

@@ -1,20 +1,36 @@
 # /*===========================================================
-#' # GWR analysis
+#' # RF analysis
 # /*===========================================================
-# ! Run GWR and do economic analysis
+# ! Run RF and do economic analysis
 
-# reg_data <- scaled_reg_data
-# cv_data <- scaled_cv_data
 
 run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
-  data <- copy(reg_data)
+  train_data <- copy(reg_data)
+  test_data <- copy(cv_data$data[[1]])
 
-  X <-
-    data[, c("N", x_vars), with = FALSE] %>%
-    data.frame()
 
-  Y <- data[, yield]
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Define X
+  # /*+++++++++++++++++++++++++++++++++++
+  int_var_names <- paste0("N_", x_vars)
+  int_var_exp <- paste0("= N * ", x_vars)
+  int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")
 
+  all_X_vars <- c("N", x_vars, int_var_names)
+
+  eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+  eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+
+  X <- train_data[, ..all_X_vars]
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Define Y
+  # /*+++++++++++++++++++++++++++++++++++
+  Y <- train_data[, yield]
+
+  # /*+++++++++++++++++++++++++++++++++++
+  #' ## Run BRF
+  # /*+++++++++++++++++++++++++++++++++++
   RF_temp <-
     grf::regression_forest(
       X = X,
@@ -25,27 +41,32 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
     )
 
   #************************   RMSR   ***********************
-  e_hat_train <- copy(data) %>%
-    .[, y_hat := predict(RF_temp,
-      newdata = .[, c("N", x_vars), with = FALSE]
-    )] %>%
+  e_hat_train <-
+    train_data %>%
+    .[, y_hat := predict(RF_temp, newdata = .[, all_X_vars, with = FALSE])] %>%
[…]

### 2022-02-02 Codes/0_prepare_data.R
update the brf to include interactions

@@ -115,28 +115,6 @@ field_with_design <-
 saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))
 
 
-# /*===========================================================
-#' # Add spatial weights matrix
-# /*===========================================================
-field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
-
-field_with_design <-
-  field_with_design %>%
-  rowwise() %>%
-  mutate(
-    weights_matrix = list(
-      list(
-        Wls_50 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 50),
-        Wls_100 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 100),
-        Wls_200 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 200),
-        Wls_500 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 500)
-      )
-    )
-  )
-
-#* save the fields with weights matrix
-saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))
-
 
 # /*===========================================================
 #' # Generate true field parameters
@@ -173,3 +151,27 @@ lapply(
   1:nrow(field_with_design),
   function(x) gen_reg_data(x, field_with_design, field_parameters)
 )
+
+
+
+# /*===========================================================
+#' # Add spatial weights matrix (aunit level)
+# /*===========================================================
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
+
+field_with_design <-
+    field_with_design %>%
+    rowwise() %>%
+    mutate(
+        weights_matrix = list(
+            list(
+                Wls_50 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 50),
+                Wls_100 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 100),
+                Wls_200 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 200),
+                Wls_500 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 500)
+            )
+        )
+    )
+
+#* save the fields with weights matrix
+saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))

### 2022-02-02 Codes/1_geo_ml_simulation.R

@@ -189,24 +189,6 @@ est_result_ls <- list()
 
 #*********************** loop over scenarios *********************#
 tic()
-for (sc_i in 1:nrow(field_with_design)) {
-
-
-  ## -----------
-  ##    data
-  ## -----------
-
-  #* field sf data
-  field_sf <- field_data[[sc_i]]
-
-  #* number of simulation cases
-  nsim <- field_parameters$field_pars[[sc_i]][, max(sim)]
-
-  #* load the simulated data
-  sim_data <-
-    field_with_design$data_file_name %>%
-    .[sc_i] %>%
-    readRDS()
 
   #* spatial weights matrix
   Wls <- field_with_design$weights_matrix[[sc_i]]

### 2022-02-02 Codes/Functions/R/run_brf_analysis.R
rf and brf modified

@@ -4,7 +4,7 @@
 # ! Run BRF and do economic analysis
 
 
-run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
+run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, include_int = FALSE) {
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
 
@@ -12,14 +12,18 @@ run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define X
   # /*+++++++++++++++++++++++++++++++++++
-  int_var_names <- paste0("N_", x_vars)
-  int_var_exp <- paste0("= N * ", x_vars)
-  int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")
+  if (include_int == FALSE) {
+    all_X_vars <- c("N", x_vars)
+  } else {
+    int_var_names <- paste0("N_", x_vars)
+    int_var_exp <- paste0("= N * ", x_vars)
+    int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")
 
-  all_X_vars <- c("N", x_vars, int_var_names)
+    all_X_vars <- c("N", x_vars, int_var_names)
 
-  eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
-  eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+    eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+    eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+  }
 
   X <- train_data[, ..all_X_vars]
 

### 2022-02-02 Codes/Functions/R/run_rf_analysis.R

@@ -4,22 +4,25 @@
 # ! Run RF and do economic analysis
 
 
-run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels) {
+run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, include_int = FALSE) {
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
-
 
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define X
   # /*+++++++++++++++++++++++++++++++++++
-  int_var_names <- paste0("N_", x_vars)
-  int_var_exp <- paste0("= N * ", x_vars)
-  int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")
+  if (include_int == FALSE) {
+    all_X_vars <- c("N", x_vars)
+  } else {
+    int_var_names <- paste0("N_", x_vars)
+    int_var_exp <- paste0("= N * ", x_vars)
+    int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")
 
-  all_X_vars <- c("N", x_vars, int_var_names)
+    all_X_vars <- c("N", x_vars, int_var_names)
 
-  eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
-  eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+    eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+    eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
+  }
 
   X <- train_data[, ..all_X_vars]
 

### 2022-02-02 Codes/Functions/R/add_errors_to_par.R
fix an error in add_errors_to_par.R

@@ -1,9 +1,9 @@
-# par_name <- "Nk"
-# 
-# 
+# par_name <- "Nk_1"
+# scaler <- 2
+# new_var_name <- "theta_NK_1"
+
 
 add_errors_to_par <- function(par_name, scaler, new_var_name, cell_data, nsim, xy, sp_range, gstat_model) {
-
   vars <- c(par_name, "sim", "cell_id")
 
   temp_data <-
@@ -21,9 +21,9 @@ add_errors_to_par <- function(par_name, scaler, new_var_name, cell_data, nsim, x
       nsim = nsim
     ) %>%
     # >>> normalize <<<
-    .[, min_temp_var := min(temp_var), by = sim] %>%
-    .[, max_temp_var := max(temp_var), by = sim] %>%
-    .[, error := scaler * (pnorm(temp_var, min_temp_var, max_temp_var) - 0.5)] %>%
+    .[, mean_temp_var := mean(temp_var), by = sim] %>%
+    .[, sd_temp_var := sd(temp_var), by = sim] %>%
+    .[, error := scaler * (pnorm(temp_var, mean = mean_temp_var, sd = sd_temp_var) - 0.5)] %>%
     .[temp_data, on = c("sim", "cell_id")] %>%
     .[, var_with_error := w_var * error] %>%
     .[, .(sim, cell_id, var_with_error)] %>%

### 2022-02-02 Codes/1_geo_ml_simulation.R
update 1_geo_ml codes

@@ -34,7 +34,9 @@ setwd(here())
 
 #* source all the R functions in the Functions/R folder
 fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
-  purrr::map(~ source(.))
+    purrr::map(~ source(.))
+
+
 
 
 # /*===========================================================
@@ -43,8 +45,8 @@ fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) 
 
 #* Read field data
 field_data <-
-  readRDS(here("Shared/Data/field_data.rds")) %>%
-  pull(field_sf)
+    readRDS(here("Shared/Data/field_data.rds")) %>%
+    pull(field_sf) 
 
 #* Read field parameters
 field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
@@ -59,76 +61,78 @@ field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 # /*===========================================================
 
 ## ---------------------------------
-## Regression functional form
+## Regression functional form 
 ## ---------------------------------
 
 x_vars <-
-  c(
-    "b0_1", "b0_2",
-    "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
-    "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
-    "theta_plateau_1", "theta_plateau_2",
-    "theta_Nk_1", "theta_Nk_2",
-    "theta_b0_1", "theta_b0_2"
-  )
+    c(
+        "b0_1", "b0_2",
+        "Nk_2_1", "Nk_2_2", "Nk_1_1",
+        # "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
+        "plateau_2_1", "plateau_2_2", "plateau_1_1",
+        # "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
+        "theta_plateau_1", "theta_plateau_2",
+        "theta_Nk_1", "theta_Nk_2",
+        "theta_b0_1", "theta_b0_2"
+    )
 
 control_vars <- paste0(x_vars, collapse = "+")
 int_vars <-
-  paste0(
-    paste0("I(N * ", x_vars, ")", collapse = "+"),
-    "+",
-    paste0("I(N2 * ", x_vars, ")", collapse = "+")
-  )
+    paste0(
[…]

### 2022-02-02 Codes/0_prepare_data.R
formatn change

@@ -152,26 +152,24 @@ lapply(
   function(x) gen_reg_data(x, field_with_design, field_parameters)
 )
 
-
-
 # /*===========================================================
 #' # Add spatial weights matrix (aunit level)
 # /*===========================================================
 field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 
 field_with_design <-
-    field_with_design %>%
-    rowwise() %>%
-    mutate(
-        weights_matrix = list(
-            list(
-                Wls_50 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 50),
-                Wls_100 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 100),
-                Wls_200 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 200),
-                Wls_500 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 500)
-            )
-        )
+  field_with_design %>%
+  rowwise() %>%
+  mutate(
+    weights_matrix = list(
+      list(
+        Wls_50 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 50),
+        Wls_100 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 100),
+        Wls_200 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 200),
+        Wls_500 = gen_weights_matrix(data_file_name = data_file_name, cutoff = 500)
+      )
     )
+  )
 
 #* save the fields with weights matrix
 saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))

### 2022-02-02 Codes/0_prepare_data.R
test

@@ -23,6 +23,7 @@ library(tictoc)
 library(here)
 options(stringsAsFactors = FALSE)
 
+
 # === Set working directory ===#
 setwd(here())
 

### 2022-02-02 Codes/3_figures.R
add boxplot codes

@@ -37,7 +37,7 @@ setwd(here())
 # load results data
 # -----------------
 est_data <-
-    readRDS(here("GitControlled/Results/est_result_ls.rds")) %>% 
+    readRDS(here("GitControlled/Results/est_result_ls_300.rds")) %>% 
     rbindlist() %>% 
     dplyr::select(model, perform, field_col) %>% 
     unnest(perform) %>% 
@@ -52,12 +52,13 @@ est_data <- est_data %>%
     .[, .(field_col, model, sim, profit, rmse_train, rmse_cv)] %>% 
     #---field size---
     .[, field_size := paste0( round(field_col * 72 * 6^2 / 10000, 1), " ha")] %>%
+    .[, field_size := factor(field_size, levels = c("9.3 ha", "18.7 ha", "37.3 ha"))] %>% 
     #---model name---
     .[model=="brf", model := "BRF"] %>%
     .[model=="rf", model := "RF"] %>%
     .[model=="lm", model := "OLS"] %>%
-    .[model=="ser", model := "SER"] %>%
-    .[, model := factor(model, levels = c("GWR", "BRF"))] %>% 
+    .[model=="ser_50", model := "SER"] %>%
+    .[, model := factor(model, levels = c("RF", "BRF", "OLS", "SER"))] %>% 
     print()
 
 
@@ -69,24 +70,26 @@ est_data <- est_data %>%
 # --------
 # boxplot
 # --------
-gdata <- est_data[field_col==72,]
+gdata <- est_data
 mean_data <- gdata %>%
     .[, .(profit = mean(profit),
           profit_sd = sd(profit),
           IQR = quantile(profit, 0.75) - quantile(profit, 0.25),
-          profit_low = quantile(profit, 0.25),
-          profit_high = quantile(profit, 0.75)
+          profit_down = quantile(profit, 0.25),
+          profit_up = quantile(profit, 0.75)
     ), 
-    by=c("field_col", "design", "model")] %>%
-    .[, profit_low := profit_low - 1.5*IQR] %>% 
-    .[, profit_high := profit_high + 1.5*IQR] %>% 
+    by=c("field_size", "model")] %>%
+    .[, profit_low := profit_down - 1.5*IQR] %>% 
+    .[, profit_high := profit_up + 1.5*IQR] %>% 
     print()
-source(here("Codes/Modules/figure_boxplot.R"))
[…]

### 2022-02-02 Codes/Modules/figure_boxplot_facet.R

@@ -1,0 +1,39 @@
+
+
+
+#------ range of profit values ------#
+value_ls <- -seq(0, -gdata[,min(profit)/5] %>% ceiling()*5, by = 10)
+yaxis_min <- gdata$profit %>% min()
+yaxis_max <- gdata$profit %>% max()
+
+#------ boxplot ------#
+library(tidytext)
+podg <- position_dodge(0.5)
+ggplot(data = gdata, 
+       aes(x = model, y = profit)) +
+    stat_boxplot(geom = "errorbar", width = 0.25, position = podg) +
+    geom_boxplot(position = podg, width = 0.25, outlier.shape = NA) +
+    geom_text(data = mean_data, 
+              aes(x = model, y = profit_high, 
+                  label = paste0(round(profit, 2), " (", round(profit_sd, 2),")")),
+              position = podg, angle = 90, 
+              hjust = 0, size = 3 ) +
+    facet_wrap(~field_size, nrow = 1, strip.position = "top", scales = "free") +
+    ylab('Average Profit Relative to True Optimal ($/ha)') +
+    xlab('') +
+    scale_x_reordered(position = "bottom") +
+    scale_y_continuous(expand = c(0, 0), breaks = value_ls, label = value_ls,
+                       limits = c(yaxis_min, yaxis_max + 10)) +
+    theme_bw() +
+    theme(
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        legend.position='none',
+        legend.title = element_text(size=12),
+        legend.key.size = unit(0.4, 'cm'),
+        legend.text = element_text(size=10),
+        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
+        axis.text=element_text(color='black')
+    ) 
+
+ 

### 2022-02-02 Codes/Modules/figure_boxplot_pool.R

@@ -1,0 +1,40 @@
+
+
+
+#------ range of profit values ------#
+value_ls <- -seq(0, -gdata[,min(profit)/5] %>% ceiling()*5, by = 10)
+yaxis_min <- gdata$profit %>% min()
+yaxis_max <- gdata$profit %>% max()
+
+#------ boxplot ------#
+library(tidytext)
+podg <- position_dodge(0.5)
+ggplot(data = gdata, 
+       aes(x = field_size, y = profit, fill = model)) +
+    stat_boxplot(geom = "errorbar", width = 0.25, position = podg) +
+    geom_boxplot(position = podg, width = 0.25, outlier.shape = NA) +
+    geom_text(data = mean_data, 
+              aes(x = field_size, y = profit_high,
+                  label = paste0(round(profit, 2), " (", round(profit_sd, 2),")")),
+              position = podg, angle = 90, 
+              hjust = 0, size = 3 ) +
+    ylab('Average Profit Relative to True Optimal ($/ha)') +
+    xlab('') +
+    scale_y_continuous(expand = c(0, 0), breaks = value_ls, label = value_ls,
+                       limits = c(yaxis_min, yaxis_max + 10)) +
+    theme_bw() +
+    theme(
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        legend.position='bottom',
+        legend.title = element_blank(),
+        legend.key.size = unit(0.4, 'cm'),
+        legend.text = element_text(margin = margin(r = 1, unit = "cm")),
+        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
+        axis.text=element_text(color='black')
+    ) +
+    guides(fill = guide_legend(label.position = "right",
+                               keywidth = unit(0.5, "cm"),
+                               keyheight = unit(0.5, "cm"),
+                               title.position = "left", 
+                               title.vjust = 1)) 

### 2022-02-02 Codes/Modules/figure_kernel_dist.R

@@ -1,0 +1,32 @@
+
+#* Kernel density distribution of profit:
+
+#------ rank design by gwr profit ------#
+design_level <- gdata %>%
+    .[model == "GWR", ] %>%
+    .[, .(profit = mean(profit)), by=c("field_col", "design", "model")] %>%
+    .[order(-profit), ] %>%
+    .$design
+gdata <- gdata[, design := factor(design, levels=design_level)] %>% 
+    .[, model := factor(model, levels = c("GWR", "BRF"))]
+
+#------ stack plot ------#
+ggplot() +
+    stat_density(data = gdata, 
+                 aes(x = profit, colour = design, linetype = design),
+                 position="identity", geom="line", size=0.5) +
+    facet_grid(model~., scales = "free_y") +
+    xlim(xlow, xhigh) +
+    xlab('Profit Relative to True Optimal ($/ha)') +
+    ylab("Density") +
+    labs(colour="Design", linetype="Design") +
+    theme_classic() +
+    theme(
+        legend.position='right',
+        legend.title = element_text(size=12),
+        legend.key.width = unit(1,"cm"),
+        legend.text = element_text(size=10),
+        plot.title = element_text(hjust = 0.5),
+        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
+        axis.text=element_text(color='black')
+    )

### 2022-02-03 Codes/3_figures.R
code for running 300 simulations

@@ -30,14 +30,11 @@ setwd(here())
 #' /*                         Load and Prepare Data                           */
 #' /*=========================================================================*/
 
-
-#******************************************************************************
-
 # -----------------
 # load results data
 # -----------------
 est_data <-
-    readRDS(here("GitControlled/Results/est_result_ls_300.rds")) %>% 
+    readRDS(here("GitControlled/Results/est_result_ls.rds")) %>% 
     rbindlist() %>% 
     dplyr::select(model, perform, field_col) %>% 
     unnest(perform) %>% 
@@ -89,11 +86,42 @@ source(here("GitControlled/Codes/Modules/figure_boxplot_pool.R"))
 ggsave(file = here('GitControlled/Graphs/profits_boxplot_pool.png'),
        height=6,width=6.5)
 
-#
+
+
+#' /*=========================================================================*/
+#' /*                       Kernel Density Distribution                       */
+#' /*=========================================================================*/
+
+# ---------------
+# kernel density
+# ---------------
+gdata <- est_data
+source(here("GitControlled/Codes/Modules/figure_kernel_dist.R"))
+ggsave(file = here('GitControlled/Graphs/profits_kernel.png'),
+       height=6.5,width=6.5)
 
 
 
 
+# -------------------------
+# extreme values of profit 
+# -------------------------
+# set <-40 $/ha as extremely low profit
+extreme_percent <- pi_data[, .(count = sum(profit<(-40)), 
+                               nsim = length(sim)), 
+                           by=.(field_col, design, model)] %>%
+    .[, extreme_percent := round(count/nsim*100, 2)] %>%
+    #--- Long to Wide: dcast()
+    dcast(field_col+design~model, value.var="extreme_percent") %>%
+    data.table() %>%
+    .[order(field_col, GWR),] %>%
+    .[field_col==144,] %>% 
+    print()
+write.csv(extreme_percent, here('Graph/tables/extreme_percent.csv'))
+
+
+
+#*******************************************************************************
 
 
 

### 2022-02-03 Codes/Modules/figure_boxplot_facet.R

@@ -23,7 +23,7 @@ ggplot(data = gdata,
     xlab('') +
     scale_x_reordered(position = "bottom") +
     scale_y_continuous(expand = c(0, 0), breaks = value_ls, label = value_ls,
-                       limits = c(yaxis_min, yaxis_max + 10)) +
+                       limits = c(yaxis_min, 0)) +
     theme_bw() +
     theme(
         panel.grid.major = element_blank(), 

### 2022-02-03 Codes/Modules/figure_boxplot_pool.R

@@ -21,7 +21,7 @@ ggplot(data = gdata,
     ylab('Average Profit Relative to True Optimal ($/ha)') +
     xlab('') +
     scale_y_continuous(expand = c(0, 0), breaks = value_ls, label = value_ls,
-                       limits = c(yaxis_min, yaxis_max + 10)) +
+                       limits = c(yaxis_min, 0)) +
     theme_bw() +
     theme(
         panel.grid.major = element_blank(), 
@@ -38,3 +38,5 @@ ggplot(data = gdata,
                                keyheight = unit(0.5, "cm"),
                                title.position = "left", 
                                title.vjust = 1)) 
+
+

### 2022-02-03 Codes/Modules/figure_kernel_dist.R

@@ -1,32 +1,38 @@
 
 #* Kernel density distribution of profit:
 
-#------ rank design by gwr profit ------#
-design_level <- gdata %>%
-    .[model == "GWR", ] %>%
-    .[, .(profit = mean(profit)), by=c("field_col", "design", "model")] %>%
-    .[order(-profit), ] %>%
-    .$design
-gdata <- gdata[, design := factor(design, levels=design_level)] %>% 
-    .[, model := factor(model, levels = c("GWR", "BRF"))]
+# #------ rank design by gwr profit ------#
+# design_level <- gdata %>%
+#     .[model == "GWR", ] %>%
+#     .[, .(profit = mean(profit)), by=c("field_col", "design", "model")] %>%
+#     .[order(-profit), ] %>%
+#     .$design
+# gdata <- gdata[, design := factor(design, levels=design_level)] %>% 
+#     .[, model := factor(model, levels = c("GWR", "BRF"))]
 
 #------ stack plot ------#
 ggplot() +
     stat_density(data = gdata, 
-                 aes(x = profit, colour = design, linetype = design),
+                 aes(x = profit, colour = model, linetype = model),
                  position="identity", geom="line", size=0.5) +
-    facet_grid(model~., scales = "free_y") +
-    xlim(xlow, xhigh) +
+    facet_wrap(~field_size, ncol = 1, strip.position = "top", scales = "free_y") +
+    # xlim(xlow, xhigh) +
     xlab('Profit Relative to True Optimal ($/ha)') +
     ylab("Density") +
-    labs(colour="Design", linetype="Design") +
-    theme_classic() +
+    # labs(colour="Design", linetype="Design") +
+    theme_bw() +
     theme(
-        legend.position='right',
-        legend.title = element_text(size=12),
-        legend.key.width = unit(1,"cm"),
-        legend.text = element_text(size=10),
-        plot.title = element_text(hjust = 0.5),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        legend.position='bottom',
+        legend.title = element_blank(),
+        legend.key.width = unit(1, 'cm'),
+        legend.text = element_text(margin = margin(r = 1, unit = "cm")),
         axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
         axis.text=element_text(color='black')
-    )
+    ) +
+    guides(fill = guide_legend(label.position = "right",
+                               keywidth = unit(0.5, "cm"),
[…]

### 2022-02-03 Codes/3_figures.R
debugged brf and rf codes

@@ -34,7 +34,7 @@ setwd(here())
 # load results data
 # -----------------
 est_data <-
-    readRDS(here("GitControlled/Results/est_result_ls.rds")) %>% 
+    readRDS(here("GitControlled/Results/est_result_ls_300.rds")) %>% 
     rbindlist() %>% 
     dplyr::select(model, perform, field_col) %>% 
     unnest(perform) %>% 
@@ -126,7 +126,7 @@ write.csv(extreme_percent, here('Graph/tables/extreme_percent.csv'))
 
 
 
-
+#*******************************************************************************
 
 
 

### 2022-02-03 Codes/Functions/R/run_brf_analysis.R

@@ -13,19 +13,20 @@ run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, inc
   #' ## Define X
   # /*+++++++++++++++++++++++++++++++++++
   if (include_int == FALSE) {
-    all_X_vars <- c("N", x_vars)
+    all_X_vars <- c(x_vars)
   } else {
     int_var_names <- paste0("N_", x_vars)
     int_var_exp <- paste0("= N * ", x_vars)
     int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")
 
-    all_X_vars <- c("N", x_vars, int_var_names)
+    all_X_vars <- c(x_vars, int_var_names)
 
     eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
     eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
   }
 
-  X <- train_data[, ..all_X_vars]
+  X <- train_data[, c("N", all_X_vars), with = FALSE]
+  
 
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define Y
@@ -43,18 +44,20 @@ run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, inc
       # min.node.size = 10
       tune.parameters = "all"
     )
+  
+  
 
   #************************   RMSR   ***********************
   e_hat_train <-
     train_data %>%
-    .[, y_hat := predict(BRF_temp, newdata = .[, all_X_vars, with = FALSE])] %>%
+    .[, y_hat := predict(BRF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%
     .[, e_hat := yield - y_hat] %>%
     .[, .(aunit_id, e_hat)] %>%
     setnames("e_hat", "e_hat_train")
 
   e_hat_cv <-
     test_data %>%
-    .[, y_hat := predict(BRF_temp, newdata = .[, all_X_vars, with = FALSE])] %>%
+    .[, y_hat := predict(BRF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%
     .[, e_hat := yield - y_hat] %>%
     .[, .(aunit_id, e_hat)] %>%
     setnames("e_hat", "e_hat_cv")
[…]

### 2022-02-03 Codes/Functions/R/run_rf_analysis.R

@@ -8,23 +8,25 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
 
+  
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define X
   # /*+++++++++++++++++++++++++++++++++++
   if (include_int == FALSE) {
-    all_X_vars <- c("N", x_vars)
+    all_X_vars <- c(x_vars)
   } else {
     int_var_names <- paste0("N_", x_vars)
     int_var_exp <- paste0("= N * ", x_vars)
     int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")
 
-    all_X_vars <- c("N", x_vars, int_var_names)
+    all_X_vars <- c(x_vars, int_var_names)
 
     eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
     eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
   }
 
-  X <- train_data[, ..all_X_vars]
+  X <- train_data[, c("N", all_X_vars), with = FALSE]
+
 
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define Y
@@ -32,7 +34,7 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
   Y <- train_data[, yield]
 
   # /*+++++++++++++++++++++++++++++++++++
-  #' ## Run BRF
+  #' ## Run RF
   # /*+++++++++++++++++++++++++++++++++++
   RF_temp <-
     grf::regression_forest(
@@ -42,34 +44,34 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
       # min.node.size = 10
       tune.parameters = "all"
     )
+  
 
   #************************   RMSR   ***********************
   e_hat_train <-
     train_data %>%
-    .[, y_hat := predict(RF_temp, newdata = .[, all_X_vars, with = FALSE])] %>%
+    .[, y_hat := predict(RF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%
     .[, e_hat := yield - y_hat] %>%
     .[, .(aunit_id, e_hat)] %>%
     setnames("e_hat", "e_hat_train")
 
[…]

### 2022-02-03 Codes/A0_prepare_data_for_sharing.rmd
program to prepare data for others created

# Objective

+ Create a dataset to share with Paul

# Set up

## Packages
```{r }
library(sf)
library(data.table)
library(tidyverse)
library(here)
```

# Prepare Data

```{r }
#* Read field data
field_data <-
  readRDS(here("Shared/Data/field_data.rds")) %>%
  pull(field_sf) %>%
  .[[1]]

saveRDS(field_data, here("Shared/Data/ToShare/field_sf.rds"))

field_with_design <- readRDS(here("Shared/Data/field_with_design.rds")) %>% .[sce_i, ]

x_vars <-
  c(
    "b0_1", "b0_2",
    "Nk_2_1", "Nk_2_2", "Nk_1_1",
    # "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
    "plateau_2_1", "plateau_2_2", "plateau_1_1",
    # "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
    "theta_plateau_1", "theta_plateau_2",
    "theta_Nk_1", "theta_Nk_2",
    "theta_b0_1", "theta_b0_2"
  )

#* Read the simulated data
sim_data <-
  field_with_design$data_file_name %>%
  readRDS() %>%
  .$reg_data %>%
  .[[1]] %>%
  .[, N_levels := NULL] %>%
  unnest() %>%
  data.table() %>%
  .[, c("sim", "aunit_id", x_vars), with = FALSE] %>%
  setnames(
    names(.),
    c(
      "sim",
      "aunit_id",
      paste0("par", 1:(length(names(.)) - 2))
    )
  )

saveRDS(sim_data, here("Shared/Data/ToShare/sim_data.rds"))
```

### 2022-02-03 Codes/Functions/R/run_brf_analysis.R
format rf and brf analysis codes a bit

@@ -5,15 +5,15 @@
 
 
 run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, include_int = FALSE) {
+
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
-
 
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define X
   # /*+++++++++++++++++++++++++++++++++++
   if (include_int == FALSE) {
-    all_X_vars <- c(x_vars)
+    all_X_vars <- x_vars
   } else {
     int_var_names <- paste0("N_", x_vars)
     int_var_exp <- paste0("= N * ", x_vars)
@@ -26,7 +26,6 @@ run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, inc
   }
 
   X <- train_data[, c("N", all_X_vars), with = FALSE]
-  
 
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define Y
@@ -44,20 +43,28 @@ run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, inc
       # min.node.size = 10
       tune.parameters = "all"
     )
-  
-  
 
   #************************   RMSR   ***********************
   e_hat_train <-
     train_data %>%
-    .[, y_hat := predict(BRF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%
+    .[, y_hat := predict(
+      BRF_temp,
+      newdata = .[, c("N", all_X_vars),
+        with = FALSE
+      ]
+    )] %>%
     .[, e_hat := yield - y_hat] %>%
     .[, .(aunit_id, e_hat)] %>%
     setnames("e_hat", "e_hat_train")
 
   e_hat_cv <-
     test_data %>%
-    .[, y_hat := predict(BRF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%
+    .[, y_hat := predict(
+      BRF_temp,
+      newdata = .[, c("N", all_X_vars),
+        with = FALSE
+      ]
+    )] %>%
     .[, e_hat := yield - y_hat] %>%
     .[, .(aunit_id, e_hat)] %>%
     setnames("e_hat", "e_hat_cv")
@@ -73,7 +80,12 @@ run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, inc
[…]

### 2022-02-03 Codes/Functions/R/run_rf_analysis.R

@@ -8,12 +8,12 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
 
-  
+
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define X
   # /*+++++++++++++++++++++++++++++++++++
   if (include_int == FALSE) {
-    all_X_vars <- c(x_vars)
+    all_X_vars <- x_vars
   } else {
     int_var_names <- paste0("N_", x_vars)
     int_var_exp <- paste0("= N * ", x_vars)
@@ -26,7 +26,6 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
   }
 
   X <- train_data[, c("N", all_X_vars), with = FALSE]
-
 
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define Y
@@ -44,7 +43,7 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
       # min.node.size = 10
       tune.parameters = "all"
     )
-  
+
 
   #************************   RMSR   ***********************
   e_hat_train <-

### 2022-02-03 Codes/Functions/R/run_brf_analysis.R
minor changes

@@ -5,7 +5,6 @@
 
 
 run_brf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, include_int = FALSE) {
-
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
 

### 2022-02-03 Codes/Functions/R/run_rf_analysis.R

@@ -8,7 +8,6 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
   train_data <- copy(reg_data)
   test_data <- copy(cv_data$data[[1]])
 
-
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define X
   # /*+++++++++++++++++++++++++++++++++++
@@ -44,8 +43,7 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
       tune.parameters = "all"
     )
 
-
-  #************************   RMSR   ***********************
+  #************************   RMSE   ***********************
   e_hat_train <-
     train_data %>%
     .[, y_hat := predict(RF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%

### 2022-02-03 Codes/1_geo_ml_simulation.R
add RF with perfect information

@@ -111,6 +111,7 @@ models_data <-
             "ma_cf", # multiarm-CF
             "brf", # boosted RF
             "rf", # random forest
+            "rf_perfect", # random forest with perfect reg data
             "dmlof_semi", # semiparmetric DML-OF
             "dmlof_quad", # semiparmetric DML-OF
             "drof" # DR-OF
@@ -127,6 +128,7 @@ models_data <-
             FALSE, # ma_cf
             TRUE, # brf
             TRUE, # rf
+            TRUE, # rf_perfect
             FALSE, # dmlof_semi
             FALSE, # dmlof_quad
             FALSE # drof
@@ -291,7 +293,7 @@ toc()
 
 
 #* save results
-saveRDS(est_result_ls, here("GitControlled", "Results", "est_result_ls_300.rds"))
+saveRDS(est_result_ls, here("GitControlled", "Results", "est_result_ls_100.rds"))
 
 
 

### 2022-02-03 Codes/Functions/R/run_indiv_analysis.R

@@ -118,6 +118,16 @@ run_indiv_analysis <- function(model, reg_data, cv_data, x_vars, pN, pCorn, N_le
               pCorn,
               N_levels
           )
+  } else if (model == "rf_perfect") { # rf_perfect
+      results <-
+          run_rf_analysis(
+              reg_data,
+              cv_data,
+              x_vars,
+              pN,
+              pCorn,
+              N_levels
+          )
   } else if (model == "dmlof_semi") { # semiparmetric DML-OF
     results <-
       run_DML_OF_c_analysis(

### 2022-02-04 Codes/A1_RF_sensitivity_check.rmd
block_id added to regression data for clustering

# Objective

+ Check how sensitive RF is to
  + the number of variables included
  + tuning parameters

# Conclusion

+ default parametrers are really good
+ tuning parameters via cross-validation does not really help

# Set up

## Packages
```{r }
library(sf)
library(data.table)
library(grf)
library(tidyverse)
library(here)
```

```{r }
fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
  purrr::map(~ source(.))

#* field
sce_i <- 3
```

# Prepare Data

```{r }
#* field sf data
field_data <-
  readRDS(here("Shared/Data/field_data.rds")) %>%
  pull(field_sf) %>%
  #* largest field
  .[[sce_i]]

#* field parameters
field_parameters <-
  readRDS(here("Shared/Data/field_parameters.rds")) %>%
  .[sce_i, ]

#* number of simulation cases
nsim <- field_parameters$field_pars[[1]][, max(sim)]

#* Read the simulated data
field_with_design <-
  readRDS(here("Shared/Data/field_with_design.rds")) %>%
  .[sce_i, ]

field_sf <- field_with_design$field_sf

sim_data <-
  field_with_design$data_file_name %>%
  readRDS()

#* define prices
pN <- sim_data$pN
pCorn <- sim_data$pCorn
```

## Define simulation function

```{r }
run_analysis <- function(sim_i, x_vars, models_data, pN, pCorn, Wls, nsim) {
  print(sim_i)

  # /*+++++++++++++++++++++++++++++++++++
  #' ## Prepare data
  # /*+++++++++++++++++++++++++++++++++++
  # /*+++++++++++++++++++++++++++++++++++
  #* extract the data for the sim_i
  train_data <- sim_data$reg_data[[1]][sim == sim_i, ]
  cv_data <- sim_data$reg_data[[1]][sim == ifelse(sim_i + 1 > nsim, 1, sim_i + 1), ]

  #* define parameters
  N_levels <- train_data$N_levels[[1]]
  reg_data <-
    train_data$data[[1]] %>%
    .[, x := (X - min(X)) / (max(X) - min(X))] %>%
    .[, y := (Y - min(Y)) / (max(Y) - min(Y))] %>%
    .[, xy := x * y] %>%
    .[, N2 := N^2]

  # reg_data[, N] %>% hist(breaks = 30)
  # ggplot(reg_data) +
  #   geom_point(aes(y = yield, x = N))

  results <-
    models_data %>%
    .[on == TRUE, ] %>%
    rowwise() %>%
    mutate(results = list(
      run_indiv_analysis(model, reg_data, cv_data, x_vars, pN, pCorn, N_levels, Wls)
    )) %>%
    mutate(results = list(
      mutate(results, model = model)
    )) %>%
    pull(results) %>%
    rbindlist()

  return(results)
}
```

## Define RF Analysis

```{r }
# /*===========================================================
#' # RF analysis
# /*===========================================================
# ! Run RF and do economic analysis

run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, include_int = FALSE) {
  train_data <- copy(reg_data)
  test_data <- copy(cv_data$data[[1]])

  # /*+++++++++++++++++++++++++++++++++++
  #' ## Define X
  # /*+++++++++++++++++++++++++++++++++++
  if (include_int == FALSE) {
    all_X_vars <- x_vars
  } else {
    int_var_names <- paste0("N_", x_vars)
    int_var_exp <- paste0("= N * ", x_vars)
    int_var_gen_exp <- paste0(int_var_names, int_var_exp, collapse = ",")

    all_X_vars <- c(x_vars, int_var_names)

    eval(parse(text = paste("train_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
    eval(parse(text = paste("test_data[, `:=`(", int_var_gen_exp, ")]", sep = "")))
  }

  X <- train_data[, c("N", all_X_vars), with = FALSE]

  # /*+++++++++++++++++++++++++++++++++++
  #' ## Define Y
  # /*+++++++++++++++++++++++++++++++++++
  Y <- train_data[, yield]

  # /*+++++++++++++++++++++++++++++++++++
  #' ## Run RF
  # /*+++++++++++++++++++++++++++++++++++
  RF_temp <-
    grf::regression_forest(
      X = X,
      Y = Y,
      num.trees = 2000,
      # min.node.size = 10
      # tune.parameters = "all",,
      # tune.parameters = c("min.node.size", "sample.fraction", "mtry"),
      # tune.num.trees = 100,
      # tune.num.reps = 100
    )

  #************************   RMSE   ***********************
  e_hat_train <-
    train_data %>%
    .[, y_hat := predict(RF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%
    .[, e_hat := yield - y_hat] %>%
    .[, .(aunit_id, e_hat)] %>%
    setnames("e_hat", "e_hat_train")

  e_hat_cv <-
    test_data %>%
    .[, y_hat := predict(RF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%
    .[, e_hat := yield - y_hat] %>%
    .[, .(aunit_id, e_hat)] %>%
    setnames("e_hat", "e_hat_cv")
  #*********************************************************

  N_seq <-
    data.table(
      N = seq(min(train_data$N), max(train_data$N), by = 2)
    )

  rf_results <-
    test_data %>%
    .[, c("aunit_id", "yield", all_X_vars), with = FALSE] %>%
    expand_grid_df(., N_seq) %>%
    .[, yield_hat := predict(RF_temp, newdata = .[, c("N", all_X_vars), with = FALSE])] %>%
    .[, pi_hat := pCorn * yield_hat - pN * N] %>%
    .[, .SD[which.max(pi_hat)], by = aunit_id] %>%
    .[, opt_N_hat := N] %>%
    .[, .(aunit_id, opt_N_hat)] %>%
    #--- RMSE ---
    .[e_hat_train, on = "aunit_id"] %>%
    .[e_hat_cv, on = "aunit_id"] %>%
    .[, sim := cv_data$sim]

  return(rf_results)
}
```

# Analysis

```{r, include=FALSE}
models_data <-
  data.table(
    model = c(
      "ser_50", # spatial error, weights_50
      "ser_100", # spatial error, weights_100
      "ser_200", # spatial error, weights_200
      "ser_500", # spatial error, weights_500
      "lm", # linear quadratic
      "gwr_t", # gwr-trevisan
      "gwr_semi", # gwr-semiparametric
      "gwr_zone_scam", # scam by zone,
      "ma_cf", # multiarm-CF
      "brf", # boosted RF
      "rf", # random forest
      "dmlof_semi", # semiparmetric DML-OF
      "dmlof_quad", # semiparmetric DML-OF
      "drof" # DR-OF
    ),
    on = c(
      FALSE, # ser_50
      FALSE, # ser_100
      FALSE, # ser_200
      FALSE, # ser_500
      FALSE, # lm
      FALSE, # gwr_t
      FALSE, # gwr_semi
      FALSE, # gwr_zone_scam
      FALSE, # ma_cf
      FALSE, # brf
      TRUE, # rf
      FALSE, # dmlof_semi
      FALSE, # dmlof_quad
      FALSE # drof
    )
  )

x_vars <-
  c(
    "b0_1", "b0_2",
    "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
    "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
    "theta_plateau_1", "theta_plateau_2",
    "theta_Nk_1", "theta_Nk_2",
    "theta_b0_1", "theta_b0_2"
  )

x_vars <-
  c(
    "b0", "Nk", "plateau"
  )

sim_range <- c(1:2)

eonr_results <-
  lapply(
    sim_range,
    function(x) {
      run_analysis(
        sim_i = x,
        x_vars = x_vars,
        models_data = models_data,
        pN = pN,
        pCorn = pCorn,
        Wls = Wls,
        nsim = nsim
      )
    }
  ) %>%
  rbindlist()

est_result <-
  eonr_results %>%
  nest_by(model) %>%
  mutate(
    perform = list(
      field_pars[sim %in% (sim_range + 1), ] %>%
        data.table(field_sf)[, .(cell_id, aunit_id)][., on = "cell_id"] %>%
        data.table(data)[., , on = c("sim", "aunit_id")] %>%
        .[, y_hat := gen_yield_QP(b0, b1, b2, Nk, opt_N_hat)] %>%
        .[, profit := pCorn * y_hat - pN * opt_N_hat] %>%
        .[, profit := profit - profit_opt] %>%
        .[, .(
          profit = mean(profit, na.rm = TRUE),
          rmse_train = mean(e_hat_train^2, na.rm = TRUE) %>% sqrt(),
          rmse_cv = mean(e_hat_cv^2, na.rm = TRUE) %>% sqrt()
        ),
        by = sim
        ]
    )
  ) %>%
  mutate(
    field_col =
      field_with_design$field_col[sc_i],
    mean_profit =
      perform[, mean(profit, na.rm = TRUE)],
    rmse_train =
      perform[, mean(rmse_train, na.rm = TRUE)],
    rmse_cv =
      perform[, mean(rmse_cv, na.rm = TRUE)]
  )

est_result
```

### 2022-02-04 Codes/1_geo_ml_simulation.R

@@ -34,7 +34,7 @@ setwd(here())
 
 #* source all the R functions in the Functions/R folder
 fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
-    purrr::map(~ source(.))
+  purrr::map(~ source(.))
 
 
 
@@ -44,8 +44,8 @@ fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) 
 
 #* Read field data
 field_data <-
-    readRDS(here("Shared/Data/field_data.rds")) %>%
-    pull(field_sf) 
+  readRDS(here("Shared/Data/field_data.rds")) %>%
+  pull(field_sf)
 
 #* Read field parameters
 field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
@@ -60,78 +60,78 @@ field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 # /*===========================================================
 
 ## ---------------------------------
-## Regression functional form 
+## Regression functional form
 ## ---------------------------------
 
 x_vars <-
-    c(
-        "b0_1", "b0_2",
-        # "Nk_2_1", "Nk_2_2", "Nk_1_1",
-        "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
-        # "plateau_2_1", "plateau_2_2", "plateau_1_1",
-        "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
-        "theta_plateau_1", "theta_plateau_2",
-        "theta_Nk_1", "theta_Nk_2",
-        "theta_b0_1", "theta_b0_2"
-    )
+  c(
+    "b0_1", "b0_2",
+    # "Nk_2_1", "Nk_2_2", "Nk_1_1",
+    "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
+    # "plateau_2_1", "plateau_2_2", "plateau_1_1",
+    "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
+    "theta_plateau_1", "theta_plateau_2",
+    "theta_Nk_1", "theta_Nk_2",
+    "theta_b0_1", "theta_b0_2"
+  )
 
 control_vars <- paste0(x_vars, collapse = "+")
 int_vars <-
-    paste0(
-        paste0("I(N * ", x_vars, ")", collapse = "+"),
[…]

### 2022-02-04 Codes/Functions/R/gen_reg_data.R

@@ -65,7 +65,7 @@ gen_reg_data <- function(i, field_with_design, field_parameters) {
     field[cell_data, on = "cell_id"] %>%
     n_assign_data[., on = c("sim", "block_id", "plot_in_block_id")] %>%
     #* add cell-level N application noise to target N
-    .[, meidan_det_N := median(N_tgt), by = sim] %>% 
+    .[, meidan_det_N := median(N_tgt), by = sim] %>%
     .[, N := N_tgt + meidan_det_N * N_error] %>%
     .[N < 0, N := 0] %>%
     #* deterministic yield
@@ -79,7 +79,7 @@ gen_reg_data <- function(i, field_with_design, field_parameters) {
     #* aggregate the data by analysis unit
     .[,
       lapply(.SD, mean),
-      by = .(sim, aunit_id),
+      by = .(sim, aunit_id, block_id),
       .SDcols = vars_to_summarize
     ] %>%
     .[, N2 := N^2] %>%

### 2022-02-04 Codes/Functions/R/run_rf_analysis.R

@@ -40,8 +40,11 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
       Y = Y,
       num.trees = 2000,
       # min.node.size = 10
-      tune.parameters = "all"
+      # tune.parameters = "all",,
+      tune.parameters = c("min.node.size", "sample.fraction", "mtry"),
+      tune.num.trees = 100
     )
+
 
   #************************   RMSE   ***********************
   e_hat_train <-

### 2022-02-04 Codes/1_geo_ml_simulation.R
Tried different RF model specifications. No big differences in results.

@@ -1,5 +1,5 @@
 
-## Packages
+#' Yield response model estimations
 
 rm(list = ls())
 
@@ -203,8 +203,11 @@ for(sc_i in 1:nrow(field_with_design)){
     #* field sf data
     field_sf <- field_data[[sc_i]]
     
+    #* field true parameters
+    field_pars <- field_parameters$field_pars[[sc_i]]
+        
     #* number of simulation cases
-    nsim <- field_parameters$field_pars[[sc_i]][, max(sim)]
+    nsim <- field_pars[, max(sim)]
     
     #* load the simulated data
     sim_data <-
@@ -224,9 +227,7 @@ for(sc_i in 1:nrow(field_with_design)){
     ## -----------------------
 
     #* find true EONR
-    field_pars <-
-        field_parameters$field_pars %>%
-        rbindlist() %>%
+    field_pars <- field_pars %>%
         .[, opt_N := (pN / pCorn - b1) / (2 * b2)] %>%
         .[, opt_N := pmin(Nk, opt_N)] %>%
         .[, opt_N := pmax(0, opt_N)] %>% 

### 2022-02-04 Codes/Functions/R/run_rf_analysis.R

@@ -39,7 +39,7 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
       X = X,
       Y = Y,
       num.trees = 2000,
-      # min.node.size = 10
+      # min.node.size = 10,
       tune.parameters = "all"
     )
 

### 2022-02-04 Codes/Functions/R/run_rf_perfect_analysis.R

@@ -12,7 +12,7 @@ run_rf_perfect_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_leve
   # /*+++++++++++++++++++++++++++++++++++
   #' ## Define X
   # /*+++++++++++++++++++++++++++++++++++
-  x_vars <- c( "Nk", "plateau", "b0")
+  x_vars <- c("Nk", "plateau", "b0")
   
   if (include_int == FALSE) {
     all_X_vars <- c(x_vars)
@@ -43,7 +43,7 @@ run_rf_perfect_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_leve
       X = X,
       Y = Y,
       num.trees = 2000,
-      # min.node.size = 10
+      # min.node.size = 10,
       tune.parameters = "all"
     )
   

### 2022-02-04 Codes/_checking_debugging.R

@@ -1,5 +1,5 @@
 
-## Packages
+#' Yield response model estimations
 
 rm(list = ls())
 
@@ -56,7 +56,7 @@ field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 
 
 # /*===========================================================
-#' #  Run estimations
+#' #  preparations
 # /*===========================================================
 
 ## ---------------------------------
@@ -66,7 +66,9 @@ field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 x_vars <-
     c(
         "b0_1", "b0_2",
+        # "Nk_2_1", "Nk_2_2", "Nk_1_1",
         "Nk_2_1", "Nk_2_2", "Nk_1_1", "Nk_1_2",
+        # "plateau_2_1", "plateau_2_2", "plateau_1_1",
         "plateau_2_1", "plateau_2_2", "plateau_1_1", "plateau_1_2",
         "theta_plateau_1", "theta_plateau_2",
         "theta_Nk_1", "theta_Nk_2",
@@ -99,24 +101,16 @@ sc_i <- 3
 #* field sf data
 field_sf <- field_data[[sc_i]]
 
+#* field true parameters
+field_pars <- field_parameters$field_pars[[sc_i]]
+
 #* number of simulation cases
-nsim <- field_parameters$field_pars[[sc_i]][, max(sim)]
+nsim <- field_pars[, max(sim)]
 
 #* load the simulated data
 sim_data <-
     field_with_design$data_file_name %>% .[sc_i] %>% 
     readRDS()
-
-
-#************************************************
-#* visual checking
-dt <- sim_data$reg_data[[1]][sim == 1, ]$data[[1]]
-f <- left_join(field_sf, dt, by = c("aunit_id"))
-ggplot() +
-    geom_sf(data = f, aes(fill = factor(N_tgt)), size = 0.3) +
-    scale_fill_viridis_d(name = "N rate (kg/ha)", direction = -1)
-#************************************************
-
 
 #* spatial weights matrix
 Wls <- field_with_design$weights_matrix[[sc_i]]
@@ -126,10 +120,12 @@ pN <- sim_data$pN
 pCorn <- sim_data$pCorn
 
 
+## -----------------------
+## Find true optimal N  
+## -----------------------
+
 #* find true EONR
-field_pars <-
-    field_parameters$field_pars %>%
[…]

### 2022-02-04 Codes/Functions/R/run_indiv_analysis.R
silly mistake in rf_pefect coding fixed

@@ -120,7 +120,7 @@ run_indiv_analysis <- function(model, reg_data, cv_data, x_vars, pN, pCorn, N_le
           )
   } else if (model == "rf_perfect") { # rf_perfect
       results <-
-          run_rf_analysis(
+          run_rf_perfect_analysis(
               reg_data,
               cv_data,
               x_vars,

### 2022-02-04 Codes/A0_prepare_data_for_sharing.R
new .R file to prepare data set for sharing

@@ -1,0 +1,347 @@
+
+#' Prepare data set for sharing with other researchers
+
+rm(list = ls())
+
+# /*===========================================================
+#' # Preparation
+# /*===========================================================
+#* set up python environment
+library(reticulate)
+
+#* packages
+library(sp)
+library(spdep)
+library(spatialreg)
+library(sf)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(dplyr)
+library(magrittr)
+library(gstat)
+library(GWmodel)
+library(scam)
+library(mgcv)
+library(magic)
+library(stringr)
+library(ggplot2)
+library(tictoc)
+library(here)
+
+#* set working directory
+setwd(here())
+
+#* source all the R functions in the Functions/R folder
+fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
+    purrr::map(~ source(.))
+
+
+
+# /*===========================================================
+#' # Read data
+# /*===========================================================
+
+#* Read field data
+field_data <-
+    readRDS(here("Shared/Data/field_data.rds")) 
+
+#* Read field parameters
+field_parameters <- 
+    readRDS(here("Shared/Data/field_parameters.rds"))
+
+#* Read regression data
+field_with_design <- 
+    readRDS(here("Shared/Data/field_with_design.rds"))
+
+
+
+# /*===========================================================
+#' # Field map data (full field)
+# /*===========================================================
+
+field_sf <- 
+    field_data %>% 
+    filter(field_col==144) %>% 
+    pull(field_sf) %>% 
+    .[[1]]
+saveRDS(field_sf, here("Shared/Data/ToShare/field_sf.rds"))
+
+
+
+# /*===========================================================
+#' # True field parameters
+# /*===========================================================
+
+field_sf <- 
+    field_data %>% 
+    filter(field_col==144) %>% 
+    pull(field_sf) %>% 
+    .[[1]]
[…]

### 2022-02-04 Codes/A0_prepare_data_for_sharing.R
completed .R codes for data sharing

@@ -6,8 +6,6 @@ rm(list = ls())
 # /*===========================================================
 #' # Preparation
 # /*===========================================================
-#* set up python environment
-library(reticulate)
 
 #* packages
 library(sp)
@@ -57,6 +55,18 @@ field_with_design <-
 
 
 # /*===========================================================
+#' # Price data (global variables)
+# /*===========================================================
+
+pCorn = 0.246063    # $/kg
+pN = 2.204624       # $/kg
+
+saveRDS(pCorn, here("Shared/Data/ToShare/pCorn.rds"))
+saveRDS(pN, here("Shared/Data/ToShare/pN.rds"))
+
+
+
+# /*===========================================================
 #' # Field map data (full field)
 # /*===========================================================
 
@@ -64,284 +74,117 @@ field_sf <-
     field_data %>% 
     filter(field_col==144) %>% 
     pull(field_sf) %>% 
-    .[[1]]
+    .[[1]] %>% 
+    data.table(.) %>% 
+    .[, col_id := NULL] %>%
+    .[, row_id := NULL] %>%
+    #---rename lat and lon---
+    setnames(
+        c("X","Y"),
+        c("lon","lat")
+    ) %>% 
+    st_as_sf()
 saveRDS(field_sf, here("Shared/Data/ToShare/field_sf.rds"))
 
 
 
 # /*===========================================================
-#' # True field parameters
+#' # Simulated regression data
 # /*===========================================================
 
-field_sf <- 
-    field_data %>% 
+#* true cell-level data
+field_pars <-
+    field_parameters %>% 
     filter(field_col==144) %>% 
-    pull(field_sf) %>% 
-    .[[1]]
-saveRDS(field_sf, here("Shared/Data/ToShare/field_sf.rds"))
+    pull(field_pars) %>% 
+    .[[1]] %>%
+    #---join aunit_id---
+    .[data.table(field_sf)[,.(cell_id, aunit_id, lat, lon)], on = "cell_id"] %>% 
+    #---true EONR---
+    .[, EONR := (pN / pCorn - b1) / (2 * b2)] %>%
[…]

### 2022-02-04 Codes/Functions/R/run_rf_analysis.R
restore run_rf_analysis() function to tune.parameters = "all" (consistent with rf_perfect)

@@ -39,15 +39,8 @@ run_rf_analysis <- function(reg_data, cv_data, x_vars, pN, pCorn, N_levels, incl
       X = X,
       Y = Y,
       num.trees = 2000,
-<<<<<<< HEAD
       # min.node.size = 10,
       tune.parameters = "all"
-=======
-      # min.node.size = 10
-      # tune.parameters = "all",,
-      tune.parameters = c("min.node.size", "sample.fraction", "mtry"),
-      tune.num.trees = 100
->>>>>>> origin/master
     )
 
 

### 2022-02-08 Codes/1_geo_ml_simulation.R
start writing

@@ -241,7 +241,7 @@ for(sc_i in 1:nrow(field_with_design)){
     ## -----------------------
     
     #* how many simulations to run
-    sim_range <- c(1:100)
+    sim_range <- c(401:1000)
     
     #* run pre-defined `run_analysis` function
     eonr_results <-
@@ -294,7 +294,7 @@ toc()
 
 
 #* save results
-saveRDS(est_result_ls, here("GitControlled", "Results", "est_result_ls_100.rds"))
+saveRDS(est_result_ls, here("GitControlled", "Results", "est_result_ls_600.rds"))
 
 
 

### 2022-02-08 Codes/3_figures.R

@@ -19,6 +19,7 @@ library(viridis)
 library(dplyr)
 library(tidyr)
 library(tidyverse)
+library(modelsummary)
 library(here)
 theme_set(theme_bw())
 
@@ -34,7 +35,7 @@ setwd(here())
 # load results data
 # -----------------
 est_data <-
-    readRDS(here("GitControlled/Results/est_result_ls_300.rds")) %>% 
+    readRDS(here("GitControlled/Results/est_result_ls_400.rds")) %>% 
     rbindlist() %>% 
     dplyr::select(model, perform, field_col) %>% 
     unnest(perform) %>% 
@@ -53,9 +54,10 @@ est_data <- est_data %>%
     #---model name---
     .[model=="brf", model := "BRF"] %>%
     .[model=="rf", model := "RF"] %>%
+    .[model=="rf_perfect", model := "RF_PERFECT"] %>%
     .[model=="lm", model := "OLS"] %>%
     .[model=="ser_50", model := "SER"] %>%
-    .[, model := factor(model, levels = c("RF", "BRF", "OLS", "SER"))] %>% 
+    .[, model := factor(model, levels = c("RF", "RF_PERFECT", "BRF", "OLS", "SER"))] %>% 
     print()
 
 
@@ -64,9 +66,9 @@ est_data <- est_data %>%
 #' /*                           Mean and Error Bars                           */
 #' /*=========================================================================*/
 
-# --------
-# boxplot
-# --------
+# ----------------
+# boxplot: profit
+# ----------------
 gdata <- est_data
 mean_data <- gdata %>%
     .[, .(profit = mean(profit),
@@ -86,6 +88,54 @@ source(here("GitControlled/Codes/Modules/figure_boxplot_pool.R"))
 ggsave(file = here('GitControlled/Graphs/profits_boxplot_pool.png'),
        height=6,width=6.5)
 
+# ----------------
+# boxplot: RMSE
+# ----------------
+gdata <- est_data
+source(here("GitControlled/Codes/Modules/figure_boxplot_rmse_pool.R"))
+ggsave(file = here('GitControlled/Graphs/rmse_boxplot_pool.png'),
+       height=6,width=6.5)
+
+# --------------------
+# Table: mean and sd 
+# --------------------
+
+profit_summary_table <- datasummary(
+    (profit) * model ~ factor(field_size) * (Mean + SD), 
+    data = gdata[, .(field_size, model, profit)])
+rmse_summary_table <- datasummary(
[…]

### 2022-02-08 Codes/3_make_figures_tables.R

@@ -1,0 +1,445 @@
+
+#' # /*===========================================================
+#' #' # Visualization the field and spatial units
+#' # /*===========================================================
+#' # fig.id = "field-layout",
+#' # fig.cap = "Simulated field layout with spatial unit definitions",
+#' # fig.dim = c(6, 6)
+#' 
+#' field_with_design <- readRDS(here("Data/field_with_design.rds"))
+#' field_sf <- field_with_design[1, ]$field_sf[[1]]
+#' 
+#' plot_sf <-
+#'   field_sf %>%
+#'   nest_by(plot_id) %>%
+#'   mutate(data = list(
+#'     st_union(data)
+#'   )) %>%
+#'   unnest() %>%
+#'   st_as_sf()
+#' 
+#' block_sf <-
+#'   field_sf %>%
+#'   nest_by(block_id) %>%
+#'   mutate(data = list(
+#'     st_union(data)
+#'   )) %>%
+#'   unnest() %>%
+#'   st_as_sf()
+#' 
+#' block_text_sf <- st_centroid(block_sf)
+#' 
+#' #* Field: plots and blocks
+#' g_field <-
+#'   ggplot() +
+#'   geom_sf(data = plot_sf, size = 0.2, fill = NA) +
+#'   geom_sf(data = filter(plot_sf, plot_id == 264), fill = "red", alpha = 0.5) +
+#'   geom_sf(data = block_sf, fill = NA, size = 1.5) +
+#'   annotate("text", x = 830, y = 74, label = "plot", color = "red", size = 5) +
+#'   geom_segment(
+#'     aes(x = 830, xend = 830, y = 30, yend = -80),
+#'     arrow = arrow(length = unit(0.5, "cm")),
+#'     size = 1,
+#'     color = "red"
+#'   ) +
+#'   geom_sf_text(
+#'     data = block_text_sf,
+#'     aes(label = paste0("block ", block_id)),
+#'     size = 5
+#'   ) +
+#'   theme_void() +
+#'   ggtitle("Panel (a): Plots and blocks in an experimental field")
+#' 
+#' ## inside a plot
+#' plot_sf_focus <- filter(field_sf, plot_id == 1)
+#' 
+#' subplot_sf <-
+#'   plot_sf_focus %>%
+#'   nest_by(aunit_id, buffer) %>%
+#'   mutate(data = list(
+#'     st_union(data)
+#'   )) %>%
+#'   unnest() %>%
+#'   st_as_sf() %>%
+#'   mutate(label = ifelse(
[…]

### 2022-02-08 Codes/Modules/figure_boxplot_rmse_pool.R

@@ -1,27 +1,21 @@
 
 
 
-#------ range of profit values ------#
-value_ls <- -seq(0, -gdata[,min(profit)/5] %>% ceiling()*5, by = 10)
-yaxis_min <- gdata$profit %>% min()
-yaxis_max <- gdata$profit %>% max()
+#------ range of values ------#
+value_ls <- seq(gdata[,min(rmse_cv)/200] %>% floor()*200, 
+                gdata[,max(rmse_cv)/200] %>% ceiling()*200, 
+                by = 200)
+
 
 #------ boxplot ------#
-library(tidytext)
-podg <- position_dodge(0.4)
+podg <- position_dodge(0.25)
 ggplot(data = gdata, 
-       aes(x = field_size, y = profit, fill = model)) +
+       aes(x = field_size, y = rmse_cv, fill = model)) +
     stat_boxplot(geom = "errorbar", width = 0.25, position = podg) +
     geom_boxplot(position = podg, width = 0.25, outlier.shape = NA) +
-    # geom_text(data = mean_data, 
-    #           aes(x = field_size, y = profit_high,
-    #               label = paste0(round(profit, 2), " (", round(profit_sd, 2),")")),
-    #           position = podg, angle = 90, 
-    #           hjust = 0, size = 3 ) +
-    ylab('Average Profit Relative to True Optimal ($/ha)') +
+    ylab('Out-of-Sample Yield Prediction RMSE (kg/ha)') +
     xlab('') +
-    scale_y_continuous(expand = c(0, 0), breaks = value_ls, label = value_ls,
-                       limits = c(yaxis_min - 10, 0)) +
+    scale_y_continuous(breaks = value_ls, label = value_ls) +
     theme_bw() +
     theme(
         panel.grid.minor.x = element_blank(),

### 2022-02-08 Writing/manuscript.rmd
code format change

@@
 ---
-title: "New"
+title: "Comparing Machine Learning and Traditional Regression Methods in Site-Specific Economically Optimal Nitrogen Rate Prediction"
 author:
@@
 library(patchwork)
+library(gridExtra)
 ```
@@
 #   lapply(., function(x) source(x))
-# 
-# #* read the results rds file
-# results <-
-#   here("Results", "pi_data.rds") %>%
-#   readRDS() %>%
-#   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
-#   .[, bias := pi_diff_est - pi_diff]
-# 
-# pi_dif_gwr <-
-#   results[, .(pi_dif = mean(pi_diff)), by = type] %>%
-#   .[, diff(pi_dif)]
-# 
-# #* create figures
-# source(here("Codes", "3_make_figures_publication.R"))
+
+# /*----------------------------------*/
+#' ##  data preparation
+# /*----------------------------------*/
+#' load results data
+est_data <-
+  readRDS(here("Results", "est_result_ls_400.rds")) %>%
+  rbindlist() %>%
+  dplyr::select(model, perform, field_col) %>%
+  unnest(perform) %>%
+  data.table()
+#' rename columns
+gdata <- est_data %>%
+  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv)] %>%
+  #---field size---
+  .[, field_size := paste0(round(field_col * 72 * 6^2 / 10000, 1), " ha")] %>%
+  .[, field_size := factor(field_size, levels = c("9.3 ha", "18.7 ha", "37.3 ha"))] %>%
+  #---model name---
+  .[model == "brf", model := "BRF"] %>%
+  .[model == "rf", model := "RF"] %>%
+  .[model == "rf_perfect", model := "RF best"] %>%
+  .[model == "lm", model := "LM"] %>%
+  .[model == "ser_50", model := "SER"] %>%
+  .[, model := factor(model, levels = c("RF", "RF best", "BRF", "LM", "SER"))]
+#' mean and sd
+mean_data <- gdata %>%
+  .[, .(
+    profit = mean(profit) %>% round(2),
+    profit_sd = sd(profit) %>% round(2),
+    rmse = mean(rmse_cv) %>% round(2),
+    rmse_sd = sd(rmse_cv) %>% round(2)
+  ),
+  by = c("field_size", "model")
+  ] %>%
+  .[order(field_size, model), ]
+
+# /*----------------------------------*/
+#' ##  create figures and tables
+# /*----------------------------------*/
+source(here("Codes", "3_make_figures_tables.R"))
 ```
@@
 
++ Traditional vs ML (LM, SER better than RF and BRF)
++ Yield prediction vs EONR prediction
++ Statistical efficiency is money (SER vs LM)
+
 # Methods
 
-## results 1
+## Linear Regression (LM)
+
+## Spatial Error Model (SER)
+
+## Random Forest (RF)
+
+## Boosted Regression Forest (BRF)
+
+## Yield prediction performance measure
+
+## EONR prediction performance measure
 
@@
 
-# Discussions
+## Yield predictions
+Machine learning methods perform better than traditional regression methods in yield prediction.
+The RMSE results for the out-of-sample yield prediction over the 1,000 simulations are displayed in Figure \@ref(fig:rmse-boxplot-pool).
+
+- For the full field (37.3 ha) scenario, the average RMSE over 1,000 simulations is `r mean_data[field_size=="37.3 ha"&model=="RF", rmse] %>% round(2)` kg ha$^{-1}$ for the RF model, and `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse] %>% round(2)` kg ha$^{-1}$ for the BRF model, which are significantly smaller than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse] %>% round(2)` kg ha$^{-1}$) and SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse] %>% round(2)` kg ha$^{-1}$) models.
+If we give RF model the best data, its RMSE will be as small as `r mean_data[field_size=="37.3 ha"&model=="RF best", rmse] %>% round(2)` kg ha$^{-1}$.
+- The trend of RMSE performance is robust to field sizes.
+For smaller field sizes, the overall levels of RMSE are slightly larger (of course), but machine learning models' RMSE (RF and BRF) are consistently smaller than the RMSE of traditional regression models (LM and SER).
+
+The finding of machine learning models' better yield prediction performances is consistent with existing literature (**citations**).
+
+## 
+RF and BRF models have better yield predictions.  So what?
+
+Better yield prediction does not necessarily translate into better EONR
+
+## Profit performances
+
+Profit performance results for different models are displayed in Figure \@ref(fig:pi-boxplot-pool).
+
+- The average profit from EONR predicted by RF model is $\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$ over 1,000 simulations for the full field data.
+That is really low.
+The BRF model is better, with profit of $\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$.
+But those are still significantly lower than even the LM model ($\$$`r mean_data[field_size=="37.3 ha"&model=="LM", profit] %>% round(2)` ha$^{-1}$).
+The SER model has the highest profit of $\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$.
+- Even if we "cheat" and feed RF model with the best data, its profit is still only $\$$`r mean_data[field_size=="37.3 ha"&model=="RF best", profit] %>% round(2)` ha$^{-1}$ 
+- For smaller field sizes, the overall levels of profit decrease, which is not surprising as model estimations become less accurate with smaller sample sizes.
+But the general trend of profit performance across models is robust to field sizes.
+- The relative performance of BRF profit improves when field size reduces.
+For the small (9.3 ha) and medium (18.7 ha) sized fields, the BRF profit outperforms LM model.
+The profit gap between BRF and SER models also reduces from $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ of large field to $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ of medium field and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ of small field.
+That may suggests machine learning is more useful for smaller field's data.
 
@@
 
-# Tables
+# Discussions
+
++ Yield prediction vs EONR prediction
++ Statistical efficiency is money (SER vs LM)
 
@@
 
-# Figures
+# Conclusions
 
@@
 # References
+
+# Figures {-}
+
+```{r rmse-boxplot-pool, fig.cap="The yield prediction performances of different models.", echo=FALSE, fig.width=7}
+rmse_boxplot_pool | pi_boxplot_pool
+```
+
+```{r pi-boxplot-pool, fig.cap="The profit performances of different models.", echo=FALSE}
+pi_boxplot_pool
+```
+
+# Tables {-}
+
+```{r extreme-percent, echo=FALSE}
+knitr::kable(mean_data, format = "markdown", caption = "Summary Statistics")
+```

### 2022-02-09 Writing/manuscript.rmd
Methods is written

@@
        sep: ": "
-bibliography: PA.bib
-csl: american-journal-of-agricultural-economics.csl
+# bibliography: PA.bib
+# csl: american-journal-of-agricultural-economics.csl
 abstract: ""
@@
 
-```{r echo = F, cache = F}
-suppressMessages(library(knitr))
-suppressMessages(library(here))
-suppressMessages(library(officedown))
-suppressMessages(library(officer))
+```{r echo = F, cache = F, include = F}
+library(knitr)
+library(here)
+
+here::i_am("GitControlled/Writing/manuscript.rmd")
 
@@
   message = F,
-  cache = F,
+  cache = T,
   echo = F,
@@
 
-```{r cache = F}
+```{r cache = F, include = F}
 #--- packages ---#
@@
 library(tidyverse)
+library(officedown)
+library(officer)
 library(flextable)
@@
 est_data <-
-  readRDS(here("Results", "est_result_ls_400.rds")) %>%
+  readRDS(here("Shared", "Results", "est_result_ls_400.rds")) %>%
   rbindlist() %>%
@@
 # /*----------------------------------*/
-source(here("Codes", "3_make_figures_tables.R"))
+source(here("GitControlled", "Codes", "3_make_figures_tables.R"))
 ```
@@
 
-# Methods
+# Methods: Monte Carlo Simulation
 
-## Linear Regression (LM)
+In our Monte Carlo simulations, we will test five estimation approches on three different sizes of fields: x ha, y ha, and x ha.
+In this section, we describe the data generating process, estimation approaches, and model evaluation.
 
-## Spatial Error Model (SER)
+## Data Generation
 
-## Random Forest (RF)
+Three simulated field of different sizes were created.
+Figure \@ref(fig:field-map) provides the map of a z-acre field as an example.
+The field consisted of $384$ 18.3 m $\times$ 73.2 m "plots," each of which was assigned an N fertilizer application rate.
+Each plot was made up of four (4-rows $\times$ 1-column) 18.3 m $\times$ 18.3 m "subplots," which were unit of analysis used in subsequent statistical analysis.
+Each subplot contained of a 6-rows $\times$ 6-columns grid of thirty-six 3.05 m $\times$ 3.05 m "cells." All field characteristics and yield data were generated at the cell level.
 
-## Boosted Regression Forest (BRF)
+Data were generated at the cell-level and then aggregted up to analysis-unit levle (why). Cell-levle yields were generated following the quadratic-plateau functional form as follows:
 
-## Yield prediction performance measure
+$$
+\begin{aligned}
+y_{i,j} = 
+  \begin{cases}
+  \alpha_{i,j} + \beta_{i,j} N + \gamma_{i,j} N^2 + \varepsilon_{i,j}, & N < \tau_{i,j} \\
+  \eta_{i,j}, & N \geq \tau_{i,j}
+  \end{cases}
+\end{aligned}
+$$
 
-## EONR prediction performance measure
+In this formualtion, yield increases as $N_{i,j}$ increaes until $N_{i,j}$ reaches $\tau_{i,j}$, at which yield hits the plateau, $\eta_{i,j}$.
+The yield level at $N_{i,j}= 0$ is $\alpha_{i,j}$.
+The rate at which yield increases with repsect to $N_{i,j}$ is governed by $\beta_{i,j}$ and $\gamma_{i,j}$.
+
+Farmers do not observe any of the parameters, but observe the decomposition of the parameters that goven the yield resopnse function. Specifically,
+
+$$
+\begin{aligned}
+\alpha_{i,j} & = \alpha^1_{i,j} + \alpha^2_{i,j} \\
+\tau_{i,j} & = min\big(min(\tau^{1,1}_{i,j}, \tau^{1,2}_{i,j}), min(\tau^{2,1}_{i,j}, \tau^{2,2}_{i,j})\big) \\
+\eta_{i,j} & = min\big(min(\eta^{1,1}_{i,j}, \eta^{1,2}_{i,j}), min(\eta^{2,1}_{i,j}, \eta^{2,2}_{i,j})\big) 
+\end{aligned}
+$$
+
+We denote the collection of covariate ($\alpha^1_{i,j}$, $\alpha^2_{i,j}$, $\tau^{1,1}_{i,j}$, $\tau^{1,2}_{i,j}$, $\tau^{2,1}_{i,j}$, $\tau^{2,2}_{i,j}$, $\eta^{1,1}_{i,j}$, $\eta^{1,2}_{i,j}$, $\eta^{2,1}_{i,j}$, $\eta^{2,2}_{i,j}$) as $X^1_{i,j}$.
+Note that $\alpha_{i,j}$, $\tau_{i,j}$, and $\eta_{i,j}$ (or equivalently $X^1_{i,j}$) have sufficient information to completely characterize the yield response function.
+This is because the coefficients $\beta_{i,j}$ and $\gamma_{i,j}$ are identified once $\alpha_{i,j}$, $\tau_{i,j}$, and $\eta_{i,j}$ are determined.
+These covariates are generated in a way that they are spatially correlated and also correlated with one another (Please see the codes available at <span style = "color: blue;"> gihutb account here</span>).
+
+In addition to the covariates, two nuisance covariates that are correlated with eahc of $\alpha_{i,j}$, $\tau_{i,j}$, and $\eta_{i,j}$ are generated: $\phi^{\alpha, 1}_{i,j}$, $\phi^{\alpha, 2}_{i,j}$, $\phi^{\tau, 1}_{i,j}$, $\phi^{\tau, 2}_{i,j}$, $\phi^{\eta, 1}_{i,j}$, $\phi^{\eta, 2}_{i,j}$.
+We denote these variables as $X^2_{i,j}$.
+These variables are nuisance in the sense that they provide no additional information about the yield response functions once $X^1_{i,j}$ are included as covariates.
+Since they are correlated with $X^1_{i,j}$, the inclusion of $X^2_{i,j}$ would interfere with accurate identification of the $X^1_{i,j}$.
+We denote $X^1_{i,j}$ and $X^2_{i,j}$ collectively as $X_{i,j}$.
+Once the cell-level variables are generated, true economically optimal can be found by solving the profit maximization problem.
+This process is repeated 1000 times to create 1000 datasets.
+See Appendix \@ref(parameters) for maps of some of the covariates and true EONR for a single simulation round as an example.
+The cell level data were then aggregated up to the analysis unit level data: $\{y_i, X_i\}$.
+
+## Estamation of yield response functions and site-specific optimal nitrogen rates
+
+**Approach 1**: Linear Model OLS (Hereafter, LM)
+
+The LM approach assumes a quadratic yield response function:
+
+$$
+\begin{aligned}
+y_i = \beta_0 + \beta_1 \cdot N_i + \beta_2\cdot N_i^2 + N_i\cdot X_i\cdot \gamma_1 + N_i^2\cdot X_i\cdot \gamma_2 + \varepsilon
+\end{aligned}
+$$
+
+where $\gamma_1$ and $\gamma_2$ are sets of interactions of $X_i$ with $N_i$, and $\varepsilon$ is the error term.
+The model is certainly misspecified because quadratic functions cannot perfectly represent yield response functions with a plateau (cite).
+It is known that the use of the quadratic functional form tends to over-estimate the true optimal nitrogen rate.
+However, it still approximates the underlying yield response functions quite well and is a popular functional form (cite).
+The _feols_ package in R was used to estimate the model (cite).
+
+**Approach 2**: Spatial Error Model (SER)
+
+The econometic model for the SER approach follows that of the LM approach except for the error term.
+
+$$
+\begin{aligned}
+y_i &= \beta_0 + \beta_1 \cdot N_i + \beta_2\cdot N_i^2 + N_i\cdot X_i\cdot \gamma_1 + N_i^2\cdot X_i\cdot \gamma_2 + \varepsilon \\
+\varepsilon & = \lambda W \mu
+\end{aligned}
+$$
+
+where $\lambda$ is scaler that reflects the degree of spatial dependence, $W$ is the user-defined weight matrix, and $\mu$ is the idiosynctaric error term that is not spatially correlated.
+Estimation via the spatial error model takes into account the spatial dependency of the error term and thus statistically more  efficient than the LM approach.
+The _spatialreg_ package in R was used to estimate the model (cite).
+
+**Approach 3**: Random Forest (RF)
+
+Unlike the LM and SER approaches, it does not assume any particular functional relationships between the dependent vairable and the covaraites.
+Random Forest consists of ensembles of trees.
+In each tree, the train data is split into a number of leaves based on the covirate values and all the observations belonging to the same leaf share the same yield estimate.
+Unlike a single classification and regression tree (CART), RF tends to avoid overfitting thanks to the averaging of estimates from the individual trees.
+The RF approach uses all the variables $(X_{i})$ as covariates.
+
+**Approach 4**: best Random Forest (RF$_{best}$)
+
+The RF$_{best}$ approach uses $\alpha$, $\beta$, and $\gamma$ directly to give a comparative advantage to RF relative to the other methods, instead of $(X_{i})$.
+
+**Approach 5**: Boosted Regression Forest (BRF)
+
+While RF builds individual trees completely independent of one another, BRF build trees in a way that focuses relatively more on imroving the parts of the data that are not well explained in the previous sequence of trees.
+Consequently, BRF tends to perform better than RF in predicting yield.
+However, its use in the context of site-specific input management is limited compared to RF at the moment.
+The BRF approach uses all the covaraites in $X$ like the LM, SER, and RF approaches.
+The _grf_ package in R was used to run the RF, RF$_{best}$, and BRF estimations (cite).
+Hyperparameters were tuned using cross-validation.
+
+For all the approches, once the yield response functions are estimated, site-specific EONR are calculated by numerically solving profit maximization problems at the cell level.
+Corn and nitrogen prices are assumed to be <span style = "color: blue;"> Xiaofei, put numbers here </span>.
+The codes to implement the MC simulations are publicly accessible at <span style = "color: blue;"> github account</span>.
+
+## Performance Measurement
+
+For a given simulation round, we calculate root mean squared error (RMSE) of yield and EONR predictions and profit deficit for each approach.
+Profit deficit is defined as the true maximum profit less the profit obtained by following the estimated site-specifc EONR.
+To calculate these measures for a given simulation round, the dataset from another simulation round is used as the test dataset.
+This practice works as datasets across simulation rounds are created independently while following the same data generating process.
 

### 2022-02-09 Writing/manuscript.rmd
title changed

@@
 ---
-title: "Comparing Machine Learning and Traditional Regression Methods in Site-Specific Economically Optimal Nitrogen Rate Prediction"
+title: "Pitfall of Prediction-orienterd Machined Learning Models and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
 author:

### 2022-02-09 Codes/3_make_figures_tables.R
write a part of the Introduction

@@ -5,10 +5,10 @@
 #' # fig.id = "field-layout",
 #' # fig.cap = "Simulated field layout with spatial unit definitions",
 #' # fig.dim = c(6, 6)
-#' 
+#'
 #' field_with_design <- readRDS(here("Data/field_with_design.rds"))
 #' field_sf <- field_with_design[1, ]$field_sf[[1]]
-#' 
+#'
 #' plot_sf <-
 #'   field_sf %>%
 #'   nest_by(plot_id) %>%
@@ -17,7 +17,7 @@
 #'   )) %>%
 #'   unnest() %>%
 #'   st_as_sf()
-#' 
+#'
 #' block_sf <-
 #'   field_sf %>%
 #'   nest_by(block_id) %>%
@@ -26,9 +26,9 @@
 #'   )) %>%
 #'   unnest() %>%
 #'   st_as_sf()
-#' 
+#'
 #' block_text_sf <- st_centroid(block_sf)
-#' 
+#'
 #' #* Field: plots and blocks
 #' g_field <-
 #'   ggplot() +
@@ -49,10 +49,10 @@
 #'   ) +
 #'   theme_void() +
 #'   ggtitle("Panel (a): Plots and blocks in an experimental field")
-#' 
+#'
 #' ## inside a plot
 #' plot_sf_focus <- filter(field_sf, plot_id == 1)
-#' 
+#'
 #' subplot_sf <-
 #'   plot_sf_focus %>%
 #'   nest_by(aunit_id, buffer) %>%
@@ -67,11 +67,11 @@
 #'     paste0("subplot-", aunit_id - 1)
 #'   )) %>%
 #'   mutate(buf_or_not = ifelse(label == "buffer", "buffer", "subplot"))
-#' 
+#'
 #' subplot_text_sf <- st_centroid(subplot_sf)
-#' 
+#'
 #' site_sf <- plot_sf_focus[7, ]
-#' 
+#'
 #' g_inside_plot <-
 #'   ggplot() +
 #'   geom_sf(data = plot_sf_focus, size = 0.2, fill = NA) +
@@ -86,30 +86,30 @@
 #'     legend.text = element_text(size = 12)
 #'   ) +
 #'   ggtitle("Panel (b): Subplots, buffers, and sites in a single plot")
-#' 
+#'
 #' g_layout <- g_field / g_inside_plot
-#' 
+#'
 #' # /*===========================================================
 #' #' # Experimental Design
[…]

### 2022-02-09 Writing/manuscript.rmd
manuscript writing

--- 2022-02-08 Writing/manuscript.rmd
@@
 library(gridExtra)
+library(kableExtra)
+library(here)
 ```
@@
 # /*===========================================================
+
 #* source all the functions in the Functions folder
@@
 est_data <-
-  readRDS(here("Results", "est_result_ls_400.rds")) %>%
+  readRDS(here("Shared", "Results", "est_result_ls.rds")) %>%
   rbindlist() %>%
@@
 gdata <- est_data %>%
-  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv)] %>%
+  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv, rmse_eonr)] %>%
   #---field size---
@@
     profit_sd = sd(profit) %>% round(2),
-    rmse = mean(rmse_cv) %>% round(2),
-    rmse_sd = sd(rmse_cv) %>% round(2)
+    rmse_yield = mean(rmse_cv) %>% round(2),
+    rmse_yield_sd = sd(rmse_cv) %>% round(2),
+    rmse_eonr = mean(rmse_eonr) %>% round(2),
+    rmse_eonr_sd = sd(rmse_eonr) %>% round(2)
   ),
@@
 
-# Results
+# Results and Discussions
 
@@
 Machine learning methods perform better than traditional regression methods in yield prediction.
-The RMSE results for the out-of-sample yield prediction over the 1,000 simulations are displayed in Figure \@ref(fig:rmse-boxplot-pool).
+The RMSE results for the out-of-sample yield prediction over the 1,000 simulations are displayed in Figure \@ref(fig:rmse-yield-boxplot).
 
-- For the full field (37.3 ha) scenario, the average RMSE over 1,000 simulations is `r mean_data[field_size=="37.3 ha"&model=="RF", rmse] %>% round(2)` kg ha$^{-1}$ for the RF model, and `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse] %>% round(2)` kg ha$^{-1}$ for the BRF model, which are significantly smaller than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse] %>% round(2)` kg ha$^{-1}$) and SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse] %>% round(2)` kg ha$^{-1}$) models.
-If we give RF model the best data, its RMSE will be as small as `r mean_data[field_size=="37.3 ha"&model=="RF best", rmse] %>% round(2)` kg ha$^{-1}$.
+- For the full field (37.3 ha) scenario, the average RMSE over 1,000 simulations is `r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$ for the RF model, and `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$ for the BRF model, which are significantly smaller than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse_yield] %>% round(2)` kg ha$^{-1}$) and SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) models.
+If we give RF model the best data, its RMSE will be as small as `r mean_data[field_size=="37.3 ha"&model=="RF best", rmse_yield] %>% round(2)` kg ha$^{-1}$.
 - The trend of RMSE performance is robust to field sizes.
@@
 
+EONR prediction performances for different models are displayed in Figure \@ref(fig:rmse-eonr-boxplot).
+
 ## Profit performances
 
-Profit performance results for different models are displayed in Figure \@ref(fig:pi-boxplot-pool).
+Profit performance results for different models are displayed in Figure \@ref(fig:pi-boxplot).
 
@@
 
-# Discussions
-
-+ Yield prediction vs EONR prediction
-+ Statistical efficiency is money (SER vs LM)
-
-`r run_pagebreak()`
-
 # Conclusions
@@
 
-```{r rmse-boxplot-pool, fig.cap="The yield prediction performances of different models.", echo=FALSE, fig.width=7}
-rmse_boxplot_pool | pi_boxplot_pool
+```{r rmse-yield-boxplot, fig.cap="The yield prediction performances of different models.", echo=FALSE, fig.width=7}
+rmse_yield_boxplot
 ```
 
-```{r pi-boxplot-pool, fig.cap="The profit performances of different models.", echo=FALSE}
-pi_boxplot_pool
+```{r rmse-eonr-boxplot, fig.cap="The yield prediction performances of different models.", echo=FALSE, fig.width=7}
+rmse_eonr_boxplot
+```
+
+```{r pi-boxplot, fig.cap="The profit performances of different models.", echo=FALSE, fig.width=7}
+pi_boxplot
 ```
@@
 ```{r extreme-percent, echo=FALSE}
-knitr::kable(mean_data, format = "markdown", caption = "Summary Statistics")
+# knitr::kable(mean_data, format = "markdown", caption = "Summary Statistics") %>% 
+#  kable_styling(font_size = 3)
 ```

### 2022-02-09 Codes/3_figures.R

@@ -31,11 +31,73 @@ setwd(here())
 #' /*                         Load and Prepare Data                           */
 #' /*=========================================================================*/
 
+#*****************************   add EONR data     *****************************
+#* simulation results
+est_result_ls <-
+    readRDS(here("Shared/Results/est_result_ls_400.rds"))
+
+#* Read field data
+field_data <-
+    readRDS(here("Shared/Data/field_data.rds")) 
+
+#* Read field parameters
+field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
+
+
+#* for scenario i
+for(sc_i in 1:length(est_result_ls)){
+    
+    #* prices
+    pN <- field_data$pN[sc_i]
+    pCorn <- field_data$pCorn[sc_i]
+    #* field sf data
+    field_sf <- field_data$field_sf[[sc_i]]
+    #* field true parameters
+    field_pars <- field_parameters$field_pars[[sc_i]] %>% 
+        #--- True cell-level EONR ---#
+        .[, EONR := (pN / pCorn - b1) / (2 * b2)] %>%
+        .[, EONR := pmin(Nk, EONR)] %>%
+        .[, EONR := pmax(0, EONR)]
+    
+    #* aggregate EONR to aunit level
+    EONR_df <- field_pars %>% 
+        #---join aunit_id---
+        .[data.table(field_sf)[,.(cell_id, aunit_id)], on = "cell_id"] %>% 
+        #---aggregate ---
+        .[, .(EONR = mean(EONR)), by = .(sim, aunit_id)]
+    
+    #* add EONR data to est_result_ls
+    est_result_ls[[sc_i]] <- 
+        est_result_ls[[sc_i]] %>% 
+        mutate(
+            data = list(
+                left_join(data, EONR_df, by = c("sim", "aunit_id"))
+            )
+        ) %>% 
+        mutate(
+            perform = list(
+                data.table(data)[, .(rmse_eonr = mean((opt_N_hat - EONR)^2, 
+                                                      na.rm = TRUE) %>% sqrt()), 
+                                 by = sim] %>% 
+                    left_join(perform, ., by = c("sim"))
+            )
+        ) %>% 
+        mutate(
+            rmse_eonr = 
+                perform[, mean(rmse_eonr, na.rm = TRUE)]
+        )
+}
[…]

### 2022-02-09 Codes/3_make_figures_tables.R

@@ -133,7 +133,7 @@
 # /*===========================================================
 #' # Boxplot of profit
 # /*===========================================================
-# fig.id = "pi-boxplot-pool",
+# fig.id = "pi-boxplot",
 # fig.cap = "The profit performances of different models"
 
 #------ range of profit values ------#
@@ -143,7 +143,7 @@ yaxis_max <- gdata$profit %>% max()
 podg <- position_dodge(0.4)
 
 #------ boxplot ------#
-pi_boxplot_pool <- 
+pi_boxplot <- 
     gdata %>% 
     ggplot(data = ., 
        aes(x = field_size, y = profit, fill = model)) +
@@ -168,9 +168,9 @@ pi_boxplot_pool <-
     )
 
 # /*===========================================================
-#' # Boxplot of RMSE
+#' # Boxplot of yield RMSE
 # /*===========================================================
-# fig.id = "rmse-boxplot-pool",
+# fig.id = "rmse-yield-boxplot",
 # fig.cap = "The yield prediction performances of different models"
 
 #------ range of values ------#
@@ -182,7 +182,7 @@ yaxis_max <- gdata$rmse_cv %>% max()
 podg <- position_dodge(0.4)
 
 #------ boxplot ------#
-rmse_boxplot_pool <- 
+rmse_yield_boxplot <- 
     gdata %>% 
     ggplot(data = ., 
        aes(x = field_size, y = rmse_cv, fill = model)) +
@@ -205,6 +205,47 @@ rmse_boxplot_pool <-
         axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
         axis.text=element_text(color='black')
     )
+
+
+# /*===========================================================
+#' # Boxplot of EONR RMSE
+# /*===========================================================
+# fig.id = "rmse-eonr-boxplot",
+# fig.cap = "The yield prediction performances of different models"
+
+#------ range of values ------#
+value_ls <- seq(gdata[,min(rmse_eonr)/200] %>% floor()*200, 
+                gdata[,max(rmse_eonr)/200] %>% ceiling()*200, 
+                by = 200)
+yaxis_min <- gdata$rmse_cv %>% min()
+yaxis_max <- gdata$rmse_cv %>% max()
+podg <- position_dodge(0.4)
+
+#------ boxplot ------#
+rmse_eonr_boxplot <- 
+    gdata %>% 
+    ggplot(data = ., 
[…]

### 2022-02-09 Codes/Modules/figure_boxplot_rmse_eonr.R

@@ -1,0 +1,32 @@
+
+
+
+#------ range of values ------#
+value_ls <- seq(gdata[,min(rmse_eonr)/10] %>% floor()*10, 
+                gdata[,max(rmse_eonr)/10] %>% ceiling()*10, 
+                by = 10)
+
+
+#------ boxplot ------#
+podg <- position_dodge(0.25)
+ggplot(data = gdata, 
+       aes(x = field_size, y = rmse_eonr, fill = model)) +
+    stat_boxplot(geom = "errorbar", width = 0.25, position = podg) +
+    geom_boxplot(position = podg, width = 0.25, outlier.shape = NA) +
+    ylab('Out-of-Sample EONR Prediction RMSE (kg/ha)') +
+    xlab('') +
+    scale_y_continuous(breaks = value_ls, label = value_ls) +
+    theme_bw() +
+    theme(
+        panel.grid.minor.x = element_blank(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        legend.position='bottom',
+        legend.title = element_blank(),
+        legend.key.size = unit(0.4, 'cm'),
+        legend.text = element_text(margin = margin(r = 1, unit = "cm")),
+        legend.margin=margin(t = -0.5, unit='cm'),
+        axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
+        axis.text=element_text(color='black')
+    )
+

### 2022-02-09 Writing/manuscript.rmd

--- 2022-02-09 Writing/manuscript.rmd
@@
 ---
-title: "Comparing Machine Learning and Traditional Regression Methods in Site-Specific Economically Optimal Nitrogen Rate Prediction"
+title: "Pitfall of Prediction-orienterd Machine Learning Models and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
 author:
@@
 
+Prediction-oriented ML methods swept the field of optimal input management as if yield prediction is the ultimate goal. RF in particular is used a lot.
+
+Apply ML without any clear purposes of how to use the trained models.
+
 + Traditional vs ML (LM, SER better than RF and BRF)
@@
 + Statistical efficiency is money (SER vs LM)
+
+The main purpose of this study is to compare the performance of prediction-oriented ML methods and traditional linear regreression approaches in terms of the profitability of estimated site-specific nitrogen recommendation.
+Since the true site-specific EONR and maximum profit achievable is never observable for real fields, testing the statistical and economic properties of statistical methods have to rely on simulation analysis where the data generating process is known to the researcher.
+We conduct MC simualtions for three different field sizes to test the economic performance of linear model OLS, linear model SER, Random Fores, and Boosted Regression Forest, where the true yield follows a quadratic plateau functional form.
+
+We found that while the prediction-oriented ML methods (RF and BRF) perform much better than the traditional methods (LM and SER) in predicting yield level, they perform worse than the traditional methods (LM and SER) in predicting EONR and thus in profitability of site-specific EONR recommendation.
+SER in particular performs the best in profitability.
+The economic value of its statistical efficiency over the LM approach is not negligible at <span style = "color: blue;"> Xiafei, put numbers here </span>.
+Our results provide a cautionary tale for those who place unsubstantiated and blind trust in prediction-oriented ML methods and apply them when the accurate estimation of ceteris paribus causal impacts of the variable of interest is warranted.
 

### 2022-02-09 Codes/3_make_figures_tables.R
removed the ">>>>>>> origin/master" thing

@@ -143,7 +143,6 @@ yaxis_max <- gdata$profit %>% max()
 podg <- position_dodge(0.4)
 
 #------ boxplot ------#
-<<<<<<< HEAD
 pi_boxplot <- 
     gdata %>% 
     ggplot(data = ., 
@@ -167,8 +166,6 @@ pi_boxplot <-
         axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
         axis.text=element_text(color='black')
     )
-=======
-pi_boxplot_pool <-
   gdata %>%
   ggplot(
     data = .,
@@ -195,7 +192,6 @@ pi_boxplot_pool <-
     axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
     axis.text = element_text(color = "black")
   )
->>>>>>> origin/master
 
 # /*===========================================================
 #' # Boxplot of yield RMSE
@@ -213,7 +209,6 @@ yaxis_max <- gdata$rmse_cv %>% max()
 podg <- position_dodge(0.4)
 
 #------ boxplot ------#
-<<<<<<< HEAD
 rmse_yield_boxplot <- 
     gdata %>% 
     ggplot(data = ., 
@@ -237,7 +232,6 @@ rmse_yield_boxplot <-
         axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
         axis.text=element_text(color='black')
     )
-=======
 rmse_boxplot_pool <-
   gdata %>%
   ggplot(
@@ -263,7 +257,6 @@ rmse_boxplot_pool <-
     axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
     axis.text = element_text(color = "black")
   )
->>>>>>> origin/master
 
 
 # /*===========================================================

### 2022-02-10 Writing/manuscript.rmd
minor changes

@@
 ---
-title: "Pitfall of Prediction-orienterd Machine Learning Models and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
+title: "Pitfall of Prediction-orienterd Machine Learning Methods and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
 author:

### 2022-02-10 Writing/manuscript.rmd
results writing updates

--- 2022-02-09 Writing/manuscript.rmd
@@
 est_data <-
-  readRDS(here("Shared", "Results", "est_result_ls_400.rds")) %>%
+  readRDS(here("Shared", "Results", "est_result_ls.rds")) %>%
   rbindlist() %>%
@@
 #' rename columns
-gdata <- est_data %>%
-  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv)] %>%
+est_data <- est_data %>%
+  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv, rmse_eonr)] %>%
   #---field size---
@@
 #' mean and sd
-mean_data <- gdata %>%
+mean_data <- est_data %>%
   .[, .(
@@
 # /*----------------------------------*/
+gdata <- est_data
 source(here("GitControlled", "Codes", "3_make_figures_tables.R"))
@@
 y_i &= \beta_0 + \beta_1 \cdot N_i + \beta_2\cdot N_i^2 + N_i\cdot X_i\cdot \gamma_1 + N_i^2\cdot X_i\cdot \gamma_2 + \varepsilon \\
-\varepsilon & = \lambda W \mu
+\varepsilon & = \lambda W \varepsilon + \mu
 \end{aligned}
@@
 
-# Results
+### Yield prediction
 
-## Yield predictions
-Machine learning methods perform better than traditional regression methods in yield prediction.
-The RMSE results for the out-of-sample yield prediction over the 1,000 simulations are displayed in Figure \@ref(fig:rmse-boxplot-pool).
+Root-mean-square error (RMSE) of yield prediction for a given simulation round is:
 
-- For the full field (37.3 ha) scenario, the average RMSE over 1,000 simulations is `r mean_data[field_size=="37.3 ha"&model=="RF", rmse] %>% round(2)` kg ha$^{-1}$ for the RF model, and `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse] %>% round(2)` kg ha$^{-1}$ for the BRF model, which are significantly smaller than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse] %>% round(2)` kg ha$^{-1}$) and SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse] %>% round(2)` kg ha$^{-1}$) models.
-If we give RF model the best data, its RMSE will be as small as `r mean_data[field_size=="37.3 ha"&model=="RF best", rmse] %>% round(2)` kg ha$^{-1}$.
-- The trend of RMSE performance is robust to field sizes.
-For smaller field sizes, the overall levels of RMSE are slightly larger (of course), but machine learning models' RMSE (RF and BRF) are consistently smaller than the RMSE of traditional regression models (LM and SER).
+$$
+\begin{aligned}
+RMSE = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{y}_i - y_i)^2}
+\end{aligned}
+$$
+where $y_i$ is the true yield of location $i$ from applying the trial N rate, and $\hat{y}_i$ is the predicted yield of the same location by a certain model.
+The total number of locations for that simulated trial field is $n$.
 
-The finding of machine learning models' better yield prediction performances is consistent with existing literature (**citations**).
+### EONR prediction
 
-## 
-RF and BRF models have better yield predictions.  So what?
+Root-mean-square error (RMSE) of EONR prediction for a given simulation round is:
 
-Better yield prediction does not necessarily translate into better EONR
+$$
+\begin{aligned}
+RMSE = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{EONR}_i - EONR_i)^2}
+\end{aligned}
+$$
+where $EONR_i$ is the true economically optimal nitrogen rate of location $i$, and $\hat{EONR}_i$ is the predicted EONR for location $i$ by a certain model.
+The total number of locations for that simulated trial field is $n$.
 
-## Profit performances
+### Profit
 
-Profit performance results for different models are displayed in Figure \@ref(fig:pi-boxplot-pool).
+The production profit of location $i$ by applying the estimated site-specific EONR is:
 
-- The average profit from EONR predicted by RF model is $\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$ over 1,000 simulations for the full field data.
-That is really low.
-The BRF model is better, with profit of $\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$.
-But those are still significantly lower than even the LM model ($\$$`r mean_data[field_size=="37.3 ha"&model=="LM", profit] %>% round(2)` ha$^{-1}$).
-The SER model has the highest profit of $\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$.
+$$
+\begin{aligned}
+\pi_i = p_{corn} f(\hat{EONR}_i) - p_N N_i - C
+\end{aligned}
+$$
+where $f()$ is the true yield response function set by the simulation.
+
+The field-level profit is measured as:
+
+$$
+\begin{aligned}
+\pi = {\frac{1}{n} \sum_{i=1}^{n} (\pi_i - \pi_i^{*})}
+\end{aligned}
+$$
+where $\pi_i^{*}$ is the true maximum profit of location $i$:
+
+$$
+\begin{aligned}
+\pi_i^{*} = p_{corn} f(EONR_i) - p_N N_i - C
+\end{aligned}
+$$
+It is a relative profit measure compared the true maximum. So $\pi$ is always negative.
+
+# Results and Discussions
+
+## Main point 1:
+Despite machine learning models perform better in yield predicting, their EONR prediction is poor.
+
+The performances of different models in out-of-sample yield prediction, EONR prediction, and EONR profitability over 1,000 simulations are displayed in Figure \@ref(fig:comb-boxplot-large) for the large trial field (37.3 ha) scenario.
+
+- Indeed, the simulation results showed the machine learning models perform better than traditional regression models in yield predicting.
+On average, the predicted yields' RMSE of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$) and BRF (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$) models are significantly smaller than that of the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse_yield] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) model.
+Those findings are consistent with existing literature (**citations**).
+- However, the better yield prediction of machine learning models does not necessarily translate into better EONR prediction.
+The predicted EONR's RMSE of the RF model (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is much larger than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse_eonr] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$) model, meaning the RF model generates much inaccurate EONR predictions, despite its more accurate yield predictions, than LM or SER model.
+BRF model's EONR prediction is much better than RF model, whose RMSE (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is only slightly smaller than the LM model.
+But it is still significantly larger than the SER model.
+- Finally, the less accurate EONR predictions by machine learning models lead to lower profits.
+The average profit of RF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) is extremely low.
+The BRF model profit ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) is much higher than RF, but still significantly lower than the basic LM model ($\$$`r mean_data[field_size=="37.3 ha"&model=="LM", profit] %>% round(2)` ha$^{-1}$).
+The SER model profit is as high as $\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$.
+
+So, we should be cautious about the pitfall of machine learning models' good yield predicting performances.
+Almost all existing studies use yield prediction performance as the measure of yield estimation models.
+This can be very misleading and cost producers a lot when it is used in developing input management recommendations, since models with good yield prediction can have bad profit at the same time.
+
+## Main point 2:
+The model performances are generally robust to field sizes. But we also found that machine learning models' performances are less affected by field size reduction.
+
+The simulation results for medium (18.7 ha) and small (9.3 ha) trial field scenarios are displayed in Figure \@ref(fig:comb-boxplot-medium) and \@ref(fig:comb-boxplot-small).
+
+- The RF model still has better yield prediction while worse EONR prediction and profit than the LM and SER models.
+- The BRF model outperforms LM model in EONR prediction and profit in medium and small trial fields. 
+- Though the BRF model still cannot beat SER model in smaller fields, the gap between BRF and SER shrink as field size reduces.
+For the small field (9.3 ha), BRF's predicted EONR RMSE (`r mean_data[field_size=="9.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is almost as small as that of the SER model (`r mean_data[field_size=="9.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$), and the profit gap between the BRF model (`r mean_data[field_size=="9.3 ha"&model=="BRF", profit] %>% round(2)` kg ha$^{-1}$) and the SER model (`r mean_data[field_size=="9.3 ha"&model=="BRF", profit] %>% round(2)` kg ha$^{-1}$) reduces to only about two thirds of the large field (37.3 ha) scenario.
+
+So, the better economic performances of traditional regression models require larger trial field sizes.
+Machine learning models' performances are less sensitive to field sizes.
+At the current prevailing on-farm experimental field sizes, traditional regression models perform well.
+But if the trial fields are really small, machine learning models (especially BRF) will be more suitable.
+
+## Main point 3:
+EONR prediction and profit is not perfectly one-on-one corresponding.
+
+Lots of agronomy studies use predicted EONR vs "true" EONR as the criteria to evaluate input recommendation algorithms. ("true" EONR is from yield responses estimated from trial data)
+
+## Main point 4:
+RF model is bad.
+
 - Even if we "cheat" and feed RF model with the best data, its profit is still only $\$$`r mean_data[field_size=="37.3 ha"&model=="RF best", profit] %>% round(2)` ha$^{-1}$ 
-- For smaller field sizes, the overall levels of profit decrease, which is not surprising as model estimations become less accurate with smaller sample sizes.
-But the general trend of profit performance across models is robust to field sizes.
-- The relative performance of BRF profit improves when field size reduces.
-For the small (9.3 ha) and medium (18.7 ha) sized fields, the BRF profit outperforms LM model.
-The profit gap between BRF and SER models also reduces from $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ of large field to $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ of medium field and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ of small field.
-That may suggests machine learning is more useful for smaller field's data.
+If we estimate RF model with the best data, its RMSE will be further smaller (`r mean_data[field_size=="37.3 ha"&model=="RF best", rmse_yield] %>% round(2)` kg ha$^{-1}$).
 
-`r run_pagebreak()`
+## Main point 5:
+LM vs. SER: Statistical efficiency is money.
 
-# Discussions
-
-+ Yield prediction vs EONR prediction
-+ Statistical efficiency is money (SER vs LM)
+We should be more actively use SER model in yield response estimation.
 
@@
 
-```{r rmse-boxplot-pool, fig.cap="The yield prediction performances of different models.", echo=FALSE, fig.width=7}
-rmse_boxplot_pool | pi_boxplot_pool
+```{r comb-boxplot-large, fig.cap="The performances of different models, large field.", echo=FALSE, fig.width=6}
+comb_boxplot_large
 ```
 
-```{r pi-boxplot-pool, fig.cap="The profit performances of different models.", echo=FALSE}
-pi_boxplot_pool
+```{r comb-boxplot-medium, fig.cap="The performances of different models, medium field.", echo=FALSE, fig.width=6}
+comb_boxplot_medium
+```
+
+```{r comb-boxplot-small, fig.cap="The performances of different models, small field.", echo=FALSE, fig.width=6}
+comb_boxplot_small
 ```
@@
 ```{r extreme-percent, echo=FALSE}
-knitr::kable(mean_data, format = "markdown", caption = "Summary Statistics")
+# knitr::kable(mean_data, format = "markdown", caption = "Summary Statistics")
 ```

### 2022-02-10 Codes/3_figures.R

@@ -117,10 +117,10 @@ est_data <- est_data %>%
     #---model name---
     .[model=="brf", model := "BRF"] %>%
     .[model=="rf", model := "RF"] %>%
-    .[model=="rf_perfect", model := "RF_PERFECT"] %>%
+    .[model=="rf_perfect", model := "RF best"] %>%
     .[model=="lm", model := "OLS"] %>%
     .[model=="ser_50", model := "SER"] %>%
-    .[, model := factor(model, levels = c("RF", "RF_PERFECT", "BRF", "OLS", "SER"))] %>% 
+    .[, model := factor(model, levels = c("RF", "RF best", "BRF", "OLS", "SER"))] %>% 
     print()
 
 
@@ -181,6 +181,29 @@ mean_data <- gdata %>%
     by=c("field_size", "model")] %>% 
     .[order(field_size, model), ] %>% 
     print()
+
+# ----------------
+# combined boxplot
+# ----------------
+gdata_long <- est_data %>% 
+    .[, .(field_size, model, sim, rmse_cv, rmse_eonr, profit)] %>% 
+    #=== Wide to Long: melt()
+    melt(id.vars = c('field_size','model','sim')) %>% 
+    #--- label field size ---#
+    .[field_size=="9.3 ha", fsize := "small"] %>% 
+    .[field_size=="18.7 ha", fsize := "medium"] %>% 
+    .[field_size=="37.3 ha", fsize := "large"] %>% 
+    print()
+for(s in unique(gdata_long$fsize)){
+    gdata <- gdata_long[fsize==s]
+    source(here("GitControlled/Codes/Modules/figure_boxplot_combined.R"))
+    ggsave(file = here("GitControlled", "Graphs", 
+                       paste0("combined_boxplot_", s, ".png")),
+           height=6,width=6.5)
+}
+
+
+
 
 
 

### 2022-02-10 Codes/3_make_figures_tables.R

@@ -1,14 +1,14 @@
-
+#' 
 #' # /*===========================================================
 #' #' # Visualization the field and spatial units
 #' # /*===========================================================
 #' # fig.id = "field-layout",
 #' # fig.cap = "Simulated field layout with spatial unit definitions",
 #' # fig.dim = c(6, 6)
-#'
+#' 
 #' field_with_design <- readRDS(here("Data/field_with_design.rds"))
 #' field_sf <- field_with_design[1, ]$field_sf[[1]]
-#'
+#' 
 #' plot_sf <-
 #'   field_sf %>%
 #'   nest_by(plot_id) %>%
@@ -17,7 +17,7 @@
 #'   )) %>%
 #'   unnest() %>%
 #'   st_as_sf()
-#'
+#' 
 #' block_sf <-
 #'   field_sf %>%
 #'   nest_by(block_id) %>%
@@ -26,9 +26,9 @@
 #'   )) %>%
 #'   unnest() %>%
 #'   st_as_sf()
-#'
+#' 
 #' block_text_sf <- st_centroid(block_sf)
-#'
+#' 
 #' #* Field: plots and blocks
 #' g_field <-
 #'   ggplot() +
@@ -49,10 +49,10 @@
 #'   ) +
 #'   theme_void() +
 #'   ggtitle("Panel (a): Plots and blocks in an experimental field")
-#'
+#' 
 #' ## inside a plot
 #' plot_sf_focus <- filter(field_sf, plot_id == 1)
-#'
+#' 
 #' subplot_sf <-
 #'   plot_sf_focus %>%
 #'   nest_by(aunit_id, buffer) %>%
@@ -67,11 +67,11 @@
 #'     paste0("subplot-", aunit_id - 1)
 #'   )) %>%
 #'   mutate(buf_or_not = ifelse(label == "buffer", "buffer", "subplot"))
-#'
+#' 
 #' subplot_text_sf <- st_centroid(subplot_sf)
-#'
+#' 
 #' site_sf <- plot_sf_focus[7, ]
-#'
+#' 
 #' g_inside_plot <-
 #'   ggplot() +
 #'   geom_sf(data = plot_sf_focus, size = 0.2, fill = NA) +
@@ -86,49 +86,158 @@
 #'     legend.text = element_text(size = 12)
 #'   ) +
 #'   ggtitle("Panel (b): Subplots, buffers, and sites in a single plot")
-#'
+#' 
 #' g_layout <- g_field / g_inside_plot
-#'
-#' # /*===========================================================
[…]

### 2022-02-10 Writing/manuscript.rmd

@@
 
-### Profit
-
-The production profit of location $i$ by applying the estimated site-specific EONR is:
+## Profit performances
 

### 2022-02-19 Writing/manuscript.rmd
results updates (figures, writing)

--- 2022-02-10 Writing/manuscript.rmd
@@
   .[model == "rf", model := "RF"] %>%
-  .[model == "rf_perfect", model := "RF best"] %>%
-  .[model == "lm", model := "LM"] %>%
+  .[model == "rf_perfect", model := "RF_b"] %>%
+  .[model == "lm", model := "OLS"] %>%
   .[model == "ser_50", model := "SER"] %>%
-  .[, model := factor(model, levels = c("RF", "RF best", "BRF", "LM", "SER"))]
+  .[, model := factor(model, levels = c("RF", "RF_b", "BRF", "OLS", "SER"))]
 #' mean and sd
@@
   .[order(field_size, model), ]
+#' load illustration data (single simulation)
+illus_data <-
+  readRDS(here("Shared", "Results", "illus_data.rds"))
 
@@
 # /*----------------------------------*/
-gdata <- est_data
 source(here("GitControlled", "Codes", "3_make_figures_tables.R"))
@@
 
-+ Traditional vs ML (LM, SER better than RF and BRF)
++ Traditional vs ML (OLS, SER better than RF and BRF)
 + Yield prediction vs EONR prediction
-+ Statistical efficiency is money (SER vs LM)
++ Statistical efficiency is money (SER vs OLS)
 
-The main purpose of this study is to compare the performance of prediction-oriented ML methods and traditional linear regreression approaches in terms of the profitability of estimated site-specific nitrogen recommendation.
+The main purpose of this study is to compare the performance of prediction-oriented ML methods and traditional linear regression approaches in terms of the profitability of estimated site-specific nitrogen recommendation.
 Since the true site-specific EONR and maximum profit achievable is never observable for real fields, testing the statistical and economic properties of statistical methods have to rely on simulation analysis where the data generating process is known to the researcher.
-We conduct MC simualtions for three different field sizes to test the economic performance of linear model OLS, linear model SER, Random Fores, and Boosted Regression Forest, where the true yield follows a quadratic plateau functional form.
+We conduct MC simulations for three different field sizes to test the economic performance of linear model OLS, linear model SER, Random Fores, and Boosted Regression Forest, where the true yield follows a quadratic plateau functional form.
 
-We found that while the prediction-oriented ML methods (RF and BRF) perform much better than the traditional methods (LM and SER) in predicting yield level, they perform worse than the traditional methods (LM and SER) in predicting EONR and thus in profitability of site-specific EONR recommendation.
+We found that while the prediction-oriented ML methods (RF and BRF) perform much better than the traditional methods (OLS and SER) in predicting yield level, they perform worse than the traditional methods (OLS and SER) in predicting EONR and thus in profitability of site-specific EONR recommendation.
 SER in particular performs the best in profitability.
-The economic value of its statistical efficiency over the LM approach is not negligible at <span style = "color: blue;"> Xiafei, put numbers here </span>.
+The economic value of its statistical efficiency over the OLS approach is not negligible at <span style = "color: blue;"> Xiafei, put numbers here </span>.
 Our results provide a cautionary tale for those who place unsubstantiated and blind trust in prediction-oriented ML methods and apply them when the accurate estimation of ceteris paribus causal impacts of the variable of interest is warranted.
@@
 
-In our Monte Carlo simulations, we will test five estimation approches on three different sizes of fields: x ha, y ha, and x ha.
+In our Monte Carlo simulations, we will test five estimation approaches on three different sizes of fields: x ha, y ha, and x ha.
 In this section, we describe the data generating process, estimation approaches, and model evaluation.
@@
 
-Data were generated at the cell-level and then aggregted up to analysis-unit levle (why). Cell-levle yields were generated following the quadratic-plateau functional form as follows:
+Data were generated at the cell-level and then aggregated up to analysis-unit level (why). Cell-level yields were generated following the quadratic-plateau functional form as follows:
 
@@
   \alpha_{i,j} + \beta_{i,j} N + \gamma_{i,j} N^2 + \varepsilon_{i,j}, & N < \tau_{i,j} \\
-  \eta_{i,j}, & N \geq \tau_{i,j}
+  \eta_{i,j} + \varepsilon_{i,j}, & N \geq \tau_{i,j}
   \end{cases}
@@
 
-In this formualtion, yield increases as $N_{i,j}$ increaes until $N_{i,j}$ reaches $\tau_{i,j}$, at which yield hits the plateau, $\eta_{i,j}$.
+In this formulation, yield increases as $N_{i,j}$ increase until $N_{i,j}$ reaches $\tau_{i,j}$, at which yield hits the plateau, $\eta_{i,j}$.
 The yield level at $N_{i,j}= 0$ is $\alpha_{i,j}$.
-The rate at which yield increases with repsect to $N_{i,j}$ is governed by $\beta_{i,j}$ and $\gamma_{i,j}$.
+The rate at which yield increases with respect to $N_{i,j}$ is governed by $\beta_{i,j}$ and $\gamma_{i,j}$.
 
-Farmers do not observe any of the parameters, but observe the decomposition of the parameters that goven the yield resopnse function. Specifically,
+Farmers do not observe any of the parameters, but observe the decomposition of the parameters that given the yield response function. Specifically,
 
@@
 
-In addition to the covariates, two nuisance covariates that are correlated with eahc of $\alpha_{i,j}$, $\tau_{i,j}$, and $\eta_{i,j}$ are generated: $\phi^{\alpha, 1}_{i,j}$, $\phi^{\alpha, 2}_{i,j}$, $\phi^{\tau, 1}_{i,j}$, $\phi^{\tau, 2}_{i,j}$, $\phi^{\eta, 1}_{i,j}$, $\phi^{\eta, 2}_{i,j}$.
+In addition to the covariates, two nuisance covariates that are correlated with each of $\alpha_{i,j}$, $\tau_{i,j}$, and $\eta_{i,j}$ are generated: $\phi^{\alpha, 1}_{i,j}$, $\phi^{\alpha, 2}_{i,j}$, $\phi^{\tau, 1}_{i,j}$, $\phi^{\tau, 2}_{i,j}$, $\phi^{\eta, 1}_{i,j}$, $\phi^{\eta, 2}_{i,j}$.
 We denote these variables as $X^2_{i,j}$.
@@
 
-**Approach 1**: Linear Model OLS (Hereafter, LM)
+**Approach 1**: Linear Model OLS (Hereafter, OLS)
 
-The LM approach assumes a quadratic yield response function:
+The OLS approach assumes a quadratic yield response function:
 
@@
 
-The econometic model for the SER approach follows that of the LM approach except for the error term.
+The econometic model for the SER approach follows that of the OLS approach except for the error term.
 
@@
 where $\lambda$ is scaler that reflects the degree of spatial dependence, $W$ is the user-defined weight matrix, and $\mu$ is the idiosynctaric error term that is not spatially correlated.
-Estimation via the spatial error model takes into account the spatial dependency of the error term and thus statistically more  efficient than the LM approach.
+Estimation via the spatial error model takes into account the spatial dependency of the error term and thus statistically more  efficient than the OLS approach.
 The _spatialreg_ package in R was used to estimate the model (cite).
@@
 
-Unlike the LM and SER approaches, it does not assume any particular functional relationships between the dependent vairable and the covaraites.
+Unlike the OLS and SER approaches, it does not assume any particular functional relationships between the dependent vairable and the covaraites.
 Random Forest consists of ensembles of trees.
@@
 However, its use in the context of site-specific input management is limited compared to RF at the moment.
-The BRF approach uses all the covaraites in $X$ like the LM, SER, and RF approaches.
+The BRF approach uses all the covaraites in $X$ like the OLS, SER, and RF approaches.
 The _grf_ package in R was used to run the RF, RF$_{best}$, and BRF estimations (cite).
@@
 \begin{aligned}
-RMSE = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{y}_i - y_i)^2}
+RMSE_{y} = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{y}_i - y_i)^2}
 \end{aligned}
@@
 \begin{aligned}
-RMSE = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{EONR}_i - EONR_i)^2}
+RMSE_{EONR} = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{EONR}_i - EONR_i)^2}
 \end{aligned}
@@
 
-## Main point 1:
-Despite machine learning models perform better in yield predicting, their EONR prediction is poor.
+## EONR prediction
 
-The performances of different models in out-of-sample yield prediction, EONR prediction, and EONR profitability over 1,000 simulations are displayed in Figure \@ref(fig:comb-boxplot-large) for the large trial field (37.3 ha) scenario.
+The performances of machine learning and traditional regression models from 1,000 simulations were compared in Figure \@ref(fig:comb-boxplot-all).
+Three performance measurements: (1) out-of-sample yield prediction, (2) out-of-sample EONR prediction, and (3) profit resultant from the predicted EONR.
 
-- Indeed, the simulation results showed the machine learning models perform better than traditional regression models in yield predicting.
-On average, the predicted yields' RMSE of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$) and BRF (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$) models are significantly smaller than that of the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse_yield] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) model.
-Those findings are consistent with existing literature (**citations**).
-- However, the better yield prediction of machine learning models does not necessarily translate into better EONR prediction.
-The predicted EONR's RMSE of the RF model (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is much larger than the LM (`r mean_data[field_size=="37.3 ha"&model=="LM", rmse_eonr] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$) model, meaning the RF model generates much inaccurate EONR predictions, despite its more accurate yield predictions, than LM or SER model.
-BRF model's EONR prediction is much better than RF model, whose RMSE (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is only slightly smaller than the LM model.
-But it is still significantly larger than the SER model.
-- Finally, the less accurate EONR predictions by machine learning models lead to lower profits.
-The average profit of RF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) is extremely low.
-The BRF model profit ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) is much higher than RF, but still significantly lower than the basic LM model ($\$$`r mean_data[field_size=="37.3 ha"&model=="LM", profit] %>% round(2)` ha$^{-1}$).
-The SER model profit is as high as $\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$.
+Table of winner counts.
+
+Look at the large field (37.3 ha) scenario in panel (A) of Figure \@ref(fig:comb-boxplot-all).
+
+- Indeed, the simulation results showed that machine learning models have better yield predictions than traditional regression models.
+On average, the out-of-sample predicted yields' RMSE of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$) and BRF (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$) models were significantly smaller than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_yield] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) model.
+Those results are consistent with existing literature (**citations**).
+- However, the better yield prediction of machine learning models does not translate into better EONR prediction.
+The average RMSE of out-of-sample predicted EONR of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was much larger than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_eonr] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$) model.
+BRF model's EONR prediction (RMSE `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was better than RF model, which was similar to OLS model, but was still significantly worse than SER model.
+Those results showed that, despite machine learning models have better yield prediction, their EONR prediction is worse than traditional regression models.
+- Ultimately, the worse EONR prediction of machine learning models resulted in lower production profit compared to the traditional regression models.
+The 1,000-simulation average profit of RF ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) or BRF ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) model is significantly lower than that of OLS ($\$$`r mean_data[field_size=="37.3 ha"&model=="OLS", profit] %>% round(2)` ha$^{-1}$) or SER ($\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$) model.
+
+## RF model is bad
+
+- Within the machine learning models, the RF model performs especially poor in EONR prediction. Its EONR prediction RMSE was much larger than BRF model, and its associated profit was extremely low. 
+- Even if we "cheat" and feed RF model with the best possible data (the true yield response parameters), its EONR prediction (RMSE `r mean_data[field_size=="37.3 ha"&model=="RF_b", rmse_eonr] %>% round(2)` kg ha$^{-1}$) and profit performance ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF_b", profit] %>% round(2)` ha$^{-1}$) were still slightly worse than BRF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) with observed data.
+- Note that RF is currently a very popular machine learning method used by many agricultural studies.
+Our simulation results showed that although RF may be OK for yield prediction, it is terrible in EONR prediction, and will cause big economic loss if using it in decision making.
+Even after spending great efforts (and costs) to obtain the perfect information, using RF model still won't achieve good economic performance.
+
+## Field sizes
+
+Figure \@ref(fig:comb-boxplot-all) panels (B) and (C) showed the simulation results for medium (18.7 ha) and small (9.3 ha) fields.
+
+- The result pattern of model performances was generally robust to field sizes.
+For any sized field, the machine learning models still have better yield predictions while worse economic performances than traditional regression models.
+- But we do notice that machine learning models' economic performances catch up when field size decreases.
+Especially, BRF model outperformed OLS model in EONR prediction and profit performance in small and medium fields.
+Although BRF model still cannot win SER in profit performance, its profit gap between SER reduced from $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in large field to $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in medium field and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in small field.
+- The results may suggest machine learning models (especially BRF) are more desirable in small fields' EONR predictions.
+But under the context of current farming practice, most production fields are larger than the smallest field (9.3 ha) scenario of our simulation, SER model is economically best option.
+
+## Illustrative explanation
+
+- One simulation example (cherry picking, similar to the mean pattern)
+
+- One location's yield response curves
+
+- Treatment effects
+
+short summary:
 
@@
 
-## Main point 2:
-The model performances are generally robust to field sizes. But we also found that machine learning models' performances are less affected by field size reduction.
+## OLS vs. SER: Statistical efficiency is money.
 
-The simulation results for medium (18.7 ha) and small (9.3 ha) trial field scenarios are displayed in Figure \@ref(fig:comb-boxplot-medium) and \@ref(fig:comb-boxplot-small).
+We should be more actively use SER model in yield response estimation.
 
-- The RF model still has better yield prediction while worse EONR prediction and profit than the LM and SER models.
-- The BRF model outperforms LM model in EONR prediction and profit in medium and small trial fields. 
-- Though the BRF model still cannot beat SER model in smaller fields, the gap between BRF and SER shrink as field size reduces.
-For the small field (9.3 ha), BRF's predicted EONR RMSE (`r mean_data[field_size=="9.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) is almost as small as that of the SER model (`r mean_data[field_size=="9.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$), and the profit gap between the BRF model (`r mean_data[field_size=="9.3 ha"&model=="BRF", profit] %>% round(2)` kg ha$^{-1}$) and the SER model (`r mean_data[field_size=="9.3 ha"&model=="BRF", profit] %>% round(2)` kg ha$^{-1}$) reduces to only about two thirds of the large field (37.3 ha) scenario.
-
-So, the better economic performances of traditional regression models require larger trial field sizes.
-Machine learning models' performances are less sensitive to field sizes.
-At the current prevailing on-farm experimental field sizes, traditional regression models perform well.
-But if the trial fields are really small, machine learning models (especially BRF) will be more suitable.
-
-## Main point 3:
-EONR prediction and profit is not perfectly one-on-one corresponding.
+## EONR prediction and profit is not perfectly one-to-one corresponding. (perhaps too much; remove this point)
 
@@
 
-## Main point 4:
-RF model is bad.
-
-- Even if we "cheat" and feed RF model with the best data, its profit is still only $\$$`r mean_data[field_size=="37.3 ha"&model=="RF best", profit] %>% round(2)` ha$^{-1}$ 
-If we estimate RF model with the best data, its RMSE will be further smaller (`r mean_data[field_size=="37.3 ha"&model=="RF best", rmse_yield] %>% round(2)` kg ha$^{-1}$).
-
-## Main point 5:
-LM vs. SER: Statistical efficiency is money.
-
-We should be more actively use SER model in yield response estimation.
+illustrative figure:
 
@@
 
+`r run_pagebreak()`
+
 # Figures {-}
 
-```{r comb-boxplot-large, fig.cap="The performances of different models, large field.", echo=FALSE, fig.width=6}
-comb_boxplot_large
+`r run_pagebreak()`
+
+```{r comb-boxplot-all, fig.cap="The estimation performances of machine learning models (RF, RF_b, BRF) and traditional regression models (OLS, SER) over 1,000 simulations for: (A) large field (37.3 ha), (B) medium field (18.7 ha), and (C) small field (9.3 ha).
+The performance measurements include: (1) out-of-sample yield prediction RMSE, (2) out-of-sample EONR prediction RMSE, and (3) profit resultant from the predicted EONR.", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
+(comb_boxplot_large + ggtitle("(A) large field")) / (comb_boxplot_medium + ggtitle("(B) medium field")) / (comb_boxplot_small + ggtitle("(C) small field"))
 ```
 
-```{r comb-boxplot-medium, fig.cap="The performances of different models, medium field.", echo=FALSE, fig.width=6}
-comb_boxplot_medium
+```{r single-simu-yield, fig.cap="Example simulation, yield.", fig.width=6, fig.height=7.5, echo=FALSE, cache=FALSE}
+single_simu_yield
 ```
 
-```{r comb-boxplot-small, fig.cap="The performances of different models, small field.", echo=FALSE, fig.width=6}
-comb_boxplot_small
+```{r single-simu-EONR, fig.cap="Example simulation, EONR", fig.width=6, fig.height=7.5, echo=FALSE, cache=FALSE}
+single_simu_EONR
 ```

### 2022-02-19 Codes/1_gwr_simulation.R

@@ -1,54 +1,0 @@
-# /*===========================================================
-#' # MC simulation
-# /*===========================================================
-mc_sim_results <-
-  lapply(
-    1:nrow(field_with_design), # indices to loop over
-    function(x) {
-
-      # ! things to do
-      #* 1. estimate GWR and optimal N
-      #* 2. estimate BRF and optimal N
-
-      w_data <- field_with_design[x, ]
-
-      # ! for debugging
-      # data <- sim_results$data[[1]]
-      # pCorn <- sim_results$pCorn[[1]]
-      # pN <- sim_results$pN[[1]]
-      # sim <- sim_results$sim[[1]]
-      # N_levels <- sim_results$N_levels[[1]]
-
-      sim_results <-
-        #* read the right regression data for this
-        #* experimental setting from the data_file_name
-        readRDS(here(w_data$data_file_name)) %>%
-        dplyr::select(reg_data, pCorn, pN) %>%
-        unnest() %>%
-        rowwise() %>%
-        # ! MC simulations
-        mutate(mc_results = list(
-          tryCatch(
-            mc_simulate(
-              data = data,
-              pCorn = pCorn,
-              pN = pN,
-              sim = sim,
-              N_levels = N_levels
-            ),
-            error = function(e) NULL
-          )
-        )) %>%
-        dplyr::select(sim, mc_results)
-
-      results_return <-
-        w_data %>%
-        mutate(sim_results = list(sim_results))
-
-      return(results_return)
-    }
-  ) %>%
-  rbindlist()
-
-#* save the field parameters
-saveRDS(mc_sim_results, here("Results/mc_sim_results.rds"))

### 2022-02-19 Codes/3_figures.R

@@ -20,96 +20,37 @@ library(dplyr)
 library(tidyr)
 library(tidyverse)
 library(modelsummary)
+library(tictoc)
 library(here)
 theme_set(theme_bw())
 
 #* set working directory
 setwd(here())
 
+#* source all the R functions in the Functions/R folder
+fs::dir_ls(here("GitControlled", "Codes", "Functions", "R"), full.names = TRUE) %>%
+    purrr::map(~ source(.))
+
 
 #' /*=========================================================================*/
 #' /*                         Load and Prepare Data                           */
 #' /*=========================================================================*/
 
-#*****************************   add EONR data     *****************************
-#* simulation results
-est_result_ls <-
-    readRDS(here("Shared/Results/est_result_ls_400.rds"))
-
-#* Read field data
-field_data <-
-    readRDS(here("Shared/Data/field_data.rds")) 
-
-#* Read field parameters
-field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
-
-
-#* for scenario i
-for(sc_i in 1:length(est_result_ls)){
-    
-    #* prices
-    pN <- field_data$pN[sc_i]
-    pCorn <- field_data$pCorn[sc_i]
-    #* field sf data
-    field_sf <- field_data$field_sf[[sc_i]]
-    #* field true parameters
-    field_pars <- field_parameters$field_pars[[sc_i]] %>% 
-        #--- True cell-level EONR ---#
-        .[, EONR := (pN / pCorn - b1) / (2 * b2)] %>%
-        .[, EONR := pmin(Nk, EONR)] %>%
-        .[, EONR := pmax(0, EONR)]
-    
-    #* aggregate EONR to aunit level
-    EONR_df <- field_pars %>% 
-        #---join aunit_id---
-        .[data.table(field_sf)[,.(cell_id, aunit_id)], on = "cell_id"] %>% 
-        #---aggregate ---
-        .[, .(EONR = mean(EONR)), by = .(sim, aunit_id)]
-    
-    #* add EONR data to est_result_ls
-    est_result_ls[[sc_i]] <- 
-        est_result_ls[[sc_i]] %>% 
-        mutate(
-            data = list(
-                left_join(data, EONR_df, by = c("sim", "aunit_id"))
-            )
-        ) %>% 
-        mutate(
-            perform = list(
[…]

### 2022-02-19 Codes/3_make_figures_tables.R

@@ -159,44 +159,42 @@
 #******************************************************************************
 
 # /*===========================================================
+#' # Single simulation illustration (aunit-level data)
+# /*===========================================================
+sim_example = 58
+gdata <- illus_data[sim==sim_example, ]
+mean_dt <- gdata %>% 
+    .[, .(
+        rmse_yield = mean((yield - yield_hat)^2, na.rm = TRUE) %>% sqrt() %>% round(1),
+        rmse_EONR = mean((EONR - opt_N_hat)^2) %>% sqrt() %>% round(1),
+        x_yield = quantile(yield, 0.05),
+        y_yield = quantile(yield_hat, 0.99),
+        x_EONR = quantile(EONR, 0.05),
+        y_EONR = quantile(opt_N_hat, 0.99) + 15
+    ),
+    by = .(model)] %>% 
+    print()
+
+#* predicted vs true yield
+single_simu_yield <- 
+    source(here("GitControlled", "Codes", "Modules", "figure_single_simu_yield.R"))$value
+#* predicted vs true EONR
+single_simu_EONR <- 
+    source(here("GitControlled", "Codes", "Modules", "figure_single_simu_EONR.R"))$value
+
+
+
+# /*===========================================================
 #' # Boxplot of yield RMSE
 # /*===========================================================
 # fig.id = "rmse-yield-boxplot",
 # fig.cap = "The yield prediction performances of different models"
 
-#------ range of values ------#
-value_ls <- seq(gdata[, min(rmse_cv) / 200] %>% floor() * 200,
-  gdata[, max(rmse_cv) / 200] %>% ceiling() * 200,
-  by = 200
-)
-yaxis_min <- gdata$rmse_cv %>% min()
-yaxis_max <- gdata$rmse_cv %>% max()
-podg <- position_dodge(0.6)
-
+gdata <- est_data
 #------ boxplot ------#
-rmse_yield_boxplot <- 
-    gdata %>% 
-    ggplot(data = ., 
-       aes(x = field_size, y = rmse_cv, fill = model)) +
-    stat_boxplot(geom = "errorbar", width = 0.3, position = podg) +
-    geom_boxplot(position = podg, width = 0.5, outlier.shape = NA) +
-    ylab('Out-of-Sample Yield Prediction RMSE (kg/ha)') +
-    xlab('') +
-    scale_y_continuous(breaks = value_ls, label = value_ls) +
[…]

### 2022-02-19 Codes/Modules/figure_boxplot_profit.R

@@ -2,23 +2,24 @@
 
 
 #------ range of profit values ------#
-value_ls <- -seq(0, -gdata[,min(profit)/5] %>% ceiling()*5, by = 10)
-yaxis_min <- gdata$profit %>% min()
+value_ls <- -seq(0, -gdata[, min(profit) / 5] %>% ceiling() * 5, by = 10)
 yaxis_max <- gdata$profit %>% max()
+yaxis_min <- gdata$profit %>% min()
+podg <- position_dodge(0.6)
 
 #------ boxplot ------#
 library(tidytext)
-podg <- position_dodge(0.4)
-ggplot(data = gdata, 
-       aes(x = field_size, y = profit, fill = model)) +
-    stat_boxplot(geom = "errorbar", width = 0.25, position = podg) +
-    geom_boxplot(position = podg, width = 0.25, outlier.shape = NA) +
+g_plot <- 
+    ggplot(data = gdata, 
+           aes(x = field_size, y = profit, fill = model)) +
+    stat_boxplot(geom = "errorbar", width = 0.3, position = podg) +
+    geom_boxplot(position = podg, width = 0.5, outlier.shape = NA) +
     # geom_text(data = mean_data, 
     #           aes(x = field_size, y = profit_high,
     #               label = paste0(round(profit, 2), " (", round(profit_sd, 2),")")),
     #           position = podg, angle = 90, 
     #           hjust = 0, size = 3 ) +
-    ylab('Average Profit Relative to True Optimal ($/ha)') +
+    ylab('Profit Relative to True Optimal ($/ha)') +
     xlab('') +
     scale_y_continuous(expand = c(0, 0), breaks = value_ls, label = value_ls,
                        limits = c(yaxis_min - 10, 0)) +
@@ -30,9 +31,10 @@ ggplot(data = gdata,
         legend.position='bottom',
         legend.title = element_blank(),
         legend.key.size = unit(0.4, 'cm'),
-        legend.text = element_text(margin = margin(r = 1, unit = "cm")),
-        legend.margin=margin(t = -0.5, unit='cm'),
+        # legend.text = element_text(margin = margin(r = 1, unit = "cm")),
+        # legend.margin=margin(t = -0.5, unit='cm'),
         axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0.5),
         axis.text=element_text(color='black')
     )
+
 

### 2022-02-20 Writing/manuscript.rmd
result 1st draft

--- 2022-02-19 Writing/manuscript.rmd
@@
 The performances of machine learning and traditional regression models from 1,000 simulations were compared in Figure \@ref(fig:comb-boxplot-all).
-Three performance measurements: (1) out-of-sample yield prediction, (2) out-of-sample EONR prediction, and (3) profit resultant from the predicted EONR.
+Three performance measurements were presented: (1) out-of-sample yield prediction, (2) out-of-sample EONR prediction, and (3) profit resultant from the predicted EONR.
 
-Table of winner counts.
+First look at the large field (37.3 ha) scenario as shown in panel (A) of Figure \@ref(fig:comb-boxplot-all).
 
-Look at the large field (37.3 ha) scenario in panel (A) of Figure \@ref(fig:comb-boxplot-all).
-
-- Indeed, the simulation results showed that machine learning models have better yield predictions than traditional regression models.
+- Indeed, machine learning models showed better yield prediction performances than traditional regression models.
 On average, the out-of-sample predicted yields' RMSE of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$) and BRF (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$) models were significantly smaller than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_yield] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) model.
 Those results are consistent with existing literature (**citations**).
-- However, the better yield prediction of machine learning models does not translate into better EONR prediction.
-The average RMSE of out-of-sample predicted EONR of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was much larger than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_eonr] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$) model.
-BRF model's EONR prediction (RMSE `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was better than RF model, which was similar to OLS model, but was still significantly worse than SER model.
-Those results showed that, despite machine learning models have better yield prediction, their EONR prediction is worse than traditional regression models.
+- However, the better yield predictions of machine learning models did not translate into better EONR predictions.
+The average RMSE of out-of-sample predicted EONR of RF model (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was much larger than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_eonr] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$) model.
+BRF model's EONR prediction (RMSE `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was better than RF model, and was similar to OLS model, but still significantly worse than SER model.
+Those simulation results demonstrate that despite machine learning models have better yield predictions, their EONR predictions are worse than traditional regression models.
 - Ultimately, the worse EONR prediction of machine learning models resulted in lower production profit compared to the traditional regression models.
-The 1,000-simulation average profit of RF ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) or BRF ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) model is significantly lower than that of OLS ($\$$`r mean_data[field_size=="37.3 ha"&model=="OLS", profit] %>% round(2)` ha$^{-1}$) or SER ($\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$) model.
+The 1,000-simulation average profit of RF ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) or BRF ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) model was significantly lower than that of OLS ($\$$`r mean_data[field_size=="37.3 ha"&model=="OLS", profit] %>% round(2)` ha$^{-1}$) or SER ($\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$) model.
 
@@
 
-- Within the machine learning models, the RF model performs especially poor in EONR prediction. Its EONR prediction RMSE was much larger than BRF model, and its associated profit was extremely low. 
-- Even if we "cheat" and feed RF model with the best possible data (the true yield response parameters), its EONR prediction (RMSE `r mean_data[field_size=="37.3 ha"&model=="RF_b", rmse_eonr] %>% round(2)` kg ha$^{-1}$) and profit performance ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF_b", profit] %>% round(2)` ha$^{-1}$) were still slightly worse than BRF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) with observed data.
-- Note that RF is currently a very popular machine learning method used by many agricultural studies.
-Our simulation results showed that although RF may be OK for yield prediction, it is terrible in EONR prediction, and will cause big economic loss if using it in decision making.
-Even after spending great efforts (and costs) to obtain the perfect information, using RF model still won't achieve good economic performance.
+- Within the machine learning models, the RF model performed especially poorly in EONR prediction.
+Its EONR prediction RMSE was much larger than BRF model, and its associated profit was extremely low (as shown in Figure \@ref(fig:comb-boxplot-all) panel (A)).
+- Even if we "cheat" and feed RF model with the best possible data (i.e., the true yield response parameters), its EONR profit ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF_b", profit] %>% round(2)` ha$^{-1}$) was still slightly lower than BRF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) that was estimated using observed messy data.
+- It is noteworthy to mention that RF model is currently a very popular machine learning method used in many agricultural studies.
+Our simulation results showed that although RF may be OK for yield prediction, it is terrible in EONR prediction, and will cause big economic loss if using it in farming recommendation development.
+Even after spending great efforts (and financial costs) to obtain the perfect information, using RF model still won't achieve good economic performance.
 
@@
 
-Figure \@ref(fig:comb-boxplot-all) panels (B) and (C) showed the simulation results for medium (18.7 ha) and small (9.3 ha) fields.
+How robust are the results to different field sizes? Figure \@ref(fig:comb-boxplot-all) panels (B) and (C) showed the simulation results for medium (18.7 ha) and small (9.3 ha) sized fields.
 
-- The result pattern of model performances was generally robust to field sizes.
-For any sized field, the machine learning models still have better yield predictions while worse economic performances than traditional regression models.
-- But we do notice that machine learning models' economic performances catch up when field size decreases.
+- The result pattern that machine learning models have better yield predictions but worse economic performances compared to traditional regression models was generally robust to field sizes. 
+- But machine learning models' economic performances catch up when field size decreases.
 Especially, BRF model outperformed OLS model in EONR prediction and profit performance in small and medium fields.
-Although BRF model still cannot win SER in profit performance, its profit gap between SER reduced from $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in large field to $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in medium field and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in small field.
-- The results may suggest machine learning models (especially BRF) are more desirable in small fields' EONR predictions.
-But under the context of current farming practice, most production fields are larger than the smallest field (9.3 ha) scenario of our simulation, SER model is economically best option.
+Though BRF model's profit was still lower than SER, the profit gap between BRF and SER reduced from $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in large field to $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in medium field and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="BRF", profit]) %>% round(2)` ha$^{-1}$ in small field.
+- The results may suggest machine learning models (especially BRF) apply better in small fields' data analysis.
+But since under the context of current farming practice most production fields are larger than the smallest field (9.3 ha) scenario in our simulation, SER model appears to be the economically best option.
 
@@
 
-- One simulation example (cherry picking, similar to the mean pattern)
+Why good yield prediction does not necessarily end up with good economic performance?
+That sound counterintuitive.
+We attempt to provide some explanations.
+Note this is not a statistical paper and providing the rigorous statistical proof is beyond the scope of this paper.
+We just try providing some illustrative explanations.
 
-- One location's yield response curves
+- Figure \@ref(fig:single-simu-illustrate) showed the predicted versus true yield (panel A) and EONR (panel B) of the 1,440 locations ($aunit$) from one example simulation's results (large field).
+The RMSE measurements associated with each model's results for this specific simulation were displayed in the figure as well.
+Though the machine learning models (RF, RF_b, and BRF) generated well-predicted yields such that the plotted points were well distributed along the 45 degree line, their predicted EONR were not continuous but fell into several discrete values.
+That results were to a large extent caused by the discrete data of five nitrogen trial rates.
+But that is how the on-farm experimental data generally look like in practice.
+On the other hand, the SER model's predicted EONR were much better aligned the 45 degree line, despite its predicted yields were not as good as the machine learning models.
+The OLS model's EONR predictions are also continuous, but with too big dispersion.
+- We further look into the yield response curve estimation at individual locations.
+Figure \@ref(fig:yield-curves) illustrated the estimated yield response curves by different models at a specific location ($aunit$).
+The circle point denoted the trial N rate and true (deterministic part of) yield.
+This figure showed that the machine learning models' predicted yields were closer to the true yield.
+However, the shapes of yield response curves predicted by machine learning models were much less accurate.
+On the other hand, SER model's predicted yield levels were heavily biased, but its predicted yield response curve had the shape much more resembling the true response curve.
+The EONR is determined by the yield response (mathematically, the slope of the curve), rather than the yield level.
+- Mathematically the slope of the curve: economics term, marginal effect, but the derivative measure is not commonly used in agronomy studies; Agronomy term, treatment effect, which is not the continuous derivative measure, but regarding the different N levels as discrete values.
+A treatment effect is defined as the change in yield from one N rate to the next level N rate.
+Here we have five N treatment rates, and therefore define four treatment effects.
+The estimated versus true treatment effects of N rates for the same simulation round's 1,440 locations were shown in Figure \@ref(fig:treatment-effect) for different models.
+Notice that we used the quadratic-plateau function as the true yield response in the simulation, and therefore at higher N levels the yields are more likely to approach or pass the plateau and the true treatment effect is quite small or even zero.
+As can be seen, the machine learning models mostly underestimated the treatment effects at all N levels.
+That is the major reason why machine learning models failed to predict accurate EONR.
+In contrast, SER model did a much better job in treatment effect predictions, particularly at the low N levels.
+OLS model's estimated treatment effects were actually less biased compared to machine learning models, but the variations were just very large.
+- (Maybe we don't need to say this, as this is so obvious.) Caveat: The single simulation round we choose was a little cherry-picking.
+We chose that the round where the five models' profit results were roughly corresponding to the means as shown in Figure \@ref(fig:comb-boxplot-all).
+Indeed, there are lots of variations across simulation rounds, such that in come simulations machine learning models outperformed SER model.
+We believe the one example simulation we showed here is representative, and can make a good illustration of the yield versus EONR prediction performances.
 
-- Treatment effects
+## OLS vs. SER: Statistical efficiency is money
 
-short summary:
+(I feel this part is only a minor point in this study. Perhaps it's not important enough to be put in the title.)
+
+- It is also interesting to compare the OLS and SER results. The good performance of SER may imply some good suggestion to production.
+- It has been well known in the econometric literature that SER model can improve the estimation efficiency compared to OLS at the presence of unknown spatial data autocorrrelation, which is a very common in crop field characteristics data.
+- However, since it is only an efficiency issue, and SER does not correct for bias, this advantage of SER model has not received enough attention.
+The efficiency improvement is only regarded as a statistical property, while its economic benefit is not well recognized.
+- Our simulation evidence showed that the statistical efficiency of SER model can actually translate into considerable more profitable EONR recommendations.
+The profit of SER model is higher than OLS model by $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$ for large, medium, and small fields, respectively.
+- So, using SER model to update the OLS model is likely to be economically beneficial in on-farm experimental data analysis, and should be encouraged.
+
+## Robustness to yield generating process
+
+- The true yield generating process used in our simulation, quadratic-plateau function, is the most established corn yield response pattern demonstrated in the agronomy literature.
+But there are also some other corn response functional forms found in existing studies.
+In case somebody criticize us on this point, we also tried several other corn yield response functions: Mitscherlich‐Baul, quadratic, ...
+
+`r run_pagebreak()`
+
+# Conclusions
 
@@
 This can be very misleading and cost producers a lot when it is used in developing input management recommendations, since models with good yield prediction can have bad profit at the same time.
-
-## OLS vs. SER: Statistical efficiency is money.
-
-We should be more actively use SER model in yield response estimation.
-
-## EONR prediction and profit is not perfectly one-to-one corresponding. (perhaps too much; remove this point)
-
-Lots of agronomy studies use predicted EONR vs "true" EONR as the criteria to evaluate input recommendation algorithms. ("true" EONR is from yield responses estimated from trial data)
-
-illustrative figure:
-
-`r run_pagebreak()`
-
-# Conclusions
 
@@
 ```{r comb-boxplot-all, fig.cap="The estimation performances of machine learning models (RF, RF_b, BRF) and traditional regression models (OLS, SER) over 1,000 simulations for: (A) large field (37.3 ha), (B) medium field (18.7 ha), and (C) small field (9.3 ha).
-The performance measurements include: (1) out-of-sample yield prediction RMSE, (2) out-of-sample EONR prediction RMSE, and (3) profit resultant from the predicted EONR.", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
+The performance measurements include: (1) out-of-sample yield prediction RMSE, (2) out-of-sample EONR prediction RMSE, and (3) profit resultant from the predicted EONR.", fig.height=8.5, fig.width=7, echo=FALSE, cache=FALSE}
 (comb_boxplot_large + ggtitle("(A) large field")) / (comb_boxplot_medium + ggtitle("(B) medium field")) / (comb_boxplot_small + ggtitle("(C) small field"))
@@
 
-```{r single-simu-yield, fig.cap="Example simulation, yield.", fig.width=6, fig.height=7.5, echo=FALSE, cache=FALSE}
-single_simu_yield
+```{r single-simu-illustrate, fig.cap="The estimation performances of one example simulation, large field (37.3 ha).
+Each dot represents a location of the field.", fig.height=8.5, fig.width=7, echo=FALSE, cache=FALSE}
+(single_simu_yield + ggtitle("(A)")) / (single_simu_EONR + ggtitle("(B)"))
 ```
 
-```{r single-simu-EONR, fig.cap="Example simulation, EONR", fig.width=6, fig.height=7.5, echo=FALSE, cache=FALSE}
-single_simu_EONR
+```{r yield-curves, fig.cap="Estimated yield response curves at a specific location", fig.height=8.5, fig.width=7, echo=FALSE, cache=FALSE}
+include_graphics(here("GitControlled", "Graphs", "802_yield.png"))
+```
+
+```{r treatment-effect, fig.cap="", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
+include_graphics(here("GitControlled", "Graphs", "treatment_sim_58.png"))
 ```

### 2022-02-20 Writing/presentation.rmd
result 1st draft missing 2888 commits

---
title: "Pitfall of Prediction-orienterd Machine Learning Models and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo = F, cache = F, include = F}
library(knitr)
library(here)

here::i_am("GitControlled/Writing/manuscript.rmd")

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = T,
  echo = F,
  fig.cap = TRUE
)
```

```{r cache = F, include = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(officedown)
library(officer)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(gridExtra)
```

```{r figure_setup, cache = F}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

```{r include = FALSE}
# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================
#* source all the functions in the Functions folder
# fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
#   lapply(., function(x) source(x))

# /*----------------------------------*/
#' ##  data preparation
# /*----------------------------------*/
#' load results data
est_data <-
  readRDS(here("Shared", "Results", "est_result_ls.rds")) %>%
  rbindlist() %>%
  dplyr::select(model, perform, field_col) %>%
  unnest(perform) %>%
  data.table()
#' rename columns
est_data <- est_data %>%
  .[, .(field_col, model, sim, profit, rmse_train, rmse_cv, rmse_eonr)] %>%
  #---field size---
  .[, field_size := paste0(round(field_col * 72 * 6^2 / 10000, 1), " ha")] %>%
  .[, field_size := factor(field_size, levels = c("9.3 ha", "18.7 ha", "37.3 ha"))] %>%
  #---model name---
  .[model == "brf", model := "BRF"] %>%
  .[model == "rf", model := "RF"] %>%
  .[model == "rf_perfect", model := "RF best"] %>%
  .[model == "lm", model := "LM"] %>%
  .[model == "ser_50", model := "SER"] %>%
  .[, model := factor(model, levels = c("RF", "RF best", "BRF", "LM", "SER"))]
#' mean and sd
mean_data <- est_data %>%
  .[, .(
    profit = mean(profit) %>% round(2),
    profit_sd = sd(profit) %>% round(2),
    rmse_yield = mean(rmse_cv) %>% round(2),
    rmse_yield_sd = sd(rmse_cv) %>% round(2),
    rmse_eonr = mean(rmse_eonr) %>% round(2),
    rmse_eonr_sd = sd(rmse_eonr) %>% round(2)
  ),
  by = c("field_size", "model")
  ] %>%
  .[order(field_size, model), ]
#' load illustration data (single simulation)
illus_data <-
  readRDS(here("Shared", "Results", "illus_data.rds"))

# /*----------------------------------*/
#' ##  create figures and tables
# /*----------------------------------*/
source(here("GitControlled", "Codes", "3_make_figures_tables.R"))
```

## Introduction

- Prediction-oriented Machine Learning (ML) methods swept the field of optimal input management in precision agriculture.
- Yield prediction is the ultimate goal.
- Big success.
- But unclear whether good yield prediction translates into farming profitability.

## Objective of This Study

- Compare the performance of prediction-oriented ML methods and traditional linear regression approaches in terms of the profitability of estimated site-specific nitrogen recommendation.
- Monte Carlo simulations
- On-farm precision experimental data

## Simulation Setting

```{r true-pars-b2, fig.cap="Simulated field", out.width="20%", out.height="20%", echo=FALSE, cache=FALSE}
include_graphics(here("GitControlled", "Graphs", "true_pars_b2.png"))
```

## True Yield Generation

Corn yield response to nitrogen (N) fertilizer at each location $i$
- Quadratic-plateau function:

$$
\begin{aligned}
y_{i} = 
  \begin{cases}
  \alpha_{i} + \beta_{i} N + \gamma_{i} N^2 + \varepsilon_{i}, & N < \tau_{i} \\
  \eta_{i}, & N \geq \tau_{i}
  \end{cases}
\end{aligned}
$$
- $\eta_i$: yield plateau
- $\tau_i$: the N rate where yield reaches plateau

## Field Characteristics Data

- Spatial variability of true parameters ($\alpha, \tau, \eta$) are generated by Gaussian process
- But producers do not observe them.
- Only observe the decomposition of the true parameters ($X_1$):

$$
\begin{aligned}
\alpha & = \alpha^1 + \alpha^2 \\
\tau & = min\big(min(\tau^{1,1}, \tau^{1,2}), min(\tau^{2,1}, \tau^{2,2})\big) \\
\eta & = min\big(min(\eta^{1,1}, \eta^{1,2}), min(\eta^{2,1}, \eta^{2,2})\big) 
\end{aligned}
$$
- and two nuisance covariates ($X_2$) that are correlated with $\alpha$, $\tau$, and $\eta$:

$$
\phi^{\alpha, 1}, \phi^{\alpha, 2}, \phi^{\tau, 1}, \phi^{\tau, 2}, \phi^{\eta, 1}, \phi^{\eta, 2}
$$

## On-Farm Nitrogen Experiment

- Five (5) nitrogen trial rates
- Latin Square experimental design

```{r N-trial-design, fig.cap="Simulated field", out.width="20%", out.height="20%", echo=FALSE, cache=FALSE}
include_graphics(here("GitControlled", "Graphs", "Nrate_Latin Square Fixed_blocked.png"))
```

## Estimation Models

Estimation of yield response functions and site-specific optimal nitrogen rates

- Machine Learning:
- Random Forest (RF)
- Random Forest with best possible data (true $\alpha$, $\tau$, and $\eta$)(RF$_{b}$)
- Boosted Regression Forest (BRF)

- Traditional Regression:
Linear Model OLS (LM)
Spatial Error Model (SER)

## Performance Measurements (1)

- Yield prediction
Root-mean-square error (RMSE) of out-of-sample predicted yield ($\hat{y}$):
$$
\begin{aligned}
RMSE_y = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{y}_i - y_i)^2}
\end{aligned}
$$
- Train data: One simulation round
- Test data: Another simulation round

## Performance Measurements (2)

- Economically optimal nitrogen rate (EONR) prediction:
Root-mean-square error (RMSE) of out-of-sample predicted EONR:

$$
\begin{aligned}
RMSE_{N} = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (\hat{EONR}_i - EONR_i)^2}
\end{aligned}
$$

## Performance Measurements (3)

- Production profit: 
Generated by applying the estimated EONR:

$$
\begin{aligned}
\pi_i = p_{corn} f_i(\hat{EONR}_i) - p_N N_i - C
\end{aligned}
$$
- $f_i()$: true yield response function

## Results

- Machine learning models perform well in yield prediction,

- but poor in EONR prediction

- Traditional SER model generates the highest profit

## An Example Simulation

```{r single-simu-yield, fig.cap="Example simulation, yield.", fig.width=6, fig.height=7.5, echo=FALSE, cache=FALSE}
single_simu_yield
```

```{r single-simu-EONR, fig.cap="Example simulation, EONR", fig.width=6, fig.height=7.5, echo=FALSE, cache=FALSE}
single_simu_EONR
```

## 1,000 Simulations
```{r comb-boxplot-large, fig.cap="The performances of different models", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
comb_boxplot_large
```

## Illustrative Explanation

Why good yield prediction does not necessarily mean good EONR prediction?

```{r illustrate-explain, fig.cap="Estimated yield response curves at a specific location", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
include_graphics(here("GitControlled", "Graphs", "802_yield.png"))
```

- Yield level prediction
- Yield response (marginal effect, treatment effect) prediction $\Rightarrow$ More important

## Illustrative Explanation (cont'd)

Estimated vs. True treatment effect

```{r illustrate-treatment-effect, fig.cap="", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
include_graphics(here("GitControlled", "Graphs", "treatment_sim_58.png"))
```

## Field Sizes

```{r comb-boxplot-all, fig.cap="The performances of different models, large field.", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
(comb_boxplot_large + ggtitle("(A) large field")) / (comb_boxplot_medium + ggtitle("(B) medium field")) / (comb_boxplot_small + ggtitle("(C) small field"))
```

- Machine learning models' performances catch up when field sizes decrease
- BRF beats LM, and shrinks gaps to SER, for smaller fields
- Performances of Traditional regression models are more sensitive to field sizes
- Machine learning models are more suitable for small fields

## Efficiency is Money

- At the presence of unknown spatial heterogeneity,
- SER model improve efficiency of LM estimates,
- But it is only treated as a statistical property
- Our simulation evidence: Statistical efficiency means more profitable EONR recommendations

```{r, fig.cap="The performances of different models, large field.", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
(comb_boxplot_large + ggtitle("(A) large field")) / (comb_boxplot_medium + ggtitle("(B) medium field")) / (comb_boxplot_small + ggtitle("(C) small field"))
```

## Conclusions

- Machine learning models perform poor in EONR prediction compared to traditional regression models, despite their better yield prediction.

- What matters more is estimating yield responses, not yield levels.

- SER model can generate the most profitable EONR recommendations for normal-sized fields

- Machine learning models are more useful for small fields.

- More actively use SER model in contrast to LM in yield response estimation.

### 2022-02-20 Codes/Modules/figure_single_simu_EONR.R

@@ -1,0 +1,21 @@
+
+#* predicted vs true EONR
+
+ggplot(data = gdata) +
+    geom_point(aes(x = EONR, y = opt_N_hat, color = model), size = 0.5) +
+    geom_text(
+        data = mean_dt, hjust = 0, size = 2.5,
+        aes(x = x_EONR, y = y_EONR, label = paste0("RMSE=", rmse_EONR))) +
+    geom_abline(intercept = 0, slope = 1, color = "black", size = 1) +
+    facet_wrap(~ model, ncol = 3) +
+    ylab("Out-of-Sample Predicted EONR (kg/ha)") +
+    xlab("True EONR (kg/ha)") +
+    theme_bw() +
+    theme(
+        panel.grid = element_blank(),
+        legend.position='none',
+        legend.title = element_blank(),
+        axis.text=element_text(color='black')
+    )
+
+

### 2022-02-21 Writing/manuscript.rmd
modified results

@@
 
-- Indeed, machine learning models showed better yield prediction performances than traditional regression models.
+Machine learning models showed better yield prediction performances than traditional regression models.
 On average, the out-of-sample predicted yields' RMSE of RF (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_yield] %>% round(2)` kg ha$^{-1}$) and BRF (`r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_yield] %>% round(2)` kg ha$^{-1}$) models were significantly smaller than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_yield] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_yield] %>% round(2)` kg ha$^{-1}$) model.
 Those results are consistent with existing literature (**citations**).
-- However, the better yield predictions of machine learning models did not translate into better EONR predictions.
+However, the better yield predictions from the machine learning models did not translate into better EONR predictions for them.
 The average RMSE of out-of-sample predicted EONR of RF model (`r mean_data[field_size=="37.3 ha"&model=="RF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was much larger than that of OLS (`r mean_data[field_size=="37.3 ha"&model=="OLS", rmse_eonr] %>% round(2)` kg ha$^{-1}$) or SER (`r mean_data[field_size=="37.3 ha"&model=="SER", rmse_eonr] %>% round(2)` kg ha$^{-1}$) model.
 BRF model's EONR prediction (RMSE `r mean_data[field_size=="37.3 ha"&model=="BRF", rmse_eonr] %>% round(2)` kg ha$^{-1}$) was better than RF model, and was similar to OLS model, but still significantly worse than SER model.
-Those simulation results demonstrate that despite machine learning models have better yield predictions, their EONR predictions are worse than traditional regression models.
-- Ultimately, the worse EONR prediction of machine learning models resulted in lower production profit compared to the traditional regression models.
-The 1,000-simulation average profit of RF ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) or BRF ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) model was significantly lower than that of OLS ($\$$`r mean_data[field_size=="37.3 ha"&model=="OLS", profit] %>% round(2)` ha$^{-1}$) or SER ($\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$) model.
+As expected, a similar pattern of relative performance of the models are observed in terms of the profitability of site-specific EONR recomendations.
+The average profit of RF ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF", profit] %>% round(2)` ha$^{-1}$) or BRF ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) model was significantly lower than that of OLS ($\$$`r mean_data[field_size=="37.3 ha"&model=="OLS", profit] %>% round(2)` ha$^{-1}$) or SER ($\$$`r mean_data[field_size=="37.3 ha"&model=="SER", profit] %>% round(2)` ha$^{-1}$) model.
+These results clearly demonstrate that better yield prediction does not necessarily lead to better site-specific EONR prediction and thus more profitable site-specific input recommendations.
+This results is a cautionary for us to not select models and methods based on their yield prediction capabilities.
 
-## RF model is bad
+It is noteworthy that RF model performed especially poor in EONR prediction because RF is currently a very popular machine learning method in yield response function estimation.
+Its EONR prediction RMSE was much larger than BRF model, and its associated profit was extremely low (as shown in Figure \@ref(fig:comb-boxplot-all) panel (A)).
+Even when the RF model is fed with the true yield response parameters ($\alpha$, $\tau$, $\eta$) directly, its EONR profit ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF_b", profit] %>% round(2)` ha$^{-1}$) was still slightly lower than BRF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) that was estimated using all the observed variables.
+Our simulation results showed that BRF is simply a superior model than RF both in terms yield prediction and EONR predictions.
+Given BRF is just as easy to implement in popular statistical software like R and python, it seems hard to justify the use of RF any longer at least in the context of site-speific yield response function estimation.
 
-- Within the machine learning models, the RF model performed especially poorly in EONR prediction.
-Its EONR prediction RMSE was much larger than BRF model, and its associated profit was extremely low (as shown in Figure \@ref(fig:comb-boxplot-all) panel (A)).
-- Even if we "cheat" and feed RF model with the best possible data (i.e., the true yield response parameters), its EONR profit ($\$$`r mean_data[field_size=="37.3 ha"&model=="RF_b", profit] %>% round(2)` ha$^{-1}$) was still slightly lower than BRF model ($\$$`r mean_data[field_size=="37.3 ha"&model=="BRF", profit] %>% round(2)` ha$^{-1}$) that was estimated using observed messy data.
-- It is noteworthy to mention that RF model is currently a very popular machine learning method used in many agricultural studies.
-Our simulation results showed that although RF may be OK for yield prediction, it is terrible in EONR prediction, and will cause big economic loss if using it in farming recommendation development.
-Even after spending great efforts (and financial costs) to obtain the perfect information, using RF model still won't achieve good economic performance.
+Finally, while the ML methods perform worse than LM and SER on average, it does not mean they perform worse in terms of profitability in every single simualtion round.
+Figure \@ref() shows the percentage each model performed the best in yield prediciton (panel a), EONR prediciton (panel b), and profitability (panel c).
+
+## Insights into the divergence in yield and EONR prediction
+
+It may sound counterintuitive that better yield prediction does not necessarily lead to better EONR prediction and economic performance.
+Here, we present an illustrative example to provide some explanations for this divergence between yield and EONR predictions.
+
+Figure \@ref(fig:single-simu-illustrate) shows the predicted versus true yield (panel A) and EONR (panel B) of the 1,440 locations ($aunit$) from a single simulation round for the large field case.
+The RMSE measurements associated with each model's results for this specific simulation were displayed in the figure as well.
+Though the machine learning models (RF, RF_b, and BRF) generated well-predicted yields such that the plotted points were well distributed along the 45 degree line, their predicted EONR were not continuous but fell into several discrete values.
+That results were to a large extent caused by the discrete data of five nitrogen trial rates.
+But that is how the on-farm experimental data generally look like in practice.
+On the other hand, the SER model's predicted EONR were much better aligned the 45 degree line, despite its predicted yields were not as good as the machine learning models.
+The OLS model's EONR predictions are also continuous, but with too big dispersion.
+
+Figure \@ref(fig:yield-curves) illustrates the estimated yield response curves by different models at a specific location ($aunit$).
+The circle point denoted the trial N rate and true (deterministic part of) yield.
+It shows that the machine learning models' predicted yields were closer to the true yield.
+However, the shape of yield response curves predicted by machine learning models were much less accurate compared to that of SER.
+On the other hand, SER model's predicted yield "level" were heavily biased unlike the ML methods, but its predicted yield response curve resembles the true response curve much more.
+It is well understood and established in the agronomic community that it is not yield "level", but the slope of the yield response curve that determins EONR.
+Therefore, it is not surprising that the failure by the ML methods to estimate site-specific yield response curve for this location accurately resulted in poor-performing input recommendation for this location.
+
+Severe underestimation of the impact of nitrogen on yield is not just for the single location.
+Figure \@ref(fig:treatment-effect) plots true and estiamted treatment effects of four treatments (<span style = "color: blue;"> Xiaofei, list cases here</span>) by model for all the locations (1440) within a single field for a single simulation round.
+It shows that the machine learning models severely underestimated the treatment effects at all N levels, resulting in severe underestimation of site-specific EONR.
+This pattern is also observed in another simulation study by \@ref(@kakimoto2022) and also an empirical study by \@ref(Alfonso).
+In contrast, SER model did a much better job in treatment effect prediction, particularly at the low N levels.
+OLS model's estimated treatment effects were less biased compared to machine learning models, but it is much less accurate compared to SER.
+Due to the flexibility of the ML methods, it is easy for them to come up with wrong explanations to yield variations.
+As we saw earlier, the ML models explaind yield variations better (lower RMSE of yield) even though they fail to recognize the impact of nitrogen on yield.
+The ML models found it more beneficial to let the other variables explain the variations in yield than nitrogen.\footnote{Note that as the nitrogen level increases, the impact of nitrogen on yield declines and it is almost zero at the higher experimental nitrogen levels.} This illustrating example above is not just a outlier that we cherry-picked.
+Figure \@ref() shows the the density plot of the average ratio of estimated EONR to the true EONR by model for all the simulation rounds.
+As you can see, the ML methods tend to severely underestiamte EONR on average.
+
+## OLS vs. SER: Statistical efficiency is money
+
+It is also interesting to compare the OLS and SER results.
+It is well-established that SER is more statistically efficient than simple OLS in the presence of unknown spatial data autocorrrelation, which is a very common in OFPE data.
+This advantage of SER does not seem to have received much attention as it is just a statistical property, economist have a tendency to focus on unbiasedness and consistency issues more than efficiency.
+However, in the context of site-specific EONR estiamtion, statistical efficiency means money.
+The more accurately estimated coefficients are, the more accurately site-specific EONRs are estimated, leading to a higher profit.
+
+- However, since it is only an efficiency issue, and SER does not correct for bias, this advantage of SER model has not received enough attention.
+The efficiency improvement is only regarded as a statistical property, while its economic benefit is not well recognized.
+- Our simulation evidence showed that the statistical efficiency of SER model can actually translate into considerable more profitable EONR recommendations.
+The profit of SER model is higher than OLS model by $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$ for large, medium, and small fields, respectively.
+- So, using SER model to update the OLS model is likely to be economically beneficial in on-farm experimental data analysis, and should be encouraged.
 
@@
 But since under the context of current farming practice most production fields are larger than the smallest field (9.3 ha) scenario in our simulation, SER model appears to be the economically best option.
-
-## Illustrative explanation
-
-Why good yield prediction does not necessarily end up with good economic performance?
-That sound counterintuitive.
-We attempt to provide some explanations.
-Note this is not a statistical paper and providing the rigorous statistical proof is beyond the scope of this paper.
-We just try providing some illustrative explanations.
-
-- Figure \@ref(fig:single-simu-illustrate) showed the predicted versus true yield (panel A) and EONR (panel B) of the 1,440 locations ($aunit$) from one example simulation's results (large field).
-The RMSE measurements associated with each model's results for this specific simulation were displayed in the figure as well.
-Though the machine learning models (RF, RF_b, and BRF) generated well-predicted yields such that the plotted points were well distributed along the 45 degree line, their predicted EONR were not continuous but fell into several discrete values.
-That results were to a large extent caused by the discrete data of five nitrogen trial rates.
-But that is how the on-farm experimental data generally look like in practice.
-On the other hand, the SER model's predicted EONR were much better aligned the 45 degree line, despite its predicted yields were not as good as the machine learning models.
-The OLS model's EONR predictions are also continuous, but with too big dispersion.
-- We further look into the yield response curve estimation at individual locations.
-Figure \@ref(fig:yield-curves) illustrated the estimated yield response curves by different models at a specific location ($aunit$).
-The circle point denoted the trial N rate and true (deterministic part of) yield.
-This figure showed that the machine learning models' predicted yields were closer to the true yield.
-However, the shapes of yield response curves predicted by machine learning models were much less accurate.
-On the other hand, SER model's predicted yield levels were heavily biased, but its predicted yield response curve had the shape much more resembling the true response curve.
-The EONR is determined by the yield response (mathematically, the slope of the curve), rather than the yield level.
-- Mathematically the slope of the curve: economics term, marginal effect, but the derivative measure is not commonly used in agronomy studies; Agronomy term, treatment effect, which is not the continuous derivative measure, but regarding the different N levels as discrete values.
-A treatment effect is defined as the change in yield from one N rate to the next level N rate.
-Here we have five N treatment rates, and therefore define four treatment effects.
-The estimated versus true treatment effects of N rates for the same simulation round's 1,440 locations were shown in Figure \@ref(fig:treatment-effect) for different models.
-Notice that we used the quadratic-plateau function as the true yield response in the simulation, and therefore at higher N levels the yields are more likely to approach or pass the plateau and the true treatment effect is quite small or even zero.
-As can be seen, the machine learning models mostly underestimated the treatment effects at all N levels.
-That is the major reason why machine learning models failed to predict accurate EONR.
-In contrast, SER model did a much better job in treatment effect predictions, particularly at the low N levels.
-OLS model's estimated treatment effects were actually less biased compared to machine learning models, but the variations were just very large.
-- (Maybe we don't need to say this, as this is so obvious.) Caveat: The single simulation round we choose was a little cherry-picking.
-We chose that the round where the five models' profit results were roughly corresponding to the means as shown in Figure \@ref(fig:comb-boxplot-all).
-Indeed, there are lots of variations across simulation rounds, such that in come simulations machine learning models outperformed SER model.
-We believe the one example simulation we showed here is representative, and can make a good illustration of the yield versus EONR prediction performances.
-
-## OLS vs. SER: Statistical efficiency is money
-
-(I feel this part is only a minor point in this study. Perhaps it's not important enough to be put in the title.)
-
-- It is also interesting to compare the OLS and SER results. The good performance of SER may imply some good suggestion to production.
-- It has been well known in the econometric literature that SER model can improve the estimation efficiency compared to OLS at the presence of unknown spatial data autocorrrelation, which is a very common in crop field characteristics data.
-- However, since it is only an efficiency issue, and SER does not correct for bias, this advantage of SER model has not received enough attention.
-The efficiency improvement is only regarded as a statistical property, while its economic benefit is not well recognized.
-- Our simulation evidence showed that the statistical efficiency of SER model can actually translate into considerable more profitable EONR recommendations.
-The profit of SER model is higher than OLS model by $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$ for large, medium, and small fields, respectively.
-- So, using SER model to update the OLS model is likely to be economically beneficial in on-farm experimental data analysis, and should be encouraged.
 

### 2022-02-21 Writing/knit.R

@@ -1,2 +1,3 @@
 library(rmarkdown)
 render(here::here("GitControlled/Writing/manuscript.rmd"))
+

### 2022-02-21 Writing/manuscript.rmd
change in lm ser

@@
 The more accurately estimated coefficients are, the more accurately site-specific EONRs are estimated, leading to a higher profit.
-
-- However, since it is only an efficiency issue, and SER does not correct for bias, this advantage of SER model has not received enough attention.
-The efficiency improvement is only regarded as a statistical property, while its economic benefit is not well recognized.
-- Our simulation evidence showed that the statistical efficiency of SER model can actually translate into considerable more profitable EONR recommendations.
+While \@ref(anselin) bluh bluh, they did not do it right.
+Our results show that improving statistical efficiency by taking into account the spatial autocorrelation of the error term can lead to a substantial increase in profit by VRA.
 The profit of SER model is higher than OLS model by $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$ for large, medium, and small fields, respectively.
-- So, using SER model to update the OLS model is likely to be economically beneficial in on-farm experimental data analysis, and should be encouraged.
+To our knowledge,
 

### 2022-02-24 Writing/manuscript.rmd
remove the 2880 pictures

--- 2022-02-20 Writing/manuscript.rmd
@@
 ---
-title: "Pitfall of Prediction-orienterd Machine Learning Methods and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
+title: "Pitfall of Prediction-orienterd Machine Learning Models and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
 author:
@@
 
-## Profit performances
+### Profit
+
+The production profit of location $i$ by applying the estimated site-specific EONR is:
 
@@
 ```{r yield-curves, fig.cap="Estimated yield response curves at a specific location", fig.height=8.5, fig.width=7, echo=FALSE, cache=FALSE}
-include_graphics(here("GitControlled", "Graphs", "802_yield.png"))
+include_graphics(here("Shared", "Graphs", "802_yield.png"))
 ```
@@
 ```{r treatment-effect, fig.cap="", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
-include_graphics(here("GitControlled", "Graphs", "treatment_sim_58.png"))
+include_graphics(here("Shared", "Graphs", "treatment_sim_58.png"))
 ```

### 2022-02-25 Writing/manuscript.rmd
Updates: (1) best-performing model count table, (2) EONR ratio kernel, (3) pairwise t-test tables

@@
   unnest(perform) %>%
-  data.table()
-#' rename columns
-est_data <- est_data %>%
+  data.table() %>% 
   .[, .(field_col, model, sim, profit, rmse_train, rmse_cv, rmse_eonr)] %>%
@@
   .[, field_size := paste0(round(field_col * 72 * 6^2 / 10000, 1), " ha")] %>%
-  .[, field_size := factor(field_size, levels = c("9.3 ha", "18.7 ha", "37.3 ha"))] %>%
+  .[, field_size := factor(field_size, levels = c("37.3 ha", "18.7 ha", "9.3 ha"))] %>%
   #---model name---
@@
   .[, model := factor(model, levels = c("RF", "RF_b", "BRF", "OLS", "SER"))]
+
 #' mean and sd
@@
   .[order(field_size, model), ]
-#' load illustration data (single simulation)
-illus_data <-
-  readRDS(here("Shared", "Results", "illus_data.rds"))
+
+#' aunit level data
+aunit_data <-
+    readRDS(here("Shared", "Results", "aunit_data.rds"))
 
@@
 
-```{r yield-curves, fig.cap="Estimated yield response curves at a specific location", fig.height=8.5, fig.width=7, echo=FALSE, cache=FALSE}
+```{r yield-curves, fig.cap="Estimated yield response curves at a specific location", fig.height=5.5, fig.width=5, echo=FALSE, cache=FALSE}
 include_graphics(here("Shared", "Graphs", "802_yield.png"))
@@
 
+```{r eonr-ratio-kernel, fig.cap="Ratio of Estimated EONR to True EONR", fig.height=4.5, fig.width=5, echo=FALSE, cache=FALSE}
+eonr_ratio_kernel
+```
+
 # Tables {-}
 
-```{r extreme-percent, echo=FALSE}
-# knitr::kable(mean_data, format = "markdown", caption = "Summary Statistics")
+```{r count-table, echo=FALSE, cache=FALSE}
+prt_table <- est_data %>% 
+    .[order(sim, model), ] %>% 
+    .[, y := (rmse_cv==min(rmse_cv)) %>% as.numeric(), by = .(sim, field_size)] %>% 
+    .[, eonr := (rmse_eonr==min(rmse_eonr)) %>% as.numeric(), by = .(sim, field_size)] %>% 
+    .[, pi := (profit==max(profit)) %>% as.numeric(), by = .(sim, field_size)] %>% 
+    .[, .(`yield` = (sum(y)/.N*100) %>% round(2),
+          `EONR` = (sum(eonr)/.N*100) %>% round(2),
+          `profit` = (sum(pi)/.N*100) %>% round(2)), by = .(field_size, model)]
+# datasummary(
+#         field_size * (yield + EONR + profit) ~ factor(model) * (Mean), 
+#         data = count_table,
+#         title = 'Percentage (%) of each model being the best-performing among the five models in a single simulation round',
+#         notes = c('A note at the bottom of the table.')
+#     )
+count_table <- prt_table %>% 
+    #=== Wide to Long: melt()
+    melt(id.vars = c('field_size','model')) %>% 
+    #=== Long to Wide: dcast()
+    dcast(field_size + variable ~ model, value.var = "value")
+knitr::kable(count_table, format = "markdown",
+             caption = "Percentage (%) of each model being the best-performing among the five models in a single simulation round")
 ```
+
+```{r pair-table-yield, echo=FALSE, cache=FALSE}
+model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
+pair_df <- data.frame()
+for(i in 1:length(model_list)){
+    for(j in 1:length(model_list)){
+        pi <- est_data %>% 
+            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
+            pull(rmse_cv)
+        pj <- est_data %>% 
+            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
+            pull(rmse_cv)
+        pv <- t.test(pi, 
+                     pj, 
+                     paired = TRUE)
+
+        pair_df[model_list[i], model_list[j]] <- 
+            round(pv$estimate, 2)
+        pair_df[as.character(i), model_list[j]] <- 
+            paste0("(", round(pv$p.value, 3), ")")
+    }
+}
+pair_df[is.na(pair_df)] <- ""
+knitr::kable(pair_df, format = "markdown",
+             caption = "Pairwise t-test of predicted yield RMSE between models, Large field (37.3 ha), values are the difference in RMSE (row vs. index) (kg/ha), p-values in parenthese")
+```
+
+```{r pair-table-eonr, echo=FALSE, cache=FALSE}
+model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
+pair_df <- data.frame()
+for(i in 1:length(model_list)){
+    for(j in 1:length(model_list)){
+        pi <- est_data %>% 
+            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
+            pull(rmse_eonr)
+        pj <- est_data %>% 
+            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
+            pull(rmse_eonr)
+        pv <- t.test(pi, 
+                     pj, 
+                     paired = TRUE)
+
+        pair_df[model_list[i], model_list[j]] <- 
+            round(pv$estimate, 2)
+        pair_df[as.character(i), model_list[j]] <- 
+            paste0("(", round(pv$p.value, 3), ")")
+    }
+}
+pair_df[is.na(pair_df)] <- ""
+knitr::kable(pair_df, format = "markdown",
+             caption = "Pairwise t-test of predicted EONR RMSE between models, Large field (37.3 ha), values are the difference in RMSE (row vs. index) (kg/ha), p-values in parenthese")
+```
+
+```{r pair-table-profit, echo=FALSE, cache=FALSE}
+model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
+pair_df <- data.frame()
+for(i in 1:length(model_list)){
+    for(j in 1:length(model_list)){
+        pi <- est_data %>% 
+            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
+            pull(profit)
+        pj <- est_data %>% 
+            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
+            pull(profit)
+        pv <- t.test(pi, 
+                     pj, 
+                     paired = TRUE)
+
+        pair_df[model_list[i], model_list[j]] <- 
+            round(pv$estimate, 2)
+        pair_df[as.character(i), model_list[j]] <- 
+            paste0("(", round(pv$p.value, 3), ")")
+    }
+}
+pair_df[is.na(pair_df)] <- ""
+knitr::kable(pair_df, format = "markdown",
+             caption = "Pairwise t-test of profits between models, Large field (37.3 ha), values are the difference in profits (row vs. index) (kg/ha), p-values in parenthese")
+```

### 2022-02-25 Codes/3_make_figures_tables.R

@@ -258,7 +258,7 @@ for(s in unique(gdata_long$fsize)){
 # fig.cap = "Illustration, single simulation"
 
 sim_example = 58
-gdata <- illus_data[sim==sim_example, ]
+gdata <- aunit_data[sim==sim_example, ]
 mean_dt <- gdata %>% 
     .[, .(
         rmse_yield = mean((yield - yield_hat)^2, na.rm = TRUE) %>% sqrt() %>% round(1),
@@ -277,6 +277,20 @@ single_simu_yield <-
 #* predicted vs true EONR
 single_simu_EONR <- 
     source(here("GitControlled", "Codes", "Modules", "figure_single_simu_EONR.R"))$value
+
+
+
+# /*===========================================================
+#' # Ratio to True EONR 
+# /*===========================================================
+# fig.id = "eonr-ratio-kernel",
+# fig.cap = ""
+
+gdata <- aunit_data
+#------ kernel density ------#
+source(here("GitControlled","Codes","Modules","figure_eonr_ratio_kernel.R"))
+eonr_ratio_kernel <- g_plot
+
 
 
 #

### 2022-02-25 Codes/Modules/figure_single_simu_yield.R

@@ -2,11 +2,11 @@
 #* predicted vs true yield
 
 ggplot(data = gdata) +
-    geom_point(aes(x = yield, y = yield_hat, color = model), size = 0.5) +
+    geom_point(aes(x = yield, y = yield_hat), size = 0.5) +
     geom_text(
         data = mean_dt, hjust = 0, size = 2.5,
         aes(x = x_yield, y = y_yield, label = paste0("RMSE=", rmse_yield))) +
-    geom_abline(intercept = 0, slope = 1, color = "black", size = 1) +
+    geom_abline(intercept = 0, slope = 1, color = "red", size = 1) +
     facet_wrap(~ model, ncol = 3) +
     ylab("Out-of-Sample Predicted Yield (kg/ha)") +
     xlab("Observed Yield (kg/ha)") +

### 2022-02-26 Writing/manuscript.rmd
minor fixes

--- 2022-02-24 Writing/manuscript.rmd
@@
 
-## Insights into the divergence in yield and EONR prediction
+## Insights into the divergence in yield and EONR prediction performance
 
@@
 The more accurately estimated coefficients are, the more accurately site-specific EONRs are estimated, leading to a higher profit.
+While \@ref(anselin) bluh bluh, they did not do it right.
+Our results show that improving statistical efficiency by taking into account the spatial autocorrelation of the error term can lead to a substantial increase in profit by VRA.
+The profit of SER model is higher than OLS model by $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$ for large, medium, and small fields, respectively.
+To our knowledge, there is no
 
-- However, since it is only an efficiency issue, and SER does not correct for bias, this advantage of SER model has not received enough attention.
-The efficiency improvement is only regarded as a statistical property, while its economic benefit is not well recognized.
-- Our simulation evidence showed that the statistical efficiency of SER model can actually translate into considerable more profitable EONR recommendations.
-The profit of SER model is higher than OLS model by $\$$`r (mean_data[field_size=="37.3 ha"&model=="SER", profit] - mean_data[field_size=="37.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, $\$$`r (mean_data[field_size=="18.7 ha"&model=="SER", profit] - mean_data[field_size=="18.7 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$, and $\$$`r (mean_data[field_size=="9.3 ha"&model=="SER", profit] - mean_data[field_size=="9.3 ha"&model=="OLS", profit]) %>% round(2)` ha$^{-1}$ for large, medium, and small fields, respectively.
-- So, using SER model to update the OLS model is likely to be economically beneficial in on-farm experimental data analysis, and should be encouraged.
-
-## Field sizes
+## Field size
 
@@
 ```{r yield-curves, fig.cap="Estimated yield response curves at a specific location", fig.height=8.5, fig.width=7, echo=FALSE, cache=FALSE}
-include_graphics(here("Shared", "Graphs", "802_yield.png"))
+include_graphics(here("Shared/Graphs/802_yield.png"))
 ```
@@
 ```{r treatment-effect, fig.cap="", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
-include_graphics(here("Shared", "Graphs", "treatment_sim_58.png"))
+include_graphics(here("Shared/Graphs/treatment_sim_58.png"))
 ```

### 2022-02-26 Writing/knit.R

@@ -1,3 +1,4 @@
 library(rmarkdown)
 render(here::here("GitControlled/Writing/manuscript.rmd"))
 
+

### 2022-02-26 Writing/appendix.rmd
codes to generate pairwise t-test updated

# Pairwise t-test of yield RMSE, EONR RMSE, and profit between models {-}
```{r count-table, echo=FALSE, cache=FALSE}

prt_table <-
  est_data %>%
  .[order(sim, model), ] %>%
  .[, y := (rmse_cv == min(rmse_cv)), by = .(sim, field_size)] %>%
  .[, eonr := (rmse_eonr == min(rmse_eonr)), by = .(sim, field_size)] %>%
  .[, profit := (profit == max(profit)), by = .(sim, field_size)] %>%
  .[,
    .(
      yield = (mean(y) * 100) %>% round(2),
      EONR = (mean(eonr) * 100) %>% round(2),
      profit = (mean(profit) * 100) %>% round(2)
    ),
    by = .(field_size, model)
  ]

#* create a table
count_table <-
  prt_table %>%
  # === Wide to Long: melt()
  melt(id.vars = c("field_size", "model")) %>%
  # === Long to Wide: dcast()
  dcast(field_size + variable ~ model, value.var = "value")

#* displary the table
knitr::kable(count_table,
  format = "markdown",
  caption = "Percentage (%) of each model being the best-performing among the five models in a single simulation round"
)
```

```{r run-pairwise-test, inlcude = FALSE}
est_data_by_model_1 <-
  est_data %>%
  arrange(sim) %>%
  nest_by(model, field_col) %>%
  mutate(data = list(
    data.table(data)
  )) %>%
  setnames(names(.), paste0(names(.), "_1"))

est_data_by_model_2 <-
  copy(est_data_by_model_1) %>%
  setnames(names(.), gsub("_1", "_2", names(.)))

source(here("GitControlled/Codes/Functions/R/expand_grid_df.R"))

test_data <-
  expand_grid_df(est_data_by_model_1, est_data_by_model_2) %>%
  #* different models
  filter(model_1 != model_2) %>%
  #* same field size
  filter(field_col_1 == field_col_2) %>%
  mutate(yield_pt = list(
    t.test(
      data_1[, rmse_cv],
      data_2[, rmse_cv],
      paired = TRUE
    )
  )) %>%
  mutate(eonr_pt = list(
    t.test(
      data_1[, rmse_eonr],
      data_2[, rmse_eonr],
      paired = TRUE
    )
  )) %>%
  mutate(pi_pt = list(
    t.test(
      data_1[, profit],
      data_2[, profit],
      paired = TRUE
    )
  ))
```

```{r pair-table-yield, tab.cap = "Pairwise t-test of predicted yield RMSE between models"}

test_data %>%
  select(field_col_1, model_1, model_2, yield_pt) %>%
  mutate(
    yield_pt_txt =
      paste0(
        round(yield_pt$estimate, digits = 2), " (",
        round(yield_pt$statistic, digits = 2), ")"
      )
  ) %>%
  data.table() %>%
  dcast(field_col_1 + model_1 ~ model_2, value.var = "yield_pt_txt") %>%
  .[model_1 != "SER", ] %>%
  .[, RF := NULL] %>%
  .[model_1 == "BRF", `:=`(RF_b = NA)] %>%
  .[model_1 == "OLS", `:=`(BRF = NA, RF_b = NA)] %>%
  setnames(c("field_col_1", "model_1"), c("Field Size", "Model\\Model")) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  hline(i = c(4, 8)) %>%
  autofit() %>%
  fix_border_issues() %>%
  align(j = c(1, 2), align = "center")
```

```{r pair-table-eonr, tab.cap = "Pairwise t-test of predicted EONR RMSE between models"}

test_data %>%
  select(field_col_1, model_1, model_2, eonr_pt) %>%
  mutate(
    eonr_pt_txt =
      paste0(
        round(eonr_pt$estimate, digits = 2), " (",
        round(eonr_pt$statistic, digits = 2), ")"
      )
  ) %>%
  data.table() %>%
  dcast(field_col_1 + model_1 ~ model_2, value.var = "eonr_pt_txt") %>%
  .[model_1 != "SER", ] %>%
  .[, RF := NULL] %>%
  .[model_1 == "BRF", `:=`(RF_b = NA)] %>%
  .[model_1 == "OLS", `:=`(BRF = NA, RF_b = NA)] %>%
  setnames(c("field_col_1", "model_1"), c("Field Size", "Model\\Model")) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  hline(i = c(4, 8)) %>%
  autofit() %>%
  fix_border_issues() %>%
  align(j = c(1, 2), align = "center")

# Note: values are the difference in RMSE (row vs. index) (kg/ha), p-values in parenthese

```

```{r pair-table-profit, tab.cap = "Pairwise t-test of profits between models"}

test_data %>%
  select(field_col_1, model_1, model_2, pi_pt) %>%
  mutate(
    pi_pt_txt =
      paste0(
        round(pi_pt$estimate, digits = 2), " (",
        round(pi_pt$statistic, digits = 2), ")"
      )
  ) %>%
  data.table() %>%
  dcast(field_col_1 + model_1 ~ model_2, value.var = "pi_pt_txt") %>%
  .[model_1 != "SER", ] %>%
  .[, RF := NULL] %>%
  .[model_1 == "BRF", `:=`(RF_b = NA)] %>%
  .[model_1 == "OLS", `:=`(BRF = NA, RF_b = NA)] %>%
  setnames(c("field_col_1", "model_1"), c("Field Size", "Model\\Model")) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  hline(i = c(4, 8)) %>%
  autofit() %>%
  fix_border_issues() %>%
  align(j = c(1, 2), align = "center")
```

### 2022-02-26 Writing/manuscript.rmd
codes to generate pairwise t-test updated

@@
 
+<div id="refs"></div>
+
 `r run_pagebreak()`
@@
 
-# Tables {-}
+# Appendix {-}
 
-```{r count-table, echo=FALSE, cache=FALSE}
-prt_table <- est_data %>% 
-    .[order(sim, model), ] %>% 
-    .[, y := (rmse_cv==min(rmse_cv)) %>% as.numeric(), by = .(sim, field_size)] %>% 
-    .[, eonr := (rmse_eonr==min(rmse_eonr)) %>% as.numeric(), by = .(sim, field_size)] %>% 
-    .[, pi := (profit==max(profit)) %>% as.numeric(), by = .(sim, field_size)] %>% 
-    .[, .(`yield` = (sum(y)/.N*100) %>% round(2),
-          `EONR` = (sum(eonr)/.N*100) %>% round(2),
-          `profit` = (sum(pi)/.N*100) %>% round(2)), by = .(field_size, model)]
-# datasummary(
-#         field_size * (yield + EONR + profit) ~ factor(model) * (Mean), 
-#         data = count_table,
-#         title = 'Percentage (%) of each model being the best-performing among the five models in a single simulation round',
-#         notes = c('A note at the bottom of the table.')
-#     )
-count_table <- prt_table %>% 
-    #=== Wide to Long: melt()
-    melt(id.vars = c('field_size','model')) %>% 
-    #=== Long to Wide: dcast()
-    dcast(field_size + variable ~ model, value.var = "value")
-knitr::kable(count_table, format = "markdown",
-             caption = "Percentage (%) of each model being the best-performing among the five models in a single simulation round")
+```{r, child = "appendix.Rmd"}
 ```
-
-```{r pair-table-yield, echo=FALSE, cache=FALSE}
-model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
-pair_df <- data.frame()
-for(i in 1:length(model_list)){
-    for(j in 1:length(model_list)){
-        pi <- est_data %>% 
-            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
-            pull(rmse_cv)
-        pj <- est_data %>% 
-            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
-            pull(rmse_cv)
-        pv <- t.test(pi, 
-                     pj, 
-                     paired = TRUE)
-
-        pair_df[model_list[i], model_list[j]] <- 
-            round(pv$estimate, 2)
-        pair_df[as.character(i), model_list[j]] <- 
-            paste0("(", round(pv$p.value, 3), ")")
-    }
-}
-pair_df[is.na(pair_df)] <- ""
-knitr::kable(pair_df, format = "markdown",
-             caption = "Pairwise t-test of predicted yield RMSE between models, Large field (37.3 ha), values are the difference in RMSE (row vs. index) (kg/ha), p-values in parenthese")
-```
-
-```{r pair-table-eonr, echo=FALSE, cache=FALSE}
-model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
-pair_df <- data.frame()
-for(i in 1:length(model_list)){
-    for(j in 1:length(model_list)){
-        pi <- est_data %>% 
-            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
-            pull(rmse_eonr)
-        pj <- est_data %>% 
-            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
-            pull(rmse_eonr)
-        pv <- t.test(pi, 
-                     pj, 
-                     paired = TRUE)
-
-        pair_df[model_list[i], model_list[j]] <- 
-            round(pv$estimate, 2)
-        pair_df[as.character(i), model_list[j]] <- 
-            paste0("(", round(pv$p.value, 3), ")")
-    }
-}
-pair_df[is.na(pair_df)] <- ""
-knitr::kable(pair_df, format = "markdown",
-             caption = "Pairwise t-test of predicted EONR RMSE between models, Large field (37.3 ha), values are the difference in RMSE (row vs. index) (kg/ha), p-values in parenthese")
-```
-
-```{r pair-table-profit, echo=FALSE, cache=FALSE}
-model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
-pair_df <- data.frame()
-for(i in 1:length(model_list)){
-    for(j in 1:length(model_list)){
-        pi <- est_data %>% 
-            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
-            pull(profit)
-        pj <- est_data %>% 
-            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
-            pull(profit)
-        pv <- t.test(pi, 
-                     pj, 
-                     paired = TRUE)
-
-        pair_df[model_list[i], model_list[j]] <- 
-            round(pv$estimate, 2)
-        pair_df[as.character(i), model_list[j]] <- 
-            paste0("(", round(pv$p.value, 3), ")")
-    }
-}
-pair_df[is.na(pair_df)] <- ""
-knitr::kable(pair_df, format = "markdown",
-             caption = "Pairwise t-test of profits between models, Large field (37.3 ha), values are the difference in profits (row vs. index) (kg/ha), p-values in parenthese")
-```

### 2022-02-26 Writing/appendix.rmd
code for tables modified

@@
 # Pairwise t-test of yield RMSE, EONR RMSE, and profit between models {-}
-```{r count-table, echo=FALSE, cache=FALSE}
+```{r count-table, tab.cap = "Percentage (%) each model performs the best for yield prediction, EONR prediction, and profit", echo=FALSE, cache=FALSE}
 
@@
     ),
-    by = .(field_size, model)
+    by = .(field_size, field_col, model)
   ]
@@
   # === Wide to Long: melt()
-  melt(id.vars = c("field_size", "model")) %>%
+  melt(id.vars = c("field_size", "field_col", "model")) %>%
   # === Long to Wide: dcast()
-  dcast(field_size + variable ~ model, value.var = "value")
+  dcast(field_size + field_col + variable ~ model, value.var = "value") %>%
+  .[variable == "yield", variable := "Yield"] %>%
+  .[variable == "profit", variable := "Profit"] %>%
+  .[order(field_col), ] %>%
+  .[, field_col := NULL] %>%
+  setnames(c("field_size", "variable"), c("Field Size", "Measurement"))
 
-#* displary the table
-knitr::kable(count_table,
-  format = "markdown",
-  caption = "Percentage (%) of each model being the best-performing among the five models in a single simulation round"
-)
+flextable(count_table) %>%
+  merge_v(j = 1) %>%
+  hline(i = c(3, 6)) %>%
+  autofit() %>%
+  fix_border_issues() %>%
+  align(j = c(1, 2), align = "center")
 ```
